### 2017-10-03 paper/deadtime.tex
Initial commit

%%
%% Beginning of file 'sample61.tex'
%%
%% Modified 2016 September
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.1 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.1
\documentclass[twocolumn]{aastex61}

\usepackage{xspace}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex61}
%% 
%% where the arguement options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex61}

%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\nustar}{\project{NuSTAR}\xspace}
\newcommand{\fermi}{\project{Fermi}\xspace}
\newcommand{\rxte}{\project{RXTE}\xspace}
\newcommand{\xmm}{\project{XMM-Newton}\xspace}
\newcommand{\rosat}{\project{ROSAT}\xspace}
\newcommand{\swift}{\project{Swift}\xspace}
\newcommand{\astrosat}{\project{Astrosat}\xspace}
\newcommand{\ixpe}{\project{IXPE}\xspace}
\newcommand{\nicer}{\project{NICER}\xspace}
\newcommand{\sref}{Section~\ref}
\newcommand{\deadt}{\ensuremath{t_d}\xspace}

\newcommand{\given}{\ensuremath{\,|\,}}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\counts}{\ensuremath{y}}
\newcommand{\pars}{\ensuremath{\theta}}
\newcommand{\mean}{\ensuremath{\lambda}}
\newcommand{\likelihood}{\ensuremath{{\mathcal L}}}
\newcommand{\Poisson}{\ensuremath{{\mathcal P}}}
\newcommand{\Uniform}{\ensuremath{{\mathcal U}}}

\newcommand{\Normal}{\ensuremath{{\mathcal N}}}
\newcommand{\bg}{\ensuremath{\mathrm{bg}}}
\newcommand{\word}{\ensuremath{\phi}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{XXXX}
\revised{XXXX}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJL}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.1 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%
%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
%% collaboration" on the front page of this example manuscript.
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{The Fourier Amplitude Difference correction for periodograms}
\shortauthors{Bachetti \& Huppenkothen}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{No time for dead time - Use the Fourier amplitude differences to normalize dead time-affected periodograms}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.1 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affilations. The change was necessary to implement 
%% autoindexing of affilations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% arguement which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.1 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.1 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

\correspondingauthor{Matteo Bachetti}
\email{bachetti@oa-cagliari.inaf.it}

\author[0000-0002-4576-9337]{Matteo Bachetti}
\affil{INAF-Osservatorio Astronomico di Cagliari, via della Scienza 5, I-09047 Selargius (CA)}

\author{Daniela Huppenkothen}
\affiliation{Center for Data Science, New York University, 60 5h Avenue, 7th Floor, New York, NY 10003 }
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003, USA}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.1 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
Dead time affects many of the instruments used in X-ray astronomy, by producing a strong distortion in power density spectra. This can make it difficult to model the aperiodic variability of the source or look for quasi-periodic oscillations.
Whereas in some instruments a simple a-priori correction for dead time-affected power spectra is possible, 
this is not the case for others such as \nustar, where the dead time is non-constant and long ($\sim$2.5\,ms).
\citet{Bachetti+15} suggested the cospectrum obtained from light curves of independent detectors within the same instrument as a possible way out, but this solution has always only been a partial one: the measured rms was still affected by dead time, because the width of the power distribution of the cospectrum was modulated by dead time in a frequency-dependent way.

In this Letter we suggest a new, powerful method to normalize cospectra and, with some caveats, even power density spectra. Our approach uses the difference of the Fourier amplitudes from two independent detectors to characterize and filter out the effect of dead time. This method is crucially important for the accurate modelling of periodograms derived from instruments affected by dead time on board current missions like \nustar and \astrosat, but also future missions such as \ixpe.
\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{X-rays: binaries --- 
X-rays: general --- methods: data analysis --- methods: statistical}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\section{Introduction} \label{sec:intro}
Dead time is an unavoidable and common issue of photon-counting instruments.
It is the time $\deadt$ that the instrument takes to process an event and be ready for the next event.
In most current astronomical photon-counting X-ray missions, dead time is of the \textit{non-paralyzable} kind, meaning that the instrument does not accept new events during dead time, avoiding a complete lock of the instrument if the incident rate of photons is higher than $1/\deadt$.
Being roughly energy-independent, dead time is not usually an issue for spectroscopy, as it only affects the maximum rate of photons that can be recorded, so it basically only increases the observing time needed for high quality spectra.
For timing analysis, the effect of dead time is far more problematic.
The periodogram, commonly referred to as power density spectrum (PDS)%
\footnote{here we will use the term PDS for the actual source power spectrum, and \textit{periodogram} to indicate our estimate of it, or otherwise said, the realization of the ``real'' power spectrum we observe in the data}%
, which is the most widely used statistical tool to investigate rapid variability, is heavily distorted by dead time, with a characteristic pattern similar to a damped oscillator.
This pattern is stronger for brighter sources, and it is often not possible to disentangle this spectral distortion due to dead time and the broadband noise components characterizing the emission of accreting systems.
In the special case where dead time is constant, its shape can be modeled precisely \citep{Zhang+95,Vikhlinin+94}.
However, dead time is often different on an event-to-event basis, and it is not obvious how to model it precisely, also because the information on dead time is often incomplete in the data files distributed by HEASARC%
\footnote{Whereas in principle this information could be obtained by using the PRIOR column in the unfiltered event files for some missions, the live time given in this column is affected by events that are not recorded in the file, like shield vetos in the case of \nustar, and the estimate of dead time is necessarily uncertain}%
.
For a more thorough discussion about different dead time behaviors see \citet{Zhang+95}.

When using data from missions carrying two or more \textit{identical and independent} detectors like \nustar, \citet{Bachetti+15} proposed an approach to mitigate instrumental effects like dead time exploiting this redundancy: 
where in standard analysis, light curves of multiple detectors are summed before Fourier transforming the summed light curve, 
it is possible to instead Fourier-transform the signal of two independent detectors and combine the Fourier amplitudes in a \textit{cospectrum} -- the real part of the cross spectrum -- instead of the periodogram. 
Since dead time is uncorrelated between the two detectors, the resulting powers have a mean white noise level fixed to 0, which resolves the first and most problematic issue created by dead time (see details in \citealt{Bachetti+15}); however, the resulting powers no longer follow the statistical distribution expected for power spectra, and their probability distribution is frequency-dependent.
Whereas a noise cospectrum in the absence of dead time would follow a Laplace distribution (Huppenkothen and Bachetti, sub.),
dead time affects the width of the probability distribution for cospectral powers and modulates the measured rms proportionally to the distortion acted on power spectra.
In this Letter, we show a method to precisely recover the shape of the power density spectrum by looking at the difference of the Fourier amplitudes of the light curves of two independent detectors.
This difference, in fact, contains information on the uncorrelated noise produced by dead time, but not on the source-related  signal which is correlated between the two detectors.
This allows to disentangle the effects of dead time from those of the source variability.

In \sref{sec:data} we briefly describe our data analysis and simulation setup.
In \sref{sec:fourierdiff} we show that, in the absence of dead time, the Fourier amplitudes of two independent detectors contain the sum of the correlated signal (the source signal) and uncorrelated noise (detector-related noise), and that their difference eliminates the source part. 
In \sref{sec:wndeadtime} we show that, in the presence of dead time, the difference of the Fourier amplitude still eliminates the source signal but retains information on dead time effects.
In \sref{sec:correction} we show that this can be used to recover the dead noise-free power spectrum.

\section{Data simulation and analysis} \label{sec:data}
\subsection{Simulated datasets}
All simulated data sets in this paper have been produced with a combination of the two Python libraries \texttt{stingray} \citep{huppenkothen2016} and \texttt{HENDRICS} \citep[formerly known as MaLTPyNT][]{2015ascl.soft02021B}, both based on Astropy \citep{astropy2013}.
The \texttt{stingray.simulate.Simulator} class was used to simulate light curves with a given noise profile, 
the \texttt{stingray.Eventlist.simulate\_times()} function was used to transform the light curves into event lists using rejection sampling, 
and finally the \texttt{hendrics.fake.filter\_for\_deadtime()} function was used to apply a non-paralyzable dead time to the simulated event lists. For more details on the simulated data sets, see also Section \ref{sec:correction} and the available Jupyter notebooks\footnote{\href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II}} \citep[for a description of Jupyter notebooks, see][]{kluyver2016jupyter}.

\subsection{Cyg X-1 \nustar dataset}
We downloaded the observation directory of ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package [ASCL in prep.]. 
Starting from the standard cleaned science event files distributed by HEASARC, we applied a barycenter correction using the FTOOL \texttt{barycorr} shipped with HEASOFT 6.21 with the clock correction file n. 71 from the \nustar CALDB.
We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.
We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and selected photons from 3 to 79 keV.

\section{On the difference of Fourier amplitudes} \label{sec:fourierdiff}
\begin{figure*}
\plottwo{imgs/rn_fourierdiff}{imgs/rn_fourierdiff_dt}
\caption{Real Fourier amplitudes obtained by single light curves (top panels) and difference between two realizations of the same source light curve (bottom) in two cases: (Left) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (Right) no red noise and strong dead time, calculated over many 5\,s segments of the light curve. 
The choice of different segment length reflects the range of frequencies we want to highlight in the two cases.
The red curve gives the frequency-dependent spread of the distributions, measured by the standard deviation of the curves in each frequency bin. 
As expected, in the first case, the Fourier amplitude follows a power law curve, while the standard deviation of the difference is remarkably stable at all frequencies, as expected by the fact that the Poisson white noise is independent of frequency. 
In the second case, instead, dead time is frequency dependent and white noise is also affected, so that the difference of Fourier amplitudes is modulated as well.}
\label{fig:fourierdiff}
\end{figure*}

Let us consider two identical and independent detectors observing the same variable source, producing independent time series $\mathbf{x} = \{x_k\}_{k=1}^N$ and $\mathbf{y} = \{y_k\}_{k=1}^N$. For a stochastic process (e.g.\ $1/\nu$-type red noise), the Fourier amplitudes will vary as a function of $N_{\mathrm{phot}}P(\nu)/4$, where $P(\nu)$ is the shape of the power spectrum underlying the stochastic process, and $N_{\mathrm{phot}}$ denotes the number of photons in a light curve. If the two detectors observe the same source simultaneously, the amplitudes and phases of the stochastic process will be shared among $\mathbf{x}$ and $\mathbf{y}$, while each light curve will be affected \textit{independently} by both the photon counting noise in the detector, as well as the dead time process. The resulting Fourier amplitudes will be of the form

\begin{eqnarray}
A_{xj} &=& A_{xsj} + A_{xdj} + A_{xnj} \nonumber \\
B_{xj} &=& B_{xsj} + A_{xdj} + B_{xnj} \, ,
\end{eqnarray}

\noindent where $A_{xsj}$ and $B_{xsj}$ denote the real and imaginary components of the signal power in the Fourier amplitudes,  $A_{xdj}$ and $B_{xdj}$ denote the variance introduced by dead time, and $A_{xnj}$ and $B_{xnj}$ similarly denote the white noise components in the Fourier amplitudes.
For a large enough number of data points $N$, the Fourier amplitudes $A_{xj}$ and $B_{xj}$ will be composed of a sum of three independent random normal variables, with $A_{xsj} \sim \Normal(0, \sigma_{sj}^2)$,  $A_{xdj} \sim \Normal(0, \sigma_{dj}^2)$ and $A_{xnj} \sim \Normal(0, \sigma_n^2)$, where $\sigma_{sj}^2 = \sigma_{s}^2(\nu) = N_\mathrm{phot}P(\nu)/4$ is given by the (Leahy-normalized, \citealt{Leahy+83}) power spectrum of the underlying stochastic process, $P_j = P(\nu_j)$, $\sigma_{dj}^2$ is an unknown, frequency-dependent variance introduced by dead time, and $N_{\mathrm{phot}} = \sum_{k=1}^{N}{x_k}$ is the integrated flux in the light curve. We also have $\sigma_n^2 = N_\mathrm{phot}/2$, and hence the combined distributions become

\begin{eqnarray}
A_{xj} &\sim & \Normal(0, \sigma_{sj}^2 + \sigma_{dj}^2 + \sigma_{n}^2) \nonumber \\
A_{yj} &\sim & \Normal(0, \sigma_{sj}^2 + \sigma_{dj}^2 + \sigma_{n}^2) \nonumber \, .
\end{eqnarray}

\noindent Similar expressions can be found for $A_{yj}$ and $B_{yj}$, respectively. It is important to note that $A_{xsj} = A_{ysj}$ and similarly $B_{xsj} = B_{ysj}$, that is, the amplitudes of the stationary noise process will be the same for the Fourier transforms of $\mathbf{x}$ and $\mathbf{y}$, while the components due to dead time and white noise differ between the two time series.

As depicted in Figure~\ref{fig:fourierdiff}, the correlation between Fourier amplitudes implies that their difference will be independent of the source-induced variability $P(\nu_j)$ and will again be distributed following a normal distribution

\[
A_{xj} - A_{yj} \sim \Normal(0, 2\sigma_{dj}^2 + 2\sigma_{n}^2) \; .
\]

\noindent The difference in Fourier amplitudes effectively separates the frequency-dependent effects of source variability and variability due to detector effects.

\section{dead time-affected white noise} \label{sec:wndeadtime}

\begin{figure*}
\gridline{\fig{imgs/fourier_vs_diff_dt}{0.3\textwidth}{(a)}
          \fig{imgs/pds_pdf}{0.3\textwidth}{(b)}
          \fig{imgs/cosp_pdf}{0.3\textwidth}{(c)}}

\caption{(a) Scatter distribution of dead time-affected Fourier amplitudes versus the difference of Fourier amplitudes:
their relation is clearly linear, with a factor $1/\sqrt{2}$. 
(b) Distribution of powers in the periodogram, before the FAD correction and after, shown as a histogram.
After correction, the powers follow remarkably well the expected $\chi^2_2$ distribution.
(c) Same, for the cospectrum.
The correct Laplace distribution is followed after FAD correction}
\label{fig:dist}
\end{figure*}

Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec and a dead time of 2.5 ms, as we would expect from two identical detectors observing the same stable X-ray source. 
This case is illustrated in Figure ~\ref{fig:fourierdiff} (right panel).
The Fourier amplitudes $A_{xj}$ and $A_{yj}$ of the light curves from the two detectors are heavily distorted by dead time, with the characteristic damped oscillator-like shape \citep{Vikhlinin+94,Zhang+95}. 
As laid out in Section \ref{sec:fourierdiff}, the difference of Fourier amplitudes from two independent but identical detectors shows no source variability, but \textit{still shows the same distortion} due to dead time.
This gives a clear way to disentangle between source- and dead time-driven variability.
By using the difference between the Fourier amplitudes in two detectors, we can in principle renormalize the power spectrum so that only the source variability alters its otherwise flat shape.

As shown in Figure~\ref{fig:dist} (left panel), the single-channel Fourier amplitudes are proportional to the difference of the Fourier amplitudes in different realizations, with a constant factor $1/\sqrt{2}$.
Therefore, we expect that the periodogram will be proportional to the square of the Fourier amplitude difference, divided by 2.
Let us try to \textit{divide the power spectrum by a smoothed version of the squared Fourier differences}, and multiply by 2.
For smoothing, we used a Gaussian running window with a window width of 50 bins.
Given that the initial binning had 50 bins/Hz, this interpolation allows an aggressive smoothing over bins whose y value does not change significantly.
In general, we recommend smoothing over as many bins as allowed by the shape of the periodogram.
In this paper, when not specified we average over the number of bins contained in 1Hz of the spectrum.
We call this procedure the \textbf{Fourier Amplitude Difference} (hereafter FAD) \textbf{correction}.

The correction is depicted in Figure~\ref{fig:pds}, right. 
Starting from a heavily distorted distribution of the powers, applying the FAD correction reinstates a remarkably correct distribution of powers, following the expected $\chi^2_2$ distribution \citep{Lewin+88} very closely.
Analogously, the corrected cospectrum will follow the expected Laplace distribution.
While the original dead time-affected cospectrum had a frequency-dependent modification to the rms level, the FAD-corrected cospectrum gets back to a frequency-independent shape, like in the dead time-free case.

\section{Testing the FAD correction on simulated data} \label{sec:correction}

\begin{figure*}
    \gridline{\fig{imgs/rednoise_rebin}{0.33\textwidth}{(a)}
        \fig{imgs/rednoise_rebin_zoom}{0.33\textwidth}{(b)}
        \fig{imgs/simu_rebin_log}{0.33\textwidth}{(c)}}
    \gridline{\fig{imgs/cygx1_soft_nustar_2_rebin}{0.33\textwidth}{(d)}
        \fig{imgs/cygx1_soft_nustar_2_rebin_zoom}{0.33\textwidth}{(e)}
        \fig{imgs/cygx1_soft_nustar_2_rebin_log}{0.33\textwidth}{(f)}}  
    \caption{
        Top: simulated dataset with two strong and broad Lorentzian components, incident count rate $\sim$810 ct/s, and total rms $\sim$15\% (``detected'' after dead time: $\sim$270 and $\sim$4\% resp.).
        Bottom: \nustar observation of the black hole candidate Cyg X-1. 
        (a) and (d): comparison of the distortion of the dead time-affected periodogram with the FAD-corrected periodogram, the dead time-affected and the FAD-corrected cospectrum. The spectra have been shifted vertically for clarity.
        The shape of the uncorrected periodogram is clearly distorted by dead time. 
        (b) and (e): the FAD correction successfully flattens the periodogram, but there remain a few intervals where the baseline is imperfect, indicated by the arrows.
        This is due to the flux mismatch between the two detectors (see \sref{sec:realdata}).
        The cospectral powers are always distributed around zero, but dead time changes the width of the resulting distribution, and the FAD correction attenuates the width of the distribution back to the width expected in the dead time-free case (see e.g.\ (b) for a striking case).
        Moreover, the source-dominated part of the spectrum also receives a boost, which corrects precisely the measured rms of the source from the ``hushing'' effect of dead time.
        (c) and (f): FAD-corrected periodogram and cospectra, plotted in $\mathrm{(rms/mean)}^2$ normalization and fitted with two Lorentzian curves (c) and with an exponential cutoff power law (f).
        The additional gain coming from the FAD normalization is evident by the comparison with the uncorrected cospectrum.}
    \label{fig:pds}
\end{figure*}

We are now ready to verify the last step: is the FAD-corrected power spectrum equivalent (albeit with some loss of sensitivity due to the lower number of photons) to the dead time-free power spectrum?
To test this, we produced a number of different synthetic datasets, containing different combinations of QPOs and broadband noise components. 
We first calculated the periodogram of the dead time-free data.
Then, we applied a dead time filter and calculated the power density spectrum and the cospectrum. 
At this point, we applied the FAD correction, as follows:
\begin{enumerate}
\item split the two light curves in segments of 128 to 512 seconds
\item for each pair of light curve segments: 
	\begin{itemize}
	\item calculate the Fourier transform of each channel separately, and then of the summed channels;
	\item multiply the Fourier amplitudes by $\sqrt{2/N_{ph}}$ in order to obtain Leahy-normalized periodograms;
	\item subtract the Fourier amplitudes of the two channels between them and obtain the Fourier Amplitude Difference (FAD);
	\item \textit{smooth} the FAD using a Gaussian-window interpolation with a width of 1-2 seconds;
	\item use the separated single-channel and summed Fourier amplitudes to calculate the periodograms;
	\item use the Fourier amplitudes from channels A and B to calculate the cospectrum;
	\item divide all periodograms and the cospectrum by the smoothed and squared FAD, and multiply by 2.
	\end{itemize}
\end{enumerate}

All spectra were then expressed in fractional rms \citep{BelloniHasinger90,Miyamoto+91} normalization, where the integral of the fitted spectral components returns directly its fractional rms.
In the rms normalization, the values of each point of the periodogram should be consistent between the dead time-free and the FAD-corrected periodograms.
We first checked visually that the spectra (white-noise subtracted in the case of periodograms) after FAD correction were all consistent with the dead time-free periodogram. 
Then, we fitted all spectra with the model which produced the simulated data and checked that the values were always consistent with the input model parameters and the fit on the dead time-free periodogram.
Finally, we verified that the total rms of the FAD-corrected spectra was always consistent with the total rms of the dead time-affected cospectrum \textit{times the ratio between incident and detected photons}, using the count rates before and after applying the dead time filter.
To calculate this rms, we fitted the spectra with two Lorentzian components, and used their amplitude in the calculation.
In this normalization, the amplitude of a Lorentzian gives the total rms squared of the component.
For periodograms, the model included also a constant offset to account for the white noise level.
An example of this analysis is shown in Figure~\ref{fig:pds} (upper panel).

The simulations show that the shape of the periodogram is precisely corrected by the FAD procedure \textit{if} the input light curves have the same count rate. 
However, in real life the two detectors can receive slightly different signals due to slightly different responses, the presence of gaps inside the PSF, etc.
Simulating datasets with slightly different light curve mean rates in the two channels, we indeed find that the performance of the FAD correction degrades.
The degradation is higher for higher count rates and higher difference between the two channels. 
Since the exact degradation is dependent on the shape of the periodograms, we recommend to FAD-correct both the periodogram and the cospectrum, and verify visually that the white-noise subtracted periodogram and the cospectrum are consistent.
For example, look for bumps or valleys in the white noise-subtracted periodogram that are not present in the cospectrum, and
trust the additional signal to noise of the periodogram only in the regions where the two are consistent.

\section{Application to Cyg X-1}\label{sec:realdata}
In this Section we apply the FAD correction to a \nustar observation of Cyg X-1.
This source was discovered in the early days of X-ray astronomy \citep{Bowyer+65} and it is among the best studied X-ray sources in the sky.
It is a persistent black hole X-ray binary, alternating soft and hard spectral states with distinct timing and spectral features \citep[see, e.g., ][]{Grinberg+13}.
The observation we analyze here was taken during the source's soft state, that is characterized by a non-thermal X-ray spectrum, stable radio jets and, what matters the most here, distinct aperiodic variability that is well fitted by an exponential cutoff power law with index $\sim1$ (see, e.g., \citealt{Gilfanov+00}).
We followed the procedure described in \sref{sec:correction}, dividing the light curves in 512-s segments and smoothing the squared FAD with a Gaussian window of 1-s width (512 bins).
The results are shown in Figure~\ref{fig:pds}, lower panel for comparison with the simulations.

We fitted the four spectra of Cyg X-1 with an exponential cutoff power law. 
For periodograms, we added to the models an additive constant to account for the white noise level.
In all cases, the estimates returned by the fit were consistent between the different spectra in all but the amplitude parameter of the power law curve.
We used this amplitude to calculate the ratios between the rms measured by the deadtime-affected cospectrum and the FAD-corrected spectra.
The increase of rms between the dead time-affected cospectrum and the FAD-corrected cospectrum and periodograms is consistent to 2\% with the ratio $r_{in}/r_{det}$, where $r_{in}$ is the incident count rate, and $r_{det}$ is the detected count rate,
given by

\begin{equation}
r_{det} = \frac{r_{in}}{1 + \deadt r_{in}}
\end{equation} 
(using the standard non-paralyzable dead time formula, where \deadt is dead time) which is the drop of rms expected from the effect of dead time \citep{Bachetti+15}.

\section{Conclusions}
In this Letter we described a method to correct the normalization of dead time-affected periodograms.
This method is valid in principle for 
1) correcting the shape of the periodogram, eliminating the well known pattern produced by dead time, and 
2) adjusting the white noise standard deviation of periodogram and cospectra to its correct value at all frequencies.
In general, we recommend applying the FAD correction to both the periodogram and the cospectrum. 
The periodogram, if obtained by the sum of the light curves, can yield a higher signal-to-noise ratio.
However, the white noise level subtraction is not always very precise due to mismatches in the mean count rate in the two light curves. 
A comparison with the FAD-corrected cospectrum, to verify visually the white noise subtraction, is always recommended.
It is important to be reasonably sure of the white noise level of the periodogram, as the white noise subtraction is the most important step when calculating the significance of a given feature in the periodogram \citep[e.g.][]{Barret+12,Huppenkothen+17}.
The cospectrum has the advantage of not requiring white noise level subtraction.

In all cases, we find that the adjustment of the white noise standard deviation in the periodogram and the cospectrum works remarkably well, allowing to make a confident analysis of X-ray variability even in sources where this was precluded until now.
This software will be merged into the main repository of \texttt{stingray} before publication.
A number of jupyter notebooks will also be posted at the address \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the full analysis plotted in the Figures of this paper, plus more examples of application of these techniques to simulated and real data.

\acknowledgments
We thank David W. Hogg for useful discussions on the topic of Fourier analysis.
MB is supported in part by the Italian Space Agency through agreement ASI-INAF n.2017-12-H.0 and ASI-INFN agreement n.2017-13-H.0.
DH is supported by the James Arthur Postdoctoral Fellowship and the Moore-Sloan Data Science Environment at New York University.

\bibliographystyle{aasjournal}
%\bibliography{deadtime,papers3}
\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\providecommand{\url}[1]{\href{#1}{#1}}

\bibitem[{{Astropy Collaboration} {et~al.}(2013){Astropy Collaboration},
  {Robitaille}, {Tollerud}, {Greenfield}, {Droettboom}, {Bray}, {Aldcroft},
  {Davis}, {Ginsburg}, {Price-Whelan}, {Kerzendorf}, {Conley}, {Crighton},
  {Barbary}, {Muna}, {Ferguson}, {Grollier}, {Parikh}, {Nair}, {Unther},
  {Deil}, {Woillez}, {Conseil}, {Kramer}, {Turner}, {Singer}, {Fox}, {Weaver},
  {Zabalza}, {Edwards}, {Azalee Bostroem}, {Burke}, {Casey}, {Crawford},
  {Dencheva}, {Ely}, {Jenness}, {Labrie}, {Lim}, {Pierfederici}, {Pontzen},
  {Ptak}, {Refsdal}, {Servillat}, \& {Streicher}}]{astropy2013}
{Astropy Collaboration}, {Robitaille}, T.~P., {Tollerud}, E.~J., {et~al.} 2013,
  \aap, 558, A33

\bibitem[{Bachetti(2015)}]{2015ascl.soft02021B}
Bachetti, M. 2015, Astrophysics Source Code Library, ascl:1502.021

\bibitem[{Bachetti {et~al.}(2015)Bachetti, Harrison, Cook, Tomsick, Schmid,
  Grefenstette, Barret, Boggs, Christensen, Craig, Fabian, F{\"u}rst, Gandhi,
  Hailey, Kara, Maccarone, Miller, Pottschmidt, Stern, Uttley, Walton, Wilms,
  \& Zhang}]{Bachetti+15}
Bachetti, M., Harrison, F.~A., Cook, R., {et~al.} 2015, ApJ, 800, 109

\bibitem[{Barret \& Vaughan(2012)}]{Barret+12}
Barret, D., \& Vaughan, S. 2012, ApJ, 746, 131

\bibitem[{Belloni \& Hasinger(1990)}]{BelloniHasinger90}
Belloni, T., \& Hasinger, G. 1990, A{\&}A, 230, 103

\bibitem[{Bowyer {et~al.}(1965)Bowyer, Byram, Chubb, \& Friedman}]{Bowyer+65}
Bowyer, S., Byram, E.~T., Chubb, T.~A., \& Friedman, H. 1965, Astronomical
  Observations from Space Vehicles, 23, 227

\bibitem[{Gilfanov {et~al.}(2000)Gilfanov, Churazov, \&
  Revnivtsev}]{Gilfanov+00}
Gilfanov, M., Churazov, E., \& Revnivtsev, M. 2000, MNRAS, 316, 923

\bibitem[{Grinberg {et~al.}(2013)Grinberg, Hell, Pottschmidt, B{\"o}ck, Nowak,
  Rodriguez, Bodaghee, Cadolle~Bel, Case, Hanke, K{\"u}hnel, Markoff, Pooley,
  Rothschild, Tomsick, Wilson-Hodge, \& Wilms}]{Grinberg+13}
Grinberg, V., Hell, N., Pottschmidt, K., {et~al.} 2013, 554, 88

\bibitem[{{Huppenkothen} {et~al.}(2016){Huppenkothen}, {Bachetti}, {Stevens},
  {Migliari}, \& {Balm}}]{huppenkothen2016}
{Huppenkothen}, D., {Bachetti}, M., {Stevens}, A.~L., {Migliari}, S., \&
  {Balm}, P. 2016, {Stingray: Spectral-timing software}, Astrophysics Source
  Code Library, , , ascl:1608.001

\bibitem[{Huppenkothen {et~al.}(2017)Huppenkothen, Younes, Ingram, Kouveliotou,
  G{\"o}{\u{g}}{\"u}{\c s}, Bachetti, Sanchez-Fernandez, Chenevez, Motta,
  van~der Klis, Granot, Gehrels, Kuulkers, Tomsick, \&
  Walton}]{Huppenkothen+17}
Huppenkothen, D., Younes, G., Ingram, A., {et~al.} 2017, ApJ, 834, 90

\bibitem[{Kluyver {et~al.}(2016)Kluyver, Ragan-Kelley, P{\'e}rez, Granger,
  Bussonnier, Frederic, Kelley, Hamrick, Grout, Corlay,
  {et~al.}}]{kluyver2016jupyter}
Kluyver, T., Ragan-Kelley, B., P{\'e}rez, F., {et~al.} 2016, in ELPUB, 87--90

\bibitem[{Leahy {et~al.}(1983)Leahy, Darbro, Elsner, Weisskopf, Kahn,
  Sutherland, \& Grindlay}]{Leahy+83}
Leahy, D.~A., Darbro, W., Elsner, R.~F., {et~al.} 1983, ApJ, 266, 160

\bibitem[{Lewin {et~al.}(1988)Lewin, van Paradijs, \& van~der Klis}]{Lewin+88}
Lewin, W. H.~G., van Paradijs, J., \& van~der Klis, M. 1988, SSRv, 46, 273

\bibitem[{Miyamoto {et~al.}(1991)Miyamoto, Kimura, Kitamoto, Dotani, \&
  Ebisawa}]{Miyamoto+91}
Miyamoto, S., Kimura, K., Kitamoto, S., Dotani, T., \& Ebisawa, K. 1991, ApJ,
  383, 784

\bibitem[{Vikhlinin {et~al.}(1994)Vikhlinin, Churazov, \&
  Gilfanov}]{Vikhlinin+94}
Vikhlinin, A., Churazov, E., \& Gilfanov, M. 1994, 287, 73

\bibitem[{Zhang {et~al.}(1995)Zhang, Jahoda, Swank, Morgan, \&
  Giles}]{Zhang+95}
Zhang, W., Jahoda, K., Swank, J.~H., Morgan, E.~H., \& Giles, A.~B. 1995, ApJ,
  449, 930

\end{thebibliography}
\end{document}

% End of file `sample61.tex'.

### 2017-10-03 notebooks/fad_correction.py

@@ -1,0 +1,93 @@
+import scipy
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+from stingray.utils import rebin_data_log
+from stingray.gti import bin_intervals_from_gtis
+from stingray.gti import cross_two_gtis
+from stingray import Powerspectrum, Crossspectrum, AveragedPowerspectrum, AveragedCrossspectrum
+from hendrics.base import r_in, r_det
+from hendrics.io import load_events
+from scipy.ndimage.filters import gaussian_filter1d
+from scipy.interpolate import UnivariateSpline
+import copy
+
+
+def _get_fourier_intv(lc, start_ind, end_ind):
+    time = lc.time[start_ind:end_ind]
+    counts = lc.counts[start_ind:end_ind]
+
+    fourier = scipy.fftpack.fft(counts)
+
+    freq = scipy.fftpack.fftfreq(len(time), lc.dt)
+    good = freq > 0
+# #     print("Bu", factor, countrate_factor, counts[:10], counts_r_out[:10], fourier[:10])
+
+    return freq[good], fourier[good], fourier[good] * np.sqrt(2 / (np.sum(counts)))
+
+
+def FAD_power_spectra(lc1, lc2, segment_size, plot=False, smoothing_alg='gauss'):
+    gti = cross_two_gtis(lc1.gti, lc2.gti)
+    lc1.gti = gti
+    lc2.gti = gti
+    lc1._apply_gtis()
+    lc2._apply_gtis()
+    summed_lc = copy.deepcopy(lc1)
+    summed_lc.counts = lc1.counts + lc2.counts
+    start_inds, end_inds = \
+        bin_intervals_from_gtis(gti, segment_size, lc1.time,
+                                dt=lc1.dt)
+    pds1 = 0
+    pds2 = 0
+    ptot = 0
+    cs = 0
+    n = 0
+
+    if plot:
+        plt.figure()
+
+    for start_ind, end_ind in zip(start_inds, end_inds):
+        freq, f1, f1_leahy = _get_fourier_intv(lc1, start_ind, end_ind)
+        freq, f2, f2_leahy = _get_fourier_intv(lc2, start_ind, end_ind)
+        freq, ftot, ftot_leahy = _get_fourier_intv(summed_lc, start_ind, end_ind)
+        
+        fourier_diff = f1_leahy - f2_leahy
+        if smoothing_alg == 'gauss':
[…]

### 2017-11-01 paper/deadtime.tex
Some modifications to start addressing referee's comments and allow further clarifications

@@
 \section{Data simulation and analysis} \label{sec:data}
+All simulated and real data sets in this paper were produced and/or analyzed with a combination of the two Python libraries \texttt{stingray}%
+\footnote{The library is under heavy development.
+    For this work we used the version identified by the hash \texttt{XXXXXX}}
+\citep{huppenkothen2016} and \texttt{HENDRICS} v.\texttt{3.0b1} \citep[formerly known as MaLTPyNT;][]{2015ascl.soft02021B}, both based on Astropy \citep{astropy2013}.
+
 \subsection{Simulated datasets}
-All simulated data sets in this paper have been produced with a combination of the two Python libraries \texttt{stingray} \citep{huppenkothen2016} and \texttt{HENDRICS} \citep[formerly known as MaLTPyNT][]{2015ascl.soft02021B}, both based on Astropy \citep{astropy2013}.
-The \texttt{stingray.simulate.Simulator} class was used to simulate light curves with a given noise profile, 
-the \texttt{stingray.Eventlist.simulate\_times()} function was used to transform the light curves into event lists using rejection sampling, 
-and finally the \texttt{hendrics.fake.filter\_for\_deadtime()} function was used to apply a non-paralyzable dead time to the simulated event lists.
-For more details on the simulated data sets, see also Section \ref{sec:correction} and the available Jupyter notebooks\footnote{\href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II}} \citep[for a description of Jupyter notebooks, see][]{kluyver2016jupyter}.
+We used the same procedure and algorithms described by \citet{Bachetti+15}, Section 4, that we briefly summarize here together with references to the methods and classes of the libraries above where these steps are implemented.
+The classes in \texttt{stingray.simulate} were used to simulate light curves with a given noise profile. 
+These classes use the \citet{timmer1995} method to create a noise-affected light curve starting from a given power spectral shape described by a powerlaw index, an \texttt{astropy} model or a list of arrays containing the frequency and power of the model spectrum.
+We then used an acceptance-rejection method to obtain simulated events from these light curves (\texttt{stingray.Eventlist.simulate\_times()}). 
+Finally, the \texttt{hendrics.fake.filter\_for\_deadtime()} function was used to apply a non-paralyzable dead time of 2.5\,ms to the simulated event lists.
+For more details on the simulated data sets, see also Section \ref{sec:correction} and the available Jupyter notebooks%
+\footnote{\href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II}} \citep[for a description of Jupyter notebooks, see][]{kluyver2016jupyter}.
 
 \subsection{Cyg X-1 \nustar dataset}
-We downloaded the observation directory of ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package [ASCL in prep.]. 
+We downloaded the observation directory of \nustar ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package (Bachetti et al., ASCL identifier requested).
 Starting from the standard cleaned science event files distributed by HEASARC, we applied a barycenter correction using the FTOOL \texttt{barycorr} shipped with HEASOFT 6.21 with the clock correction file n.
@@
 We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.
-We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and selected photons from 3 to 79 keV.
+We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and produced light curves with photons from 3 to 79 keV%
+\footnote{This procedure uses the scripts \texttt{HENreadfile}, \texttt{HENcalibrate} and \texttt{HENlcurve}, as described at\\ \href{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}}.
 
@@
 
-\section{dead time-affected white noise} \label{sec:wndeadtime}
+\section{Dead time-affected white noise} \label{sec:wndeadtime}
 
@@
 
-The correction is depicted in Figure~\ref{fig:pds}, right. 
+The correction is depicted in Figure~\ref{fig:dist}, right. 
 Starting from a heavily distorted distribution of the powers, applying the FAD correction reinstates a remarkably correct distribution of powers, following the expected $\chi^2_2$ distribution \citep{Lewin+88} very closely.
@@
 \bibliographystyle{aasjournal}
-%\bibliography{deadtime,papers3}
-\begin{thebibliography}{}
-\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-\providecommand{\url}[1]{\href{#1}{#1}}
-
-\bibitem[{{Astropy Collaboration} {et~al.}(2013){Astropy Collaboration},
-  {Robitaille}, {Tollerud}, {Greenfield}, {Droettboom}, {Bray}, {Aldcroft},
-  {Davis}, {Ginsburg}, {Price-Whelan}, {Kerzendorf}, {Conley}, {Crighton},
-  {Barbary}, {Muna}, {Ferguson}, {Grollier}, {Parikh}, {Nair}, {Unther},
-  {Deil}, {Woillez}, {Conseil}, {Kramer}, {Turner}, {Singer}, {Fox}, {Weaver},
-  {Zabalza}, {Edwards}, {Azalee Bostroem}, {Burke}, {Casey}, {Crawford},
-  {Dencheva}, {Ely}, {Jenness}, {Labrie}, {Lim}, {Pierfederici}, {Pontzen},
-  {Ptak}, {Refsdal}, {Servillat}, \& {Streicher}}]{astropy2013}
-{Astropy Collaboration}, {Robitaille}, T.~P., {Tollerud}, E.~J., {et~al.} 2013,
-  \aap, 558, A33
-
-\bibitem[{Bachetti(2015)}]{2015ascl.soft02021B}
-Bachetti, M. 2015, Astrophysics Source Code Library, ascl:1502.021
-
-\bibitem[{Bachetti {et~al.}(2015)Bachetti, Harrison, Cook, Tomsick, Schmid,
-  Grefenstette, Barret, Boggs, Christensen, Craig, Fabian, F{\"u}rst, Gandhi,
-  Hailey, Kara, Maccarone, Miller, Pottschmidt, Stern, Uttley, Walton, Wilms,
-  \& Zhang}]{Bachetti+15}
-Bachetti, M., Harrison, F.~A., Cook, R., {et~al.} 2015, ApJ, 800, 109
-
-\bibitem[{Barret \& Vaughan(2012)}]{Barret+12}
-Barret, D., \& Vaughan, S. 2012, ApJ, 746, 131
-
-\bibitem[{Belloni \& Hasinger(1990)}]{BelloniHasinger90}
-Belloni, T., \& Hasinger, G. 1990, A{\&}A, 230, 103
-
-\bibitem[{Bowyer {et~al.}(1965)Bowyer, Byram, Chubb, \& Friedman}]{Bowyer+65}
-Bowyer, S., Byram, E.~T., Chubb, T.~A., \& Friedman, H. 1965, Astronomical
-  Observations from Space Vehicles, 23, 227
-
-\bibitem[{Gilfanov {et~al.}(2000)Gilfanov, Churazov, \&
-  Revnivtsev}]{Gilfanov+00}
-Gilfanov, M., Churazov, E., \& Revnivtsev, M. 2000, MNRAS, 316, 923
-
-\bibitem[{Grinberg {et~al.}(2013)Grinberg, Hell, Pottschmidt, B{\"o}ck, Nowak,
-  Rodriguez, Bodaghee, Cadolle~Bel, Case, Hanke, K{\"u}hnel, Markoff, Pooley,
-  Rothschild, Tomsick, Wilson-Hodge, \& Wilms}]{Grinberg+13}
-Grinberg, V., Hell, N., Pottschmidt, K., {et~al.} 2013, 554, 88
-
-\bibitem[{{Huppenkothen} {et~al.}(2016){Huppenkothen}, {Bachetti}, {Stevens},
-  {Migliari}, \& {Balm}}]{huppenkothen2016}
-{Huppenkothen}, D., {Bachetti}, M., {Stevens}, A.~L., {Migliari}, S., \&
-  {Balm}, P. 2016, {Stingray: Spectral-timing software}, Astrophysics Source
-  Code Library, , , ascl:1608.001
-
-\bibitem[{Huppenkothen {et~al.}(2017)Huppenkothen, Younes, Ingram, Kouveliotou,
-  G{\"o}{\u{g}}{\"u}{\c s}, Bachetti, Sanchez-Fernandez, Chenevez, Motta,
-  van~der Klis, Granot, Gehrels, Kuulkers, Tomsick, \&
-  Walton}]{Huppenkothen+17}
-Huppenkothen, D., Younes, G., Ingram, A., {et~al.} 2017, ApJ, 834, 90
-
-\bibitem[{Kluyver {et~al.}(2016)Kluyver, Ragan-Kelley, P{\'e}rez, Granger,
-  Bussonnier, Frederic, Kelley, Hamrick, Grout, Corlay,
-  {et~al.}}]{kluyver2016jupyter}
-Kluyver, T., Ragan-Kelley, B., P{\'e}rez, F., {et~al.} 2016, in ELPUB, 87--90
-
-\bibitem[{Leahy {et~al.}(1983)Leahy, Darbro, Elsner, Weisskopf, Kahn,
-  Sutherland, \& Grindlay}]{Leahy+83}
-Leahy, D.~A., Darbro, W., Elsner, R.~F., {et~al.} 1983, ApJ, 266, 160
-
-\bibitem[{Lewin {et~al.}(1988)Lewin, van Paradijs, \& van~der Klis}]{Lewin+88}
-Lewin, W. H.~G., van Paradijs, J., \& van~der Klis, M. 1988, SSRv, 46, 273
-
-\bibitem[{Miyamoto {et~al.}(1991)Miyamoto, Kimura, Kitamoto, Dotani, \&
-  Ebisawa}]{Miyamoto+91}
-Miyamoto, S., Kimura, K., Kitamoto, S., Dotani, T., \& Ebisawa, K. 1991, ApJ,
-  383, 784
-
-\bibitem[{Vikhlinin {et~al.}(1994)Vikhlinin, Churazov, \&
-  Gilfanov}]{Vikhlinin+94}
-Vikhlinin, A., Churazov, E., \& Gilfanov, M. 1994, 287, 73
-
-\bibitem[{Zhang {et~al.}(1995)Zhang, Jahoda, Swank, Morgan, \&
-  Giles}]{Zhang+95}
-Zhang, W., Jahoda, K., Swank, J.~H., Morgan, E.~H., \& Giles, A.~B. 1995, ApJ,
-  449, 930
-
-\end{thebibliography}
+\bibliography{deadtime,papers3}
+%\begin{thebibliography}{}
+%\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+%\providecommand{\url}[1]{\href{#1}{#1}}
+%
+%\bibitem[{{Astropy Collaboration} {et~al.}(2013){Astropy Collaboration},
+%  {Robitaille}, {Tollerud}, {Greenfield}, {Droettboom}, {Bray}, {Aldcroft},
+%  {Davis}, {Ginsburg}, {Price-Whelan}, {Kerzendorf}, {Conley}, {Crighton},
+%  {Barbary}, {Muna}, {Ferguson}, {Grollier}, {Parikh}, {Nair}, {Unther},
+%  {Deil}, {Woillez}, {Conseil}, {Kramer}, {Turner}, {Singer}, {Fox}, {Weaver},
+%  {Zabalza}, {Edwards}, {Azalee Bostroem}, {Burke}, {Casey}, {Crawford},
+%  {Dencheva}, {Ely}, {Jenness}, {Labrie}, {Lim}, {Pierfederici}, {Pontzen},
+%  {Ptak}, {Refsdal}, {Servillat}, \& {Streicher}}]{astropy2013}
+%{Astropy Collaboration}, {Robitaille}, T.~P., {Tollerud}, E.~J., {et~al.} 2013,
+%  \aap, 558, A33
+%
+%\bibitem[{Bachetti(2015)}]{2015ascl.soft02021B}
+%Bachetti, M. 2015, Astrophysics Source Code Library, ascl:1502.021
+%
+%\bibitem[{Bachetti {et~al.}(2015)Bachetti, Harrison, Cook, Tomsick, Schmid,
+%  Grefenstette, Barret, Boggs, Christensen, Craig, Fabian, F{\"u}rst, Gandhi,
+%  Hailey, Kara, Maccarone, Miller, Pottschmidt, Stern, Uttley, Walton, Wilms,
+%  \& Zhang}]{Bachetti+15}
+%Bachetti, M., Harrison, F.~A., Cook, R., {et~al.} 2015, ApJ, 800, 109
+%
+%\bibitem[{Barret \& Vaughan(2012)}]{Barret+12}
+%Barret, D., \& Vaughan, S. 2012, ApJ, 746, 131
+%
+%\bibitem[{Belloni \& Hasinger(1990)}]{BelloniHasinger90}
+%Belloni, T., \& Hasinger, G. 1990, A{\&}A, 230, 103
+%
+%\bibitem[{Bowyer {et~al.}(1965)Bowyer, Byram, Chubb, \& Friedman}]{Bowyer+65}
+%Bowyer, S., Byram, E.~T., Chubb, T.~A., \& Friedman, H. 1965, Astronomical
+%  Observations from Space Vehicles, 23, 227
+%
+%\bibitem[{Gilfanov {et~al.}(2000)Gilfanov, Churazov, \&
+%  Revnivtsev}]{Gilfanov+00}
+%Gilfanov, M., Churazov, E., \& Revnivtsev, M. 2000, MNRAS, 316, 923
+%
+%\bibitem[{Grinberg {et~al.}(2013)Grinberg, Hell, Pottschmidt, B{\"o}ck, Nowak,
+%  Rodriguez, Bodaghee, Cadolle~Bel, Case, Hanke, K{\"u}hnel, Markoff, Pooley,
+%  Rothschild, Tomsick, Wilson-Hodge, \& Wilms}]{Grinberg+13}
+%Grinberg, V., Hell, N., Pottschmidt, K., {et~al.} 2013, 554, 88
+%
+%\bibitem[{{Huppenkothen} {et~al.}(2016){Huppenkothen}, {Bachetti}, {Stevens},
+%  {Migliari}, \& {Balm}}]{huppenkothen2016}
+%{Huppenkothen}, D., {Bachetti}, M., {Stevens}, A.~L., {Migliari}, S., \&
+%  {Balm}, P. 2016, {Stingray: Spectral-timing software}, Astrophysics Source
+%  Code Library, , , ascl:1608.001
+%
+%\bibitem[{Huppenkothen {et~al.}(2017)Huppenkothen, Younes, Ingram, Kouveliotou,
+%  G{\"o}{\u{g}}{\"u}{\c s}, Bachetti, Sanchez-Fernandez, Chenevez, Motta,
+%  van~der Klis, Granot, Gehrels, Kuulkers, Tomsick, \&
+%  Walton}]{Huppenkothen+17}
+%Huppenkothen, D., Younes, G., Ingram, A., {et~al.} 2017, ApJ, 834, 90
+%
+%\bibitem[{Kluyver {et~al.}(2016)Kluyver, Ragan-Kelley, P{\'e}rez, Granger,
+%  Bussonnier, Frederic, Kelley, Hamrick, Grout, Corlay,
+%  {et~al.}}]{kluyver2016jupyter}
+%Kluyver, T., Ragan-Kelley, B., P{\'e}rez, F., {et~al.} 2016, in ELPUB, 87--90
+%
+%\bibitem[{Leahy {et~al.}(1983)Leahy, Darbro, Elsner, Weisskopf, Kahn,
+%  Sutherland, \& Grindlay}]{Leahy+83}
+%Leahy, D.~A., Darbro, W., Elsner, R.~F., {et~al.} 1983, ApJ, 266, 160
+%
+%\bibitem[{Lewin {et~al.}(1988)Lewin, van Paradijs, \& van~der Klis}]{Lewin+88}
+%Lewin, W. H.~G., van Paradijs, J., \& van~der Klis, M. 1988, SSRv, 46, 273
+%
+%\bibitem[{Miyamoto {et~al.}(1991)Miyamoto, Kimura, Kitamoto, Dotani, \&
+%  Ebisawa}]{Miyamoto+91}
+%Miyamoto, S., Kimura, K., Kitamoto, S., Dotani, T., \& Ebisawa, K. 1991, ApJ,
+%  383, 784
+%
+%\bibitem[{Vikhlinin {et~al.}(1994)Vikhlinin, Churazov, \&
+%  Gilfanov}]{Vikhlinin+94}
+%Vikhlinin, A., Churazov, E., \& Gilfanov, M. 1994, 287, 73
+%
+%\bibitem[{Zhang {et~al.}(1995)Zhang, Jahoda, Swank, Morgan, \&
+%  Giles}]{Zhang+95}
+%Zhang, W., Jahoda, K., Swank, J.~H., Morgan, E.~H., \& Giles, A.~B. 1995, ApJ,
+%  449, 930
+%
+%\end{thebibliography}
 \end{document}

### 2017-11-06 paper/deadtime.tex
Various improvements to data analysis section

@@
 \subsection{Cyg X-1 \nustar dataset}
+We tested the method also on real data of several bright sources observed by \nustar.
+As an example, we report here one such test done on \nustar data of the black hole binary Cyg~X-1 together with the steps to reproduce our analysis, using the linked Jupyter notebook if needed.
 We downloaded the observation directory of \nustar ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package (Bachetti et al., ASCL identifier requested).
+Equivalently, this download can be done using the online tools provided by HEASARC (e.g. \texttt{xamin}).
 Starting from the standard cleaned science event files distributed by HEASARC, we applied a barycenter correction using the FTOOL \texttt{barycorr} shipped with HEASOFT 6.21 with the clock correction file n.
 71 from the \nustar CALDB.
-We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.
-We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and produced light curves with photons from 3 to 79 keV%
+We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.%
+\footnote{To use the method on different sources, it is sufficient to download a different ObsID and change the region file containing the position of the source}.
+We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and produced light curves with photons from 3 to 79 keV and binned with uniform time bins of 1/4096$\sim2.44\cdot10^{-4}$\,sec%
 \footnote{This procedure uses the scripts \texttt{HENreadfile}, \texttt{HENcalibrate} and \texttt{HENlcurve}, as described at\\ \href{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}}.
@@
 A_{xj} &=& A_{xsj} + A_{xdj} + A_{xnj} \nonumber \\
-B_{xj} &=& B_{xsj} + A_{xdj} + B_{xnj} \, ,
+B_{xj} &=& B_{xsj} + B_{xdj} + B_{xnj} \, ,
 \end{eqnarray}

### 2017-12-05 notebooks/plot_all_trials.py
Correct calculation of rms

@@ -45,8 +45,9 @@ def pairplot(file, toler_d_clean=0.5, filters={'channel_ratio': [0.8, 1.2]}):
         good_clean = good_clean & (results[key] > val[0])&(results[key] < val[1])
     meanrate = results['incident_rate'] // 100 * 100 + 50
     results["rate"] = meanrate
+    results["median_ratio"] = results['median'] / results['clean_median']
     vars_unfilt = ['channel_ratio', 'frequency', 'Frac_rms',
-            'CS', 'PDS 1', 'PDStot', 'slope', 'median', 'clean_median']
+            'CS', 'PDS 1', 'PDStot', 'slope', 'median_ratio']
     vars = []
     for v in vars_unfilt:
         if v in results:
@@ -261,7 +262,7 @@ def fit_pds_quantities_vs_rms(file, toler_d_clean=0.01,
     ax1.set_xlabel('Frac_rms')
     ax1.set_ylabel('Slope of '+ quantity)
     
-    print(par[0])
+    retval = par[0]
     ax3.scatter(frac_rmss[good], qs[good], c=colors[good], cmap='viridis')
     ax3.set_ylim([np.min(qs), np.max(qs)])
     par, pcov = curve_fit(line, frac_rmss[good], qs[good])
@@ -272,46 +273,62 @@ def fit_pds_quantities_vs_rms(file, toler_d_clean=0.01,
     ax3.set_xlabel('Frac_rms')
     ax3.set_ylabel('Intercept of '+ quantity)
 
-    print(par)
     cmap = mpl.cm.viridis
     norm = mpl.colors.Normalize(vmin=np.min(results['Frac_rms']),
                                 vmax=np.max(results['Frac_rms']))
 
     cb = mpl.colorbar.ColorbarBase(ax2, cmap=cmap, norm=norm)
     cb.set_label('Fractional rms')
+    return retval
 
 if __name__ == '__main__':
     import sys
     import time
+    from hendrics.base import r_in, r_det
+    import warnings
+    warnings.filterwarnings('ignore')
     infile = sys.argv[1]
 
     toler_d_clean = 0.01
-    plt.ion()
-    post_filters = {'channel_ratio': [0.7, 1.5]} 
-    filters ={}# {'median': [0, 0.03]}
-    while True:
+#    plt.ion()
+    post_filters = {'channel_ratio': [0.7, 1.5]}
+    for f in np.logspace(1, np.log10(500), 5):
+        filters ={'frequency': [f, f + 30]}
[…]

### 2017-12-08 paper/deadtime.tex
Draft significant changes, many new figures

--- 2017-10-03 paper/deadtime.tex
@@
 
-In this Letter we suggest a new, powerful method to normalize cospectra and, with some caveats, even power density spectra.
+In this Letter we suggest a new, powerful method to normalize deadtime-affected cospectra and power density spectra.
 Our approach uses the difference of the Fourier amplitudes from two independent detectors to characterize and filter out the effect of dead time.
-This method is crucially important for the accurate modelling of periodograms derived from instruments affected by dead time on board current missions like \nustar and \astrosat, but also future missions such as \ixpe.
+This method is crucially important for the accurate modeling of periodograms derived from instruments affected by dead time on board current missions like \nustar and \astrosat, but also future missions such as \ixpe.
 \end{abstract}
@@
 %% to the KEY in the \bibitem in the reference list below.
+
+%%%%%%%%%%%%%%%%%%%%%%%% SECTION 1 %%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%% SECTION 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Data simulation and analysis} \label{sec:data}
+All simulated and real data sets in this paper were produced and/or analyzed with a combination of the two Python libraries \texttt{stingray}%
+\footnote{The library is under heavy development.
+    For this work we used the version identified by the hash \texttt{XXXXXX}}
+\citep{huppenkothen2016} and \texttt{HENDRICS} v.\texttt{3.0b1} \citep[formerly known as MaLTPyNT;][]{2015ascl.soft02021B}, both based on Astropy \citep{astropy2013}.
+
 \subsection{Simulated datasets}
-All simulated data sets in this paper have been produced with a combination of the two Python libraries \texttt{stingray} \citep{huppenkothen2016} and \texttt{HENDRICS} \citep[formerly known as MaLTPyNT][]{2015ascl.soft02021B}, both based on Astropy \citep{astropy2013}.
-The \texttt{stingray.simulate.Simulator} class was used to simulate light curves with a given noise profile, 
-the \texttt{stingray.Eventlist.simulate\_times()} function was used to transform the light curves into event lists using rejection sampling, 
-and finally the \texttt{hendrics.fake.filter\_for\_deadtime()} function was used to apply a non-paralyzable dead time to the simulated event lists.
-For more details on the simulated data sets, see also Section \ref{sec:correction} and the available Jupyter notebooks\footnote{\href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II}} \citep[for a description of Jupyter notebooks, see][]{kluyver2016jupyter}.
+We used the same procedure and algorithms described by \citet{Bachetti+15}, Section 4, that we briefly summarize here together with references to the methods and classes of the libraries above where these steps are implemented.
+The classes in \texttt{stingray.simulate} were used to simulate light curves with a given noise profile. 
+These classes use the \citet{timmer1995} method to create a noise-affected light curve starting from a given power spectral shape described by a powerlaw index, an \texttt{astropy} model or a list of arrays containing the frequency and power of the model spectrum.
+We first created the light curves and then used an acceptance-rejection method to obtain simulated events from these light curves (\texttt{stingray.Eventlist.simulate\_times()}). 
+This step needs to be done carefully: if the initial light curves are done directly with the wanted count rate, they contain significant random noise, and the process for the creation of events amplifies this noise (because it further creates a random variate on the top of the local count rate, which is varying randomly already) producing a non-Poissonian final light curve.
+Therefore, we initially used the \citet{timmer1995} method to get light curves with a very high count rate - a way to reduce the relative importance of the Poisson noise because of the square root involved - then renormalized the light curves to the wanted (lower) count rate and rms and finally used these light curves to simulate event lists.
+Finally, the \texttt{hendrics.fake.filter\_for\_deadtime()} function was used to apply a non-paralyzable dead time of 2.5\,ms to the simulated event lists.
+For more details on the simulated data sets, see also Section \ref{sec:correction} and the available Jupyter notebooks%
+\footnote{\href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II}} \citep[for a description of Jupyter notebooks, see][]{kluyver2016jupyter}.
 
 \subsection{Cyg X-1 \nustar dataset}
-We downloaded the observation directory of ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package [ASCL in prep.]. 
+We tested the method also on real data of several bright sources observed by \nustar.
+As an example, we report here one such test done on \nustar data of the black hole binary Cyg~X-1 together with the steps to reproduce our analysis, using the linked Jupyter notebook if needed.
+We downloaded the observation directory of \nustar ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package (Bachetti et al., ASCL identifier requested).
+Equivalently, this download can be done using the online tools provided by HEASARC (e.g. \texttt{xamin}).
 Starting from the standard cleaned science event files distributed by HEASARC, we applied a barycenter correction using the FTOOL \texttt{barycorr} shipped with HEASOFT 6.21 with the clock correction file n.
 71 from the \nustar CALDB.
-We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.
-We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and selected photons from 3 to 79 keV.
+We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.%
+\footnote{To use the method on different sources, it is sufficient to download a different ObsID and change the region file containing the position of the source}.
+We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and produced light curves with photons from 3 to 79 keV and binned with uniform time bins of 1/4096$\sim2.44\cdot10^{-4}$\,sec%
+\footnote{This procedure uses the scripts \texttt{HENreadfile}, \texttt{HENcalibrate} and \texttt{HENlcurve}, as described at\\ \href{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}}.
+
+%%%%%%%%%%%%%%%%%%%%%%%% SECTION 3 %%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{figure*}
-\plottwo{imgs/rn_fourierdiff}{imgs/rn_fourierdiff_dt}
-\caption{Real Fourier amplitudes obtained by single light curves (top panels) and difference between two realizations of the same source light curve (bottom) in two cases: (Left) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (Right) no red noise and strong dead time, calculated over many 5\,s segments of the light curve.
+\gridline{\fig{imgs/rn_fourierdiff.eps}{0.33\textwidth}{(a)}
+	\fig{imgs/wn_fourierdiff.eps}{0.33\textwidth}{(b)}
+	\fig{imgs/fourier_vs_diff_dt.eps}{0.33\textwidth}{(c)}}
+
+\caption{(a) and (b): Real Fourier amplitudes obtained by single light curves (top panels) and difference between two realizations of the same source light curve (bottom) in two cases: (a) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (b) no red noise and strong dead time, calculated over many 5\,s segments of the light curve.
 The choice of different segment length reflects the range of frequencies we want to highlight in the two cases.
@@
 As expected, in the first case, the Fourier amplitude follows a power law curve, while the standard deviation of the difference is remarkably stable at all frequencies, as expected by the fact that the Poisson white noise is independent of frequency.
-In the second case, instead, dead time is frequency dependent and white noise is also affected, so that the difference of Fourier amplitudes is modulated as well.}
+In the second case, instead, dead time is frequency dependent and white noise is also affected, so that the difference of Fourier amplitudes is modulated as well.
+(c) Scatter distribution of the absolute values of dead time-affected Fourier amplitudes versus the difference of Fourier amplitudes for case (b): their relation is clearly linear, with a factor $1/\sqrt{2}$.
+}
 \label{fig:fourierdiff}
@@
 
-\section{dead time-affected white noise} \label{sec:wndeadtime}
+%%%%%%%%%%%%%%%%%%%%%%%% SECTION 4 %%%%%%%%%%%%%%%%%%%%%%%%%%
 
+\section{Dead time-affected white noise} \label{sec:wndeadtime}
+
+%\begin{figure*}
+%\gridline{\fig{imgs/pds_pdf}{0.5\textwidth}{(b)}
+%          \fig{imgs/cosp_pdf}{0.5\textwidth}{(c)}}
+%
+%\caption{(b) Distribution of powers in the periodogram, before the FAD correction and after, shown as a histogram.
+%After correction, the powers follow remarkably well the expected $\chi^2_2$ distribution.
+%(c) Same, for the cospectrum.
+%The correct Laplace distribution is followed after FAD correction}
+%\label{fig:dist}
+%\end{figure*}
 \begin{figure*}
-\gridline{\fig{imgs/fourier_vs_diff_dt}{0.3\textwidth}{(a)}
-          \fig{imgs/pds_pdf}{0.3\textwidth}{(b)}
-          \fig{imgs/cosp_pdf}{0.3\textwidth}{(c)}}
-
-\caption{(a) Scatter distribution of dead time-affected Fourier amplitudes versus the difference of Fourier amplitudes:
-their relation is clearly linear, with a factor $1/\sqrt{2}$. 
-(b) Distribution of powers in the periodogram, before the FAD correction and after, shown as a histogram.
-After correction, the powers follow remarkably well the expected $\chi^2_2$ distribution.
-(c) Same, for the cospectrum.
-The correct Laplace distribution is followed after FAD correction}
+\gridline{\fig{imgs/before_and_after.eps}{\textwidth}{(a)}}
+\gridline{\fig{imgs/pds_pdf.pdf}{\textwidth}{(b)}}
+\caption{(Top) Periodogram and cospectrum, before and after FAD correction, for a pure white noise light curve. 
+The deadtime-driven distortion of the white noise level in the periodogram, and the frequency-dependent modulation of the rms in both spectra, disappear after applying the FAD correction. 
+Spectra were calculated over 2-sec intervals and averaged, to decrease the scatter and highlight the distortion of powers.
+(Bottom) PDF of non-averaged powers in the cospectrum (red) and the periodogram (black), before the FAD correction and after, shown as a histogram. 
+After correction, the powers follow remarkably well the expected Laplace and $\chi^2_2$ distributions respectively, as highlighted by the overplotted probability density functions (PDF).}
 \label{fig:dist}
 \end{figure*}
-
 Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec and a dead time of 2.5 ms, as we would expect from two identical detectors observing the same stable X-ray source.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%% SECTION 5 %%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Testing the FAD correction on simulated data} \label{sec:correction}
 
+%\begin{figure*}
+%    \gridline{\fig{imgs/rednoise_rebin}{0.33\textwidth}{(a)}
+%        \fig{imgs/rednoise_rebin_zoom}{0.33\textwidth}{(b)}
+%        \fig{imgs/simu_rebin_log}{0.33\textwidth}{(c)}}
+%    \gridline{\fig{imgs/cygx1_soft_nustar_2_rebin}{0.33\textwidth}{(d)}
+%        \fig{imgs/cygx1_soft_nustar_2_rebin_zoom}{0.33\textwidth}{(e)}
+%        \fig{imgs/cygx1_soft_nustar_2_rebin_log}{0.33\textwidth}{(f)}}  
+%    \caption{
+%        Top: simulated dataset with two strong and broad Lorentzian components, incident count rate $\sim$810 ct/s, and total rms $\sim$15\% (``detected'' after dead time: $\sim$270 and $\sim$4\% resp.).
+%        Bottom: \nustar observation of the black hole candidate Cyg X-1. 
+%        (a) and (d): comparison of the distortion of the dead time-affected periodogram with the FAD-corrected periodogram, the dead time-affected and the FAD-corrected cospectrum.
+The spectra have been shifted vertically for clarity.
+%        The shape of the uncorrected periodogram is clearly distorted by dead time. 
+%        (b) and (e): the FAD correction successfully flattens the periodogram, but there remain a few intervals where the baseline is imperfect, indicated by the arrows.
+%        This is due to the flux mismatch between the two detectors (see \sref{sec:realdata}).
+%        The cospectral powers are always distributed around zero, but dead time changes the width of the resulting distribution, and the FAD correction attenuates the width of the distribution back to the width expected in the dead time-free case (see e.g.\ (b) for a striking case).
+%        Moreover, the source-dominated part of the spectrum also receives a boost, which corrects precisely the measured rms of the source from the ``hushing'' effect of dead time.
+%        (c) and (f): FAD-corrected periodogram and cospectra, plotted in $\mathrm{(rms/mean)}^2$ normalization and fitted with two Lorentzian curves (c) and with an exponential cutoff power law (f).
+%        The additional gain coming from the FAD normalization is evident by the comparison with the uncorrected cospectrum.}
+%    \label{fig:pds}
+%\end{figure*}
 \begin{figure*}
-    \gridline{\fig{imgs/rednoise_rebin}{0.33\textwidth}{(a)}
-        \fig{imgs/rednoise_rebin_zoom}{0.33\textwidth}{(b)}
-        \fig{imgs/simu_rebin_log}{0.33\textwidth}{(c)}}
-    \gridline{\fig{imgs/cygx1_soft_nustar_2_rebin}{0.33\textwidth}{(d)}
-        \fig{imgs/cygx1_soft_nustar_2_rebin_zoom}{0.33\textwidth}{(e)}
-        \fig{imgs/cygx1_soft_nustar_2_rebin_log}{0.33\textwidth}{(f)}}  
-    \caption{
-        Top: simulated dataset with two strong and broad Lorentzian components, incident count rate $\sim$810 ct/s, and total rms $\sim$15\% (``detected'' after dead time: $\sim$270 and $\sim$4\% resp.).
-        Bottom: \nustar observation of the black hole candidate Cyg X-1. 
-        (a) and (d): comparison of the distortion of the dead time-affected periodogram with the FAD-corrected periodogram, the dead time-affected and the FAD-corrected cospectrum.
-The spectra have been shifted vertically for clarity.
-        The shape of the uncorrected periodogram is clearly distorted by dead time. 
-        (b) and (e): the FAD correction successfully flattens the periodogram, but there remain a few intervals where the baseline is imperfect, indicated by the arrows.
-        This is due to the flux mismatch between the two detectors (see \sref{sec:realdata}).
-        The cospectral powers are always distributed around zero, but dead time changes the width of the resulting distribution, and the FAD correction attenuates the width of the distribution back to the width expected in the dead time-free case (see e.g.\ (b) for a striking case).
-        Moreover, the source-dominated part of the spectrum also receives a boost, which corrects precisely the measured rms of the source from the ``hushing'' effect of dead time.
-        (c) and (f): FAD-corrected periodogram and cospectra, plotted in $\mathrm{(rms/mean)}^2$ normalization and fitted with two Lorentzian curves (c) and with an exponential cutoff power law (f).
-        The additional gain coming from the FAD normalization is evident by the comparison with the uncorrected cospectrum.}
+    \plotone{imgs/four_qpos.eps}
+    \caption{Periodograms and cospectra from a simulation with four Lorentzian features (at 50, 200, 300 and 400 Hz) with 40-Hz full with at half maximum (FWHM). 
+    We plotted and fitted periodograms and cospectra before and after applying the dead time filter
+    The total rms before dead time was 40\% and the incident photon flux 400 ct/s. 
+    After applying a dead time of 2.5 ms like in \nustar, the ``detected'' photon flux decreased to $\sim$200 ct/s as expected. 
+    As can be seen from the best-fit curves, there is no significant difference between FAD-normalized and deadtime-free periodograms and cospectra.
+    For comparison, we also plot the cospectrum without FAD (pink), showing very different amplitudes for the four Lorentzians, due to dead time.
+    }
     \label{fig:pds}
@@
 We are now ready to verify the last step: is the FAD-corrected power spectrum equivalent (albeit with some loss of sensitivity due to the lower number of photons) to the dead time-free power spectrum?
-To test this, we produced a number of different synthetic datasets, containing different combinations of QPOs and broadband noise components. 
-We first calculated the periodogram of the dead time-free data.
-Then, we applied a dead time filter and calculated the power density spectrum and the cospectrum. 
-At this point, we applied the FAD correction, as follows:
+To test this, we produced a number of different synthetic datasets as explained in Section~\ref{sec:wndeadtime}, containing different combinations of QPOs and broadband noise components. 
+We first calculated the periodogram and cospectrum of the dead time-free data, averaged over 128-s intervals.
+Then, we applied a dead time filter to the event list and applied the FAD correction, as follows:
 \begin{enumerate}
@@
 	\begin{itemize}
-	\item calculate the Fourier transform of each channel separately, and then of the summed channels;
+	\item calculate the Fourier transform of each channel separately, and then of the summed channels (hereafter the \textit{total-intensity} light curve);
 	\item multiply the Fourier amplitudes by $\sqrt{2/N_{ph}}$ in order to obtain Leahy-normalized periodograms;
-	\item subtract the Fourier amplitudes of the two channels between them and obtain the Fourier Amplitude Difference (FAD);
+	\item subtract the Fourier amplitudes of the two channels between them, \textit{take the absolute value}, and obtain this way the Fourier Amplitude Differences (FAD);
 	\item \textit{smooth} the FAD using a Gaussian-window interpolation with a width of 1-2 seconds;
-	\item use the separated single-channel and summed Fourier amplitudes to calculate the periodograms;
+	\item use the separated single-channel and total-intensity Fourier amplitudes to calculate the periodograms;
 	\item use the Fourier amplitudes from channels A and B to calculate the cospectrum;
@@
 
-All spectra were then expressed in fractional rms \citep{BelloniHasinger90,Miyamoto+91} normalization, where the integral of the fitted spectral components returns directly its fractional rms.
-In the rms normalization, the values of each point of the periodogram should be consistent between the dead time-free and the FAD-corrected periodograms.
+All spectra were then expressed in fractional rms \citep{BelloniHasinger90,Miyamoto+91} normalization, where the integral of the fitted spectral components over the frequency returns directly its fractional rms.
+In the rms normalization, the values of each point of the periodogram, after white noise subtraction, should be consistent between the dead time-free and the FAD-corrected periodograms.
 We first checked visually that the spectra (white-noise subtracted in the case of periodograms) after FAD correction were all consistent with the dead time-free periodogram. 
-Then, we fitted all spectra with the model which produced the simulated data and checked that the values were always consistent with the input model parameters and the fit on the dead time-free periodogram.
-Finally, we verified that the total rms of the FAD-corrected spectra was always consistent with the total rms of the dead time-affected cospectrum \textit{times the ratio between incident and detected photons}, using the count rates before and after applying the dead time filter.
-To calculate this rms, we fitted the spectra with two Lorentzian components, and used their amplitude in the calculation.
-In this normalization, the amplitude of a Lorentzian gives the total rms squared of the component.
+Then, we fitted all spectra with the model which produced the simulated data and checked if the values were consistent with the input model parameters and the fit on the dead time-free periodogram.
+Finally, we verified if \textit{at low frequencies} the total rms of the FAD-corrected spectra was consistent with the total rms of the dead time-affected cospectrum \textit{times the ratio between incident and detected photons}, using the count rates before and after applying the dead time filter.
+To calculate this rms, we fitted the spectra with two Lorentzian components, and integrated the model over the full frequency range.
 For periodograms, the model included also a constant offset to account for the white noise level.
-An example of this analysis is shown in Figure~\ref{fig:pds} (upper panel).
+An example of this analysis is shown in Figure~\ref{fig:pds}.
 
-The simulations show that the shape of the periodogram is precisely corrected by the FAD procedure \textit{if} the input light curves have the same count rate. 
-However, in real life the two detectors can receive slightly different signals due to slightly different responses, the presence of gaps inside the PSF, etc.
-Simulating datasets with slightly different light curve mean rates in the two channels, we indeed find that the performance of the FAD correction degrades.
-The degradation is higher for higher count rates and higher difference between the two channels. 
-Since the exact degradation is dependent on the shape of the periodograms, we recommend to FAD-correct both the periodogram and the cospectrum, and verify visually that the white-noise subtracted periodogram and the cospectrum are consistent.
-For example, look for bumps or valleys in the white noise-subtracted periodogram that are not present in the cospectrum, and
-trust the additional signal to noise of the periodogram only in the regions where the two are consistent.
+\section{Caveats}\label{sec:caveat}
+The simulations show that the shape of the periodogram is precisely corrected by the FAD procedure \textit{if the input light curves have the same count rate} and \textit{for values of the input count rate and rms that are not too extreme}.
+The first caveat turns out to be an issue only for the single-channel periodogram. 
+At high count rates, single-channel periodograms are corrected very well only if the two channels have very similar count rates, with the requirement being unsurprisingly stricter and stricter as the count rate increases.
+However, we find that the total-intensity periodogram and the cospectrum remains well corrected by the FAD even if the count rate in the two channels differs by 30\%, for any reasonable count rate.
+Therefore, we recommend to use the FAD very carefully with single-channel periodograms, which should not be an issue given that the total-intensity periodogram is more sensitive and more convenient to use anyway.
+A comparison with the cospectrum, that is not affected by white noise distortions, is always recommended.
+
+The second caveat needs some attention. 
+We find that the FAD correction consistently overestimates the integrated rms when the count rate and rms are \textit{both} very high, \textit{independently from the frequency}.
+This latter feature is less intuitive, because we would expect that this overestimation should somehow be more relevant where the correction is stronger, while this is not the case.
+But for this very reason, it is somewhat easier to account for this through simulations, without having to make further risky frequency-dependent corrections to the rms.
+At standard count rates and fractional rms for bright black hole binaries, $\sim$200 ct/s and 30\% rms, the difference is below 5\%. 
+However, it increases \textit{linearly} with the count rate and \textit{quadratically} with rms.
+A practical way to estimate this effect during analysis is to apply the FAD, obtain a best fit model, calculate the rms, then use the codes we shared with the Jupyter notebooks to simulate a number of realizations of the code, evaluating what is the amount of overestimation involved.
+
+%%%%%%%%%%%%%%%%%%%%%%%% SECTION 6 %%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 (using the standard non-paralyzable dead time formula, where \deadt is dead time) which is the drop of rms expected from the effect of dead time \citep{Bachetti+15}.
+
+%%%%%%%%%%%%%%%%%%%%%%%% SECTION 7 %%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2017-12-10 paper/deadtime.tex
Complete draft of the revised paper - MB

@@
 
-\newcommand{\given}{\ensuremath{\,|\,}}
-\newcommand{\dd}{\ensuremath{\mathrm{d}}}
-\newcommand{\counts}{\ensuremath{y}}
-\newcommand{\pars}{\ensuremath{\theta}}
-\newcommand{\mean}{\ensuremath{\lambda}}
-\newcommand{\likelihood}{\ensuremath{{\mathcal L}}}
-\newcommand{\Poisson}{\ensuremath{{\mathcal P}}}
-\newcommand{\Uniform}{\ensuremath{{\mathcal U}}}
+\newcommand{\given}{\ensuremath{\,|\,}\xspace}
+\newcommand{\dd}{\ensuremath{\mathrm{d}}\xspace}
+\newcommand{\counts}{\ensuremath{y}\xspace}
+\newcommand{\rms}{\ensuremath{\mathrm{r.m.s.}}\xspace}
+\newcommand{\pars}{\ensuremath{\theta}\xspace}
+\newcommand{\mean}{\ensuremath{\lambda}\xspace}
+\newcommand{\likelihood}{\ensuremath{{\mathcal L}}\xspace}
+\newcommand{\Poisson}{\ensuremath{{\mathcal P}}\xspace}
+\newcommand{\Uniform}{\ensuremath{{\mathcal U}}\xspace}
 
-\newcommand{\Normal}{\ensuremath{{\mathcal N}}}
-\newcommand{\bg}{\ensuremath{\mathrm{bg}}}
-\newcommand{\word}{\ensuremath{\phi}}
+\newcommand{\Normal}{\ensuremath{{\mathcal N}}\xspace}
+\newcommand{\bg}{\ensuremath{\mathrm{bg}}\xspace}
+\newcommand{\word}{\ensuremath{\phi}\xspace}
 
@@
 this is not the case for others such as \nustar, where the dead time is non-constant and long ($\sim$2.5\,ms).
-\citet{Bachetti+15} suggested the cospectrum obtained from light curves of independent detectors within the same instrument as a possible way out, but this solution has always only been a partial one: the measured rms was still affected by dead time, because the width of the power distribution of the cospectrum was modulated by dead time in a frequency-dependent way.
+\citet{Bachetti+15} suggested the cospectrum obtained from light curves of independent detectors within the same instrument as a possible way out, but this solution has always only been a partial one: the measured \rms was still affected by dead time, because the width of the power distribution of the cospectrum was modulated by dead time in a frequency-dependent way.
 
@@
 Whereas a noise cospectrum in the absence of dead time would follow a Laplace distribution (Huppenkothen and Bachetti, sub.),
-dead time affects the width of the probability distribution for cospectral powers and modulates the measured rms proportionally to the distortion acted on power spectra.
+dead time affects the width of the probability distribution for cospectral powers and modulates the measured \rms proportionally to the distortion acted on power spectra.
 In this Letter, we show a method to precisely recover the shape of the power density spectrum by looking at the difference of the Fourier amplitudes of the light curves of two independent detectors.
@@
 
-\section{Data simulation and analysis} \label{sec:data}
+\section{Data simulation} \label{sec:data}
 All simulated and real data sets in this paper were produced and/or analyzed with a combination of the two Python libraries \texttt{stingray}%
@@
 
-\subsection{Simulated datasets}
 We used the same procedure and algorithms described by \citet{Bachetti+15}, Section 4, that we briefly summarize here together with references to the methods and classes of the libraries above where these steps are implemented.
 The classes in \texttt{stingray.simulate} were used to simulate light curves with a given noise profile. 
-These classes use the \citet{timmer1995} method to create a noise-affected light curve starting from a given power spectral shape described by a powerlaw index, an \texttt{astropy} model or a list of arrays containing the frequency and power of the model spectrum.
-We first created the light curves and then used an acceptance-rejection method to obtain simulated events from these light curves (\texttt{stingray.Eventlist.simulate\_times()}). 
+These classes use the \citet{timmer1995} method to create a noise-affected light curve starting from a given power spectral shape.
+We first created the noisy light curves and then used an acceptance-rejection method to obtain simulated events from these light curves (\texttt{stingray.Eventlist.simulate\_times()}). 
 This step needs to be done carefully: if the initial light curves are done directly with the wanted count rate, they contain significant random noise, and the process for the creation of events amplifies this noise (because it further creates a random variate on the top of the local count rate, which is varying randomly already) producing a non-Poissonian final light curve.
-Therefore, we initially used the \citet{timmer1995} method to get light curves with a very high count rate - a way to reduce the relative importance of the Poisson noise because of the square root involved - then renormalized the light curves to the wanted (lower) count rate and rms and finally used these light curves to simulate event lists.
+Therefore, we initially used the \citet{timmer1995} method to get light curves with a very high count rate - so that the Poisson noise is relatively small - then renormalized the light curves to the wanted (lower) count rate and \rms and finally used these light curves to simulate event lists.
 Finally, the \texttt{hendrics.fake.filter\_for\_deadtime()} function was used to apply a non-paralyzable dead time of 2.5\,ms to the simulated event lists.
@@
 
-\subsection{Cyg X-1 \nustar dataset}
-We tested the method also on real data of several bright sources observed by \nustar.
-As an example, we report here one such test done on \nustar data of the black hole binary Cyg~X-1 together with the steps to reproduce our analysis, using the linked Jupyter notebook if needed.
-We downloaded the observation directory of \nustar ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package (Bachetti et al., ASCL identifier requested).
-Equivalently, this download can be done using the online tools provided by HEASARC (e.g. \texttt{xamin}).
-Starting from the standard cleaned science event files distributed by HEASARC, we applied a barycenter correction using the FTOOL \texttt{barycorr} shipped with HEASOFT 6.21 with the clock correction file n.
+%\subsection{Cyg X-1 \nustar dataset}
+%We tested the method also on real data of several bright sources observed by \nustar.
+%As an example, we report here one such test done on \nustar data of the black hole binary Cyg~X-1 together with the steps to reproduce our analysis, using the linked Jupyter notebook if needed.
+%We downloaded the observation directory of \nustar ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package (Bachetti et al., ASCL identifier requested).
+%Equivalently, this download can be done using the online tools provided by HEASARC (e.g. \texttt{xamin}).
+%Starting from the standard cleaned science event files distributed by HEASARC, we applied a barycenter correction using the FTOOL \texttt{barycorr} shipped with HEASOFT 6.21 with the clock correction file n.
 71 from the \nustar CALDB.
-We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.%
-\footnote{To use the method on different sources, it is sufficient to download a different ObsID and change the region file containing the position of the source}.
-We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and produced light curves with photons from 3 to 79 keV and binned with uniform time bins of 1/4096$\sim2.44\cdot10^{-4}$\,sec%
-\footnote{This procedure uses the scripts \texttt{HENreadfile}, \texttt{HENcalibrate} and \texttt{HENlcurve}, as described at\\ \href{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}}.
+%We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.%
+%\footnote{To use the method on different sources, it is sufficient to download a different ObsID and change the region file containing the position of the source}.
+%We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and produced light curves with photons from 3 to 79 keV and binned with uniform time bins of 1/4096$\sim2.44\cdot10^{-4}$\,sec%
+%\footnote{This procedure uses the scripts \texttt{HENreadfile}, \texttt{HENcalibrate} and \texttt{HENlcurve}, as described at\\ \href{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}}.
 
@@
 The choice of different segment length reflects the range of frequencies we want to highlight in the two cases.
-The red curve gives the frequency-dependent spread of the distributions, measured by the standard deviation of the curves in each frequency bin. 
+The red curve gives the frequency-dependent spread of the distributions, measured by the mean of the absolute values of the curves in each frequency bin. 
 As expected, in the first case, the Fourier amplitude follows a power law curve, while the standard deviation of the difference is remarkably stable at all frequencies, as expected by the fact that the Poisson white noise is independent of frequency.
@@
 
-%\begin{figure*}
-%\gridline{\fig{imgs/pds_pdf}{0.5\textwidth}{(b)}
-%          \fig{imgs/cosp_pdf}{0.5\textwidth}{(c)}}
-%
-%\caption{(b) Distribution of powers in the periodogram, before the FAD correction and after, shown as a histogram.
-%After correction, the powers follow remarkably well the expected $\chi^2_2$ distribution.
-%(c) Same, for the cospectrum.
-%The correct Laplace distribution is followed after FAD correction}
-%\label{fig:dist}
-%\end{figure*}
 \begin{figure*}
-\gridline{\fig{imgs/before_and_after.eps}{\textwidth}{(a)}}
-\gridline{\fig{imgs/pds_pdf.pdf}{\textwidth}{(b)}}
-\caption{(Top) Periodogram and cospectrum, before and after FAD correction, for a pure white noise light curve. 
-The deadtime-driven distortion of the white noise level in the periodogram, and the frequency-dependent modulation of the rms in both spectra, disappear after applying the FAD correction. 
-Spectra were calculated over 2-sec intervals and averaged, to decrease the scatter and highlight the distortion of powers.
-(Bottom) PDF of non-averaged powers in the cospectrum (red) and the periodogram (black), before the FAD correction and after, shown as a histogram. 
+\plotone{imgs/before_and_after.eps}
+%\plotone{imgs/pds_pdf.pdf}
+\caption{Periodogram and cospectrum, before and after FAD correction, for a pure white noise light curve. 
+The deadtime-driven distortion of the white noise level in the periodogram, and the frequency-dependent modulation of the \rms in both spectra, disappear after applying the FAD correction. 
+Spectra were calculated over 2-sec intervals and averaged, to decrease the scatter and highlight the distortion of powers.}
+\label{fig:comparison}
+\end{figure*}
+
+\begin{figure*}
+\plotone{imgs/pds_pdf.pdf}
+\caption{PDF of non-averaged powers in the cospectrum (red) and the periodogram (black), before the FAD correction and after, shown as a histogram. 
 After correction, the powers follow remarkably well the expected Laplace and $\chi^2_2$ distributions respectively, as highlighted by the overplotted probability density functions (PDF).}
@@
 \end{figure*}
-Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec and a dead time of 2.5 ms, as we would expect from two identical detectors observing the same stable X-ray source.
-This case is illustrated in Figure ~\ref{fig:fourierdiff} (right panel).
+
+Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec [CHECK] and a dead time of 2.5 ms, as we would expect from two identical detectors observing the same stable X-ray source.
+This case is illustrated in Figure ~\ref{fig:fourierdiff} (middle panel).
 The Fourier amplitudes $A_{xj}$ and $A_{yj}$ of the light curves from the two detectors are heavily distorted by dead time, with the characteristic damped oscillator-like shape \citep{Vikhlinin+94,Zhang+95}.
@@
 
-As shown in Figure~\ref{fig:dist} (left panel), the single-channel Fourier amplitudes are proportional to the difference of the Fourier amplitudes in different realizations, with a constant factor $1/\sqrt{2}$.
+As shown in Figure~\ref{fig:fourierdiff} (left panel), the single-channel Fourier amplitudes are proportional to the difference of the Fourier amplitudes in different realizations, with a constant factor $1/\sqrt{2}$.
 Therefore, we expect that the periodogram will be proportional to the square of the Fourier amplitude difference, divided by 2.
@@
 Given that the initial binning had 50 bins/Hz, this interpolation allows an aggressive smoothing over bins whose y value does not change significantly.
-In general, we recommend smoothing over as many bins as allowed by the shape of the periodogram.
-In this paper, when not specified we average over the number of bins contained in 1Hz of the spectrum.
 We call this procedure the \textbf{Fourier Amplitude Difference} (hereafter FAD) \textbf{correction}.
 
-The correction is depicted in Figure~\ref{fig:dist}, right. 
-Starting from a heavily distorted distribution of the powers, applying the FAD correction reinstates a remarkably correct distribution of powers, following the expected $\chi^2_2$ distribution \citep{Lewin+88} very closely.
-Analogously, the corrected cospectrum will follow the expected Laplace distribution.
-While the original dead time-affected cospectrum had a frequency-dependent modification to the rms level, the FAD-corrected cospectrum gets back to a frequency-independent shape, like in the dead time-free case.
+The correction is depicted in Figure~\ref{fig:comparison}. 
+Starting from a heavily distorted distribution of the powers, applying the FAD correction ``flattens'' remarkably well the white noise level of the periodogram and the distribution of the scatter of the white noise periodogram and cospectrum.
+Also, it reinstates a remarkably correct distribution of powers, following the expected $\chi^2_2$ distribution \citep{Lewin+88} very closely. 
+Analogously, the corrected cospectrum will follow the expected Laplace distribution \citep{Huppenkothen & Bachetti, sub.}.
+While the original dead time-affected cospectrum had a frequency-dependent modification to the \rms level, the FAD-corrected cospectrum gets back to a frequency-independent shape, like in the dead time-free case.
 
@@
 
+\section{The FAD correction algorithm} \label{sec:fad}
+In practice, the FAD correction algorithm in a generic case would work as follows:
+\begin{enumerate}
+\item split the two light curves in segments as one would do to calculate standard averaged periodograms;
+\item for each pair of light curve segments: 
+	\begin{itemize}
+	\item calculate the Fourier transform of each channel separately, and then of the summed channels (hereafter total-intensity);
+	\item save the unnormalized Fourier amplitudes;
+	\item multiply these Fourier amplitudes by $\sqrt{2/N_{ph}}$ (that would give Leahy-normalized periodograms if squared);
+	\item subtract the Leahy-normalized Fourier amplitudes of the two channels between them, \textit{take the absolute value}, and obtain this way the Fourier Amplitude Differences (FAD);
+	\item \textit{smooth} the FAD using a Gaussian-window interpolation with a large number of bins, in our case all the bins contained in 1-2 Hz;
+	\item use the separated single-channel and total-intensity \textit{unnormalized} Fourier amplitudes to calculate the periodograms;
+	\item use the unnormalized Fourier amplitudes from channels A and B to calculate the cospectrum;
+	\item divide all periodograms and the cospectrum by the smoothed and squared FAD, and multiply by 2.
+	\end{itemize}
+\item normalize the periodograms to the wanted normalization (Leahy or fractional \rms).
+\end{enumerate}
+
+%%%%%%%%%%%%%%%%%%%%%%%% SECTION 6 %%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Testing the FAD correction on simulated data} \label{sec:correction}
 
-%\begin{figure*}
-%    \gridline{\fig{imgs/rednoise_rebin}{0.33\textwidth}{(a)}
-%        \fig{imgs/rednoise_rebin_zoom}{0.33\textwidth}{(b)}
-%        \fig{imgs/simu_rebin_log}{0.33\textwidth}{(c)}}
-%    \gridline{\fig{imgs/cygx1_soft_nustar_2_rebin}{0.33\textwidth}{(d)}
-%        \fig{imgs/cygx1_soft_nustar_2_rebin_zoom}{0.33\textwidth}{(e)}
-%        \fig{imgs/cygx1_soft_nustar_2_rebin_log}{0.33\textwidth}{(f)}}  
-%    \caption{
-%        Top: simulated dataset with two strong and broad Lorentzian components, incident count rate $\sim$810 ct/s, and total rms $\sim$15\% (``detected'' after dead time: $\sim$270 and $\sim$4\% resp.).
-%        Bottom: \nustar observation of the black hole candidate Cyg X-1. 
-%        (a) and (d): comparison of the distortion of the dead time-affected periodogram with the FAD-corrected periodogram, the dead time-affected and the FAD-corrected cospectrum.
-The spectra have been shifted vertically for clarity.
-%        The shape of the uncorrected periodogram is clearly distorted by dead time. 
-%        (b) and (e): the FAD correction successfully flattens the periodogram, but there remain a few intervals where the baseline is imperfect, indicated by the arrows.
-%        This is due to the flux mismatch between the two detectors (see \sref{sec:realdata}).
-%        The cospectral powers are always distributed around zero, but dead time changes the width of the resulting distribution, and the FAD correction attenuates the width of the distribution back to the width expected in the dead time-free case (see e.g.\ (b) for a striking case).
-%        Moreover, the source-dominated part of the spectrum also receives a boost, which corrects precisely the measured rms of the source from the ``hushing'' effect of dead time.
-%        (c) and (f): FAD-corrected periodogram and cospectra, plotted in $\mathrm{(rms/mean)}^2$ normalization and fitted with two Lorentzian curves (c) and with an exponential cutoff power law (f).
-%        The additional gain coming from the FAD normalization is evident by the comparison with the uncorrected cospectrum.}
-%    \label{fig:pds}
-%\end{figure*}
 \begin{figure*}
@@
     We plotted and fitted periodograms and cospectra before and after applying the dead time filter
-    The total rms before dead time was 40\% and the incident photon flux 400 ct/s. 
+    The total \rms before dead time was 40\% and the incident photon flux 400 ct/s. 
     After applying a dead time of 2.5 ms like in \nustar, the ``detected'' photon flux decreased to $\sim$200 ct/s as expected. 
@@
 We first calculated the periodogram and cospectrum of the dead time-free data, averaged over 128-s intervals.
-Then, we applied a dead time filter to the event list and applied the FAD correction, as follows:
-\begin{enumerate}
-\item split the two light curves in segments of 128 to 512 seconds
-\item for each pair of light curve segments: 
-	\begin{itemize}
-	\item calculate the Fourier transform of each channel separately, and then of the summed channels (hereafter the \textit{total-intensity} light curve);
-	\item multiply the Fourier amplitudes by $\sqrt{2/N_{ph}}$ in order to obtain Leahy-normalized periodograms;
-	\item subtract the Fourier amplitudes of the two channels between them, \textit{take the absolute value}, and obtain this way the Fourier Amplitude Differences (FAD);
-	\item \textit{smooth} the FAD using a Gaussian-window interpolation with a width of 1-2 seconds;
-	\item use the separated single-channel and total-intensity Fourier amplitudes to calculate the periodograms;
-	\item use the Fourier amplitudes from channels A and B to calculate the cospectrum;
-	\item divide all periodograms and the cospectrum by the smoothed and squared FAD, and multiply by 2.
-	\end{itemize}
-\end{enumerate}
+Then, we applied a dead time filter to the event list and applied the FAD correction, as described in Section~\ref{sec:fad}
 
-All spectra were then expressed in fractional rms \citep{BelloniHasinger90,Miyamoto+91} normalization, where the integral of the fitted spectral components over the frequency returns directly its fractional rms.
-In the rms normalization, the values of each point of the periodogram, after white noise subtraction, should be consistent between the dead time-free and the FAD-corrected periodograms.
-We first checked visually that the spectra (white-noise subtracted in the case of periodograms) after FAD correction were all consistent with the dead time-free periodogram. 
-Then, we fitted all spectra with the model which produced the simulated data and checked if the values were consistent with the input model parameters and the fit on the dead time-free periodogram.
-Finally, we verified if \textit{at low frequencies} the total rms of the FAD-corrected spectra was consistent with the total rms of the dead time-affected cospectrum \textit{times the ratio between incident and detected photons}, using the count rates before and after applying the dead time filter.
-To calculate this rms, we fitted the spectra with two Lorentzian components, and integrated the model over the full frequency range.
+All spectra were then expressed in fractional \rms \citep{BelloniHasinger90,Miyamoto+91} normalization, where the integral of the fitted spectral components over the frequency returns directly its fractional \rms.
+In the \rms normalization, the values of each point of the periodogram, after white noise subtraction, should be consistent between the dead time-free and the FAD-corrected periodograms.
+We fitted all spectra with the model which produced the simulated data and checked if the \rms values were consistent with the fit on the dead time-free periodogram.
+To calculate this \rms, we fitted the spectra with two Lorentzian components, and integrated the model over the full frequency range.
 For periodograms, the model included also a constant offset to account for the white noise level.
@@
 \section{Caveats}\label{sec:caveat}
-The simulations show that the shape of the periodogram is precisely corrected by the FAD procedure \textit{if the input light curves have the same count rate} and \textit{for values of the input count rate and rms that are not too extreme}.
+\begin{figure*}
+    \plotone{imgs/errors.png}
+    \caption{Relative overestimation of FAD with respect to \rms, versus \rms, as calculated from the cospectrum.  
+    We encoded the frequency of the feature in the color, and the incident rate in the size of the scatter points.
+    From this visualization we see two regimes: below $\sim$40\% fractional \rms, the errors are dominated by statistical errors. 
+    These errors will simply decrease when we average more data, as we expect from statistical errors.
+    Over $\sim$40\% fractional \rms, the errors are significantly skewed towards an overestimation of the \rms, and this is 
+    clearly truer when the incident rate \textit{and} the \rms are high.}
+    \label{fig:errors}
+\end{figure*}
+The simulations show that the shape of the periodogram is precisely corrected by the FAD procedure \textit{if the input light curves have the same count rate} and \textit{for values of the input count rate and \rms that are not too extreme}.
 The first caveat turns out to be an issue only for the single-channel periodogram. 
@@
 The second caveat needs some attention. 
-We find that the FAD correction consistently overestimates the integrated rms when the count rate and rms are \textit{both} very high, \textit{independently from the frequency}.
-This latter feature is less intuitive, because we would expect that this overestimation should somehow be more relevant where the correction is stronger, while this is not the case.
-But for this very reason, it is somewhat easier to account for this through simulations, without having to make further risky frequency-dependent corrections to the rms.
-At standard count rates and fractional rms for bright black hole binaries, $\sim$200 ct/s and 30\% rms, the difference is below 5\%. 
-However, it increases \textit{linearly} with the count rate and \textit{quadratically} with rms.
-A practical way to estimate this effect during analysis is to apply the FAD, obtain a best fit model, calculate the rms, then use the codes we shared with the Jupyter notebooks to simulate a number of realizations of the code, evaluating what is the amount of overestimation involved.
+We find that the FAD correction consistently overestimates the integrated \rms when the count rate and \rms are \textit{both} very high, \textit{in particular at low frequency} (See Figure~\ref{fig:errors}).
+At standard count rates and fractional \rms for bright black hole binaries, $\sim$200 ct/s and 30\% \rms for the \nustar case, the relative error is below 5\% (meaning that if the \rms is 30\%, the measured \rms is between 30 and 32\%!) and it is symmetrically distributed around 0, as expected from statistical error.
+At higher incident rates and \rms, the error distribution skews towards positive relative errors, implying an overestimation of the \rms.
+This should not be a problem in most cases, where the \rms is used as a rough indicator for spectral state.
+If very precise measurements of \rms are needed (for example, to calculate \rms/energy spectra), it is somewhat safer to account for this through simulations, without having to make further risky frequency-dependent corrections to the \rms.
+As a rough estimate, the relative error on the fractional \rms increases \textit{linearly} with the count rate and \textit{quadratically} with real \rms.
+A practical way to estimate this effect during analysis is to apply the FAD, obtain a best fit model, calculate the \rms, then use the codes we shared with the Jupyter notebooks to simulate a number of realizations of the light curve, evaluating what is the amount of overestimation involved.
 
 %%%%%%%%%%%%%%%%%%%%%%%% SECTION 6 %%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Application to Cyg X-1}\label{sec:realdata}
-In this Section we apply the FAD correction to a \nustar observation of Cyg X-1.
-This source was discovered in the early days of X-ray astronomy \citep{Bowyer+65} and it is among the best studied X-ray sources in the sky.
-It is a persistent black hole X-ray binary, alternating soft and hard spectral states with distinct timing and spectral features \citep[see, e.g., ][]{Grinberg+13}.
-The observation we analyze here was taken during the source's soft state, that is characterized by a non-thermal X-ray spectrum, stable radio jets and, what matters the most here, distinct aperiodic variability that is well fitted by an exponential cutoff power law with index $\sim1$ (see, e.g., \citealt{Gilfanov+00}).
-We followed the procedure described in \sref{sec:correction}, dividing the light curves in 512-s segments and smoothing the squared FAD with a Gaussian window of 1-s width (512 bins).
-The results are shown in Figure~\ref{fig:pds}, lower panel for comparison with the simulations.
-
-We fitted the four spectra of Cyg X-1 with an exponential cutoff power law. 
-For periodograms, we added to the models an additive constant to account for the white noise level.
-In all cases, the estimates returned by the fit were consistent between the different spectra in all but the amplitude parameter of the power law curve.
-We used this amplitude to calculate the ratios between the rms measured by the deadtime-affected cospectrum and the FAD-corrected spectra.
-The increase of rms between the dead time-affected cospectrum and the FAD-corrected cospectrum and periodograms is consistent to 2\% with the ratio $r_{in}/r_{det}$, where $r_{in}$ is the incident count rate, and $r_{det}$ is the detected count rate,
-given by
-
-\begin{equation}
-r_{det} = \frac{r_{in}}{1 + \deadt r_{in}}
-\end{equation} 
-(using the standard non-paralyzable dead time formula, where \deadt is dead time) which is the drop of rms expected from the effect of dead time \citep{Bachetti+15}.
+%
+%\section{Example: Cyg X-1 \nustar dataset}
+%We tested the method also on real data of several bright sources observed by \nustar.
+%As an example, we report here one such test done on \nustar data of the black hole binary Cyg~X-1 together with the steps to reproduce our analysis, using the linked Jupyter notebook if needed.
+%
+%Cyg X-1 is a persistent black hole X-ray binary, alternating soft and hard spectral states with distinct timing and spectral features \citep[see, e.g., ][]{Grinberg+13}.
+%We downloaded standard data products of 
+%The observation we analyze here was taken during the source's soft state, that is characterized by a non-thermal X-ray spectrum, stable radio jets and, what matters the most here, distinct aperiodic variability that is well fitted by an exponential cutoff power law with index $\sim1$ (see, e.g., \citealt{Gilfanov+00}).
+%We followed the procedure described in \sref{sec:correction}, dividing the light curves in 512-s segments and smoothing the squared FAD with a Gaussian window of 1-s width (512 bins).
+%The results are shown in Figure~\ref{fig:pds}, lower panel for comparison with the simulations. 
+%
+%We fitted the four spectra of Cyg X-1 with an exponential cutoff power law. 
+%For periodograms, we added to the models an additive constant to account for the white noise level.
+%In all cases, the estimates returned by the fit were consistent between the different spectra in all but the amplitude parameter of the power law curve.
+%We used this amplitude to calculate the ratios between the \rms measured by the deadtime-affected cospectrum and the FAD-corrected spectra.
+%The increase of \rms between the dead time-affected cospectrum and the FAD-corrected cospectrum and periodograms is consistent to 2\% with the ratio $r_{in}/r_{det}$, where $r_{in}$ is the incident count rate, and $r_{det}$ is the detected count rate,
+%given by
+%
+%\begin{equation}
+%r_{det} = \frac{r_{in}}{1 + \deadt r_{in}}
+%\end{equation} 
+%(using the standard non-paralyzable dead time formula, where \deadt is dead time) which is the drop of \rms expected from the effect of dead time \citep{Bachetti+15}.
 
@@
 In all cases, we find that the adjustment of the white noise standard deviation in the periodogram and the cospectrum works remarkably well, allowing to make a confident analysis of X-ray variability even in sources where this was precluded until now.
+The only 
 This software will be merged into the main repository of \texttt{stingray} before publication.
 A number of jupyter notebooks will also be posted at the address \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the full analysis plotted in the Figures of this paper, plus more examples of application of these techniques to simulated and real data.
+The full algorithm described in Section~\ref{sec:fad} is contained in the \texttt{fad\_correction.py} file in the notebooks directory, for reference.
 
@@
 
+\bibitem[{{Timmer} \& {Koenig}(1995)}]{timmer1995}
+{Timmer}, J., \& {Koenig}, M. 1995, \aap, 300, 707
+
 \bibitem[{Vikhlinin {et~al.}(1994)Vikhlinin, Churazov, \&
@@
 \end{thebibliography}
+
 \end{document}

### 2017-12-10 paper/deadtime.tex
Further changes in response of minor referee concerns

@@
 , which is the most widely used statistical tool to investigate rapid variability, is heavily distorted by dead time, with a characteristic pattern similar to a damped oscillator.
-This pattern is stronger for brighter sources, and it is often not possible to disentangle this spectral distortion due to dead time and the broadband noise components characterizing the emission of accreting systems.
+This pattern is stronger for brighter sources, and it is often not possible to disentangle this power spectral distortion due to dead time and the broadband noise components characterizing the emission of accreting systems.
 In the special case where dead time is constant, its shape can be modeled precisely \citep{Zhang+95,Vikhlinin+94}.
@@
 
-\caption{(a) and (b): Real Fourier amplitudes obtained by single light curves (top panels) and difference between two realizations of the same source light curve (bottom) in two cases: (a) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (b) no red noise and strong dead time, calculated over many 5\,s segments of the light curve.
+\caption{(a) and (b): Real-valued Fourier amplitudes obtained by single light curves (top panels) and difference between two realizations of the same source light curve (bottom) in two cases: (a) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (b) no red noise and strong dead time, calculated over many 5\,s segments of the light curve.
 The choice of different segment length reflects the range of frequencies we want to highlight in the two cases.
@@
 
-Let us consider two identical and independent detectors observing the same variable source, producing independent time series $\mathbf{x} = \{x_k\}_{k=1}^N$ and $\mathbf{y} = \{y_k\}_{k=1}^N$.
+Let us consider two identical and independent detectors observing the same variable source, producing independent and strictly simultaneous time series, with identical binning, $\mathbf{x} = \{x_k\}_{k=1}^N$ and $\mathbf{y} = \{y_k\}_{k=1}^N$.
 For a stochastic process (e.g.\ $1/\nu$-type red noise), the Fourier amplitudes will vary as a function of $N_{\mathrm{phot}}P(\nu)/4$, where $P(\nu)$ is the shape of the power spectrum underlying the stochastic process, and $N_{\mathrm{phot}}$ denotes the number of photons in a light curve.
@@
 
-All spectra were then expressed in fractional \rms \citep{BelloniHasinger90,Miyamoto+91} normalization, where the integral of the fitted spectral components over the frequency returns directly its fractional \rms.
+All spectra were then expressed in fractional \rms \citep{BelloniHasinger90,Miyamoto+91} normalization, where the integral of the fitted power spectral components over the frequency returns directly its fractional \rms.
 In the \rms normalization, the values of each point of the periodogram, after white noise subtraction, should be consistent between the dead time-free and the FAD-corrected periodograms.

### 2017-12-11 notebooks/fad_correction.py
Cleanup

@@ -99,9 +99,6 @@ def FAD_power_spectra(lc1, lc2, segment_size, plot=False, smoothing_alg='gauss',
         elif smoothing_alg == 'spline':
             spl = UnivariateSpline(freq, fourier_diff.real**2, s=1)
             smooth_real = spl(freq.astype(np.float64))
-        elif smoothing_alg == 'savgol':
-            spl = UnivariateSpline(freq, fourier_diff.real**2, s=1)
-            smooth_real = spl(freq.astype(np.float64))
         if plot:
             plt.scatter(freq, fourier_diff, s=1)
 

### 2017-12-11 notebooks/plot_all_trials.py
New behavior with watchdog

@@ -1,6 +1,15 @@
 from pandas import read_csv
 import matplotlib.pyplot as plt
 import numpy as np
+import sys
+import time
+import logging
+from watchdog.observers import Observer
+from watchdog.events import LoggingEventHandler
+from watchdog.events import PatternMatchingEventHandler
+from hendrics.base import r_in, r_det
+import warnings
+warnings.filterwarnings('ignore')
 
 
 def plot_scatter_ratios(results, channel, toler_d_clean=0.01,
@@ -46,8 +55,8 @@ def pairplot(file, toler_d_clean=0.5, filters={'channel_ratio': [0.8, 1.2]}):
     meanrate = results['incident_rate'] // 100 * 100 + 50
     results["rate"] = meanrate
     results["median_ratio"] = results['median'] / results['clean_median']
-    vars_unfilt = ['channel_ratio', 'frequency', 'Frac_rms',
-            'CS', 'PDS 1', 'PDStot', 'slope', 'median_ratio']
+    vars_unfilt = ['channel_ratio', 'frequency', 'input_fwhm', 'Frac_rms',
+            'CS', 'PDS 1', 'PDStot']
     vars = []
     for v in vars_unfilt:
         if v in results:
@@ -118,7 +127,8 @@ def offset(x, q):
 
 
 def fit_incident_vs_delta(file, toler_d_clean=0.01, 
-                          filters={'channel_ratio': [0.8, 1.2]}):
+                          filters={'channel_ratio': [0.8, 1.2]},
+                          nsub=9):
     from scipy.optimize import curve_fit
     from matplotlib.pyplot import cm
     from matplotlib.gridspec import GridSpec
@@ -136,10 +146,11 @@ def fit_incident_vs_delta(file, toler_d_clean=0.01,
     ax0 = plt.subplot(gs[0, 0])
     ax1 = plt.subplot(gs[1, 0])
     ax2 = plt.subplot(gs[:, 1])
-    nsub = 9
+
     frac_rmss = np.linspace(0.05,
                             np.max(results['Frac_rms']), nsub)
     colors=iter(cm.magma(np.linspace(0,1,nsub)))
+    plotcolors = []
     coeffs = []
     for frac_rms_min, frac_rms_max in zip(frac_rmss[:-1], frac_rmss[1:]):
         good_rms = (results['Frac_rms'] >= frac_rms_min)&(results['Frac_rms'] < frac_rms_max)
[…]

### 2017-12-11 paper/deadtime.tex
Simulations et al.

@@
 \footnote{The library is under heavy development.
-    For this work we used the version identified by the hash \texttt{XXXXXX}}
-\citep{huppenkothen2016} and \texttt{HENDRICS} v.\texttt{3.0b1} \citep[formerly known as MaLTPyNT;][]{2015ascl.soft02021B}, both based on Astropy \citep{astropy2013}.
+    For this work we used the version identified by the hash \texttt{3e64f3d}}
+\citep{huppenkothen2016} and \texttt{HENDRICS} v.\texttt{3.0b2} \citep[formerly known as MaLTPyNT;][]{2015ascl.soft02021B}, both based on Astropy \citep{astropy2013}.
 
-We used the same procedure and algorithms described by \citet{Bachetti+15}, Section 4, that we briefly summarize here together with references to the methods and classes of the libraries above where these steps are implemented.
-The classes in \texttt{stingray.simulate} were used to simulate light curves with a given noise profile. 
-These classes use the \citet{timmer1995} method to create a noise-affected light curve starting from a given power spectral shape.
-We first created the noisy light curves and then used an acceptance-rejection method to obtain simulated events from these light curves (\texttt{stingray.Eventlist.simulate\_times()}). 
-This step needs to be done carefully: if the initial light curves are done directly with the wanted count rate, they contain significant random noise, and the process for the creation of events amplifies this noise (because it further creates a random variate on the top of the local count rate, which is varying randomly already) producing a non-Poissonian final light curve.
-Therefore, we initially used the \citet{timmer1995} method to get light curves with a very high count rate - so that the Poisson noise is relatively small - then renormalized the light curves to the wanted (lower) count rate and \rms and finally used these light curves to simulate event lists.
+We used the same procedure and algorithms described by \citet{Bachetti+15}, Section 4, that we briefly recall here together with references to the methods and classes of the libraries above where these steps are implemented.
+%The classes in the \texttt{stingray.simulate} module were used to simulate light curves with a given noise profile. 
+We used the \citet{timmer1995} method to create a noise-affected light curve starting from a given power spectral shape. 
+This method is implemented in the \texttt{stingray.simulate} module.
+%We first created the noisy light curves and then used an acceptance-rejection method to obtain simulated events. 
+This step needs to be done carefully: if the initial light curves contain significant random noise, the process for the creation of events creates a random variate on the top of the local count rate - which is varying randomly already - producing a non-Poissonian final light curve.
+So, we initially simulated light curves with a very high ``count rate'' - so that the Poisson noise was relatively small - then renormalized the light curves to the wanted (lower) count rate and \rms and finally used these light curves to simulate event lists using the rejection sampling, implemented in the \texttt{stingray.Eventlist.simulate\_times()} method.
 Finally, the \texttt{hendrics.fake.filter\_for\_deadtime()} function was used to apply a non-paralyzable dead time of 2.5\,ms to the simulated event lists.
@@
 \caption{(a) and (b): Real-valued Fourier amplitudes obtained by single light curves (top panels) and difference between two realizations of the same source light curve (bottom) in two cases: (a) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (b) no red noise and strong dead time, calculated over many 5\,s segments of the light curve.
-The choice of different segment length reflects the range of frequencies we want to highlight in the two cases.
 The red curve gives the frequency-dependent spread of the distributions, measured by the mean of the absolute values of the curves in each frequency bin. 
-As expected, in the first case, the Fourier amplitude follows a power law curve, while the standard deviation of the difference is remarkably stable at all frequencies, as expected by the fact that the Poisson white noise is independent of frequency.
-In the second case, instead, dead time is frequency dependent and white noise is also affected, so that the difference of Fourier amplitudes is modulated as well.
+The different behavior of Fourier amplitude differences under pure Poisson noise and dead time noise is evident, by comparing (a) and (b).
 (c) Scatter distribution of the absolute values of dead time-affected Fourier amplitudes versus the difference of Fourier amplitudes for case (b): their relation is clearly linear, with a factor $1/\sqrt{2}$.
@@
 
-Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec [CHECK] and a dead time of 2.5 ms, as we would expect from two identical detectors observing the same stable X-ray source.
-This case is illustrated in Figure ~\ref{fig:fourierdiff} (middle panel).
+Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec and a dead time of 2.5 ms, as we would expect from two identical detectors observing the same stable X-ray source (Figure ~\ref{fig:fourierdiff}, middle panel).
 The Fourier amplitudes $A_{xj}$ and $A_{yj}$ of the light curves from the two detectors are heavily distorted by dead time, with the characteristic damped oscillator-like shape \citep{Vikhlinin+94,Zhang+95}.
@@
 
-As shown in Figure~\ref{fig:fourierdiff} (left panel), the single-channel Fourier amplitudes are proportional to the difference of the Fourier amplitudes in different realizations, with a constant factor $1/\sqrt{2}$.
+As shown in Figure~\ref{fig:fourierdiff} (right panel), the single-channel Fourier amplitudes are proportional to the difference of the Fourier amplitudes in different realizations, with a constant factor $1/\sqrt{2}$.
 Therefore, we expect that the periodogram will be proportional to the square of the Fourier amplitude difference, divided by 2.

### 2017-12-11 paper/deadtime.tex
Rewrite section 3 with multiplicative dead time filter

@@
 Let us consider two identical and independent detectors observing the same variable source, producing independent and strictly simultaneous time series, with identical binning, $\mathbf{x} = \{x_k\}_{k=1}^N$ and $\mathbf{y} = \{y_k\}_{k=1}^N$.
-For a stochastic process (e.g.\ $1/\nu$-type red noise), the Fourier amplitudes will vary as a function of $N_{\mathrm{phot}}P(\nu)/4$, where $P(\nu)$ is the shape of the power spectrum underlying the stochastic process, and $N_{\mathrm{phot}}$ denotes the number of photons in a light curve.
+For a stochastic process (e.g.\ $1/\nu$-type red noise), the Fourier amplitudes will vary as a function of $N_{\mathrm{phot}}P(\nu)/4$, where $P(\nu)$ (Leahy-normalized, \citealt{Leahy+83}) is the shape of the power spectrum underlying the stochastic process, and $N_{\mathrm{phot}}$ denotes the number of photons in a light curve.
 If the two detectors observe the same source simultaneously, the amplitudes and phases of the stochastic process will be shared among $\mathbf{x}$ and $\mathbf{y}$, while each light curve will be affected \textit{independently} by both the photon counting noise in the detector, as well as the dead time process.
-The resulting Fourier amplitudes will be of the form
-
-\begin{eqnarray}
-A_{xj} &=& A_{xsj} + A_{xdj} + A_{xnj} \nonumber \\
-B_{xj} &=& B_{xsj} + B_{xdj} + B_{xnj} \, ,
-\end{eqnarray}
-
-\noindent where $A_{xsj}$ and $B_{xsj}$ denote the real and imaginary components of the signal power in the Fourier amplitudes,  $A_{xdj}$ and $B_{xdj}$ denote the variance introduced by dead time, and $A_{xnj}$ and $B_{xnj}$ similarly denote the white noise components in the Fourier amplitudes.
-For a large enough number of data points $N$, the Fourier amplitudes $A_{xj}$ and $B_{xj}$ will be composed of a sum of three independent random normal variables, with $A_{xsj} \sim \Normal(0, \sigma_{sj}^2)$,  $A_{xdj} \sim \Normal(0, \sigma_{dj}^2)$ and $A_{xnj} \sim \Normal(0, \sigma_n^2)$, where $\sigma_{sj}^2 = \sigma_{s}^2(\nu) = N_\mathrm{phot}P(\nu)/4$ is given by the (Leahy-normalized, \citealt{Leahy+83}) power spectrum of the underlying stochastic process, $P_j = P(\nu_j)$, $\sigma_{dj}^2$ is an unknown, frequency-dependent variance introduced by dead time, and $N_{\mathrm{phot}} = \sum_{k=1}^{N}{x_k}$ is the integrated flux in the light curve.
+Dead time can be considered a convolution of the signal \citep{Vikhlinin+94}.
+As such, for the convolution theorem we will have that the Fourier transform $\mathcal{F}$ of dead time-affected light curves will result in a \textit{product} of the Fourier transform of the signal times the Fourier transform of the dead time filter:
+\begin{equation}
+\mathcal{F}(\nu) = \mathcal{S}(\nu)\cdot\mathcal{D}(\nu)
+\end{equation}
+where $\mathcal{S}$ denotes the signal and $\mathcal{D}$ dead time.
+For a large enough number of data points $N$, the complex Fourier amplitudes $S_j$ will be composed of a sum of two independent random normal variables: $S_j = S_{sj} + S_{nj}$, with $\Re S_{sj} \sim \Normal(0, \sigma_{sj}^2)$ and $\Re S_{nj} \sim \Normal(0, \sigma_n^2)$, and similarly for the imaginary parts, where $\sigma_{sj}^2 = \sigma_{s}^2(\nu) = N_\mathrm{phot}P(\nu)/4$ is given by the power spectrum of the underlying stochastic process and $N_{\mathrm{phot}} = \sum_{k=1}^{N}{x_k}$ is the integrated flux in the light curve.
+We also have $\sigma_n^2 = N_\mathrm{phot}/2$.
+Moreover, the dead time filter will only depend on the mean count rate, which is the same in the two light curves.
+Thus, the difference between the Fourier amplitudes for the two time series $\mathbf{x}$ and $\mathbf{y}$ will be:
+\begin{equation}
+F_{xj} - F_{yj} = (S_{xj} - S_{yj})\cdot D_j = (S_{xsj} - S_{ysj} + S_{xnj} - S_{ynj})\cdot D_j
+\end{equation}
+It is important to note that $S_{xsj} = S_{ysj}$, that is, the amplitudes of the stationary noise process will be the same for the Fourier transforms of $\mathbf{x}$ and $\mathbf{y}$, while the components due to white noise differ between the two time series.
+Therefore, 
+\begin{equation}
+F_{xj} - F_{yj} = (S_{xnj} - S_{ynj})\cdot D_j
+\end{equation}
+So, in practice, the real and imaginary parts of the Fourier amplitude \textit{difference} between two simultaneous lightcurves of the same signal from identical detectors will be a random variate of the form $\Normal(0, 2\sigma_{n}^2)$ for both the imaginary and real parts, \textit{multiplied} by the Fourier transform of the dead time filter.
+But the squared norm of the latter \textit{is also what is distorting the periodograms}!
+However, whereas in the case of periodograms the source signal is mingled with the shape of $|\mathcal{D}|^2$, in this case we have a \textit{constant-scatter} random variable which is modulated by the same shape.
+Therefore, we can try to extract the shape of $|\mathcal{D}|^2$ from the Fourier amplitude differences from the two channels, and use it to correct the shape of the periodogram.
+%
+%
+%The resulting Fourier amplitudes will be of the form
+%
+%\begin{eqnarray}
+%A_{xj} &=& A_{xsj} + A_{xdj} + A_{xnj} \nonumber \\
+%B_{xj} &=& B_{xsj} + B_{xdj} + B_{xnj} \, ,
+%\end{eqnarray}
+%
+%\noindent where $A_{xsj}$ and $B_{xsj}$ denote the real and imaginary components of the signal power in the Fourier amplitudes,  $A_{xdj}$ and $B_{xdj}$ denote the variance introduced by dead time, and $A_{xnj}$ and $B_{xnj}$ similarly denote the white noise components in the Fourier amplitudes.
+%For a large enough number of data points $N$, the Fourier amplitudes $A_{xj}$ and $B_{xj}$ will be composed of a sum of three independent random normal variables, with $A_{xsj} \sim \Normal(0, \sigma_{sj}^2)$,  $A_{xdj} \sim \Normal(0, \sigma_{dj}^2)$ and $A_{xnj} \sim \Normal(0, \sigma_n^2)$, where $\sigma_{sj}^2 = \sigma_{s}^2(\nu) = N_\mathrm{phot}P(\nu)/4$ is given by the power spectrum of the underlying stochastic process, $P_j = P(\nu_j)$, $\sigma_{dj}^2$ is an unknown, frequency-dependent variance introduced by dead time, and $N_{\mathrm{phot}} = \sum_{k=1}^{N}{x_k}$ is the integrated flux in the light curve.
 We also have $\sigma_n^2 = N_\mathrm{phot}/2$, and hence the combined distributions become
-
-\begin{eqnarray}
-A_{xj} &\sim & \Normal(0, \sigma_{sj}^2 + \sigma_{dj}^2 + \sigma_{n}^2) \nonumber \\
-A_{yj} &\sim & \Normal(0, \sigma_{sj}^2 + \sigma_{dj}^2 + \sigma_{n}^2) \nonumber \, .
-\end{eqnarray}
-
-\noindent Similar expressions can be found for $A_{yj}$ and $B_{yj}$, respectively.
+%
+%\begin{eqnarray}
+%A_{xj} &\sim & \Normal(0, \sigma_{sj}^2 + \sigma_{dj}^2 + \sigma_{n}^2) \nonumber \\
+%A_{yj} &\sim & \Normal(0, \sigma_{sj}^2 + \sigma_{dj}^2 + \sigma_{n}^2) \nonumber \, .
+%\end{eqnarray}
+%
+%\noindent Similar expressions can be found for $A_{yj}$ and $B_{yj}$, respectively.
 It is important to note that $A_{xsj} = A_{ysj}$ and similarly $B_{xsj} = B_{ysj}$, that is, the amplitudes of the stationary noise process will be the same for the Fourier transforms of $\mathbf{x}$ and $\mathbf{y}$, while the components due to dead time and white noise differ between the two time series.
-
-As depicted in Figure~\ref{fig:fourierdiff}, the correlation between Fourier amplitudes implies that their difference will be independent of the source-induced variability $P(\nu_j)$ and will again be distributed following a normal distribution
-
-\[
-A_{xj} - A_{yj} \sim \Normal(0, 2\sigma_{dj}^2 + 2\sigma_{n}^2) \; .
-\]
-
-\noindent The difference in Fourier amplitudes effectively separates the frequency-dependent effects of source variability and variability due to detector effects.
+%
+%As depicted in Figure~\ref{fig:fourierdiff}, the correlation between Fourier amplitudes implies that their difference will be independent of the source-induced variability $P(\nu_j)$ and will again be distributed following a normal distribution
+%
+%\[
+%A_{xj} - A_{yj} \sim \Normal(0, 2\sigma_{dj}^2 + 2\sigma_{n}^2) \; .
+%\]
+%
+%\noindent The difference in Fourier amplitudes effectively separates the frequency-dependent effects of source variability and variability due to detector effects.
 
@@
 As laid out in Section \ref{sec:fourierdiff}, the difference of Fourier amplitudes from two independent but identical detectors shows no source variability, but \textit{still shows the same distortion} due to dead time.
-This gives a clear way to disentangle between source- and dead time-driven variability.
-By using the difference between the Fourier amplitudes in two detectors, we can in principle renormalize the power spectrum so that only the source variability alters its otherwise flat shape.
+Therefore, using the difference between the Fourier amplitudes in two detectors, we can in principle renormalize the power spectrum so that only the source variability alters its otherwise flat shape.
 

### 2017-12-11 paper/deadtime.tex
Small adjustments to Section 3

@@
 If the two detectors observe the same source simultaneously, the amplitudes and phases of the stochastic process will be shared among $\mathbf{x}$ and $\mathbf{y}$, while each light curve will be affected \textit{independently} by both the photon counting noise in the detector, as well as the dead time process.
-Dead time can be considered a convolution of the signal \citep{Vikhlinin+94}.
-As such, for the convolution theorem we will have that the Fourier transform $\mathcal{F}$ of dead time-affected light curves will result in a \textit{product} of the Fourier transform of the signal times the Fourier transform of the dead time filter:
+Dead time can be considered a convolution on the signal \citep{Vikhlinin+94}. 
+As such, for the convolution theorem we will have that the Fourier transform $\mathcal{F}$ of dead time-affected light curves will result in a \textit{product} of the Fourier transform of the signal $\mathcal{S}$ times the Fourier transform of the dead time filter $\mathcal{D}$:
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{S}$ denotes the signal and $\mathcal{D}$ dead time.
-For a large enough number of data points $N$, the complex Fourier amplitudes $S_j$ will be composed of a sum of two independent random normal variables: $S_j = S_{sj} + S_{nj}$, with $\Re S_{sj} \sim \Normal(0, \sigma_{sj}^2)$ and $\Re S_{nj} \sim \Normal(0, \sigma_n^2)$, and similarly for the imaginary parts, where $\sigma_{sj}^2 = \sigma_{s}^2(\nu) = N_\mathrm{phot}P(\nu)/4$ is given by the power spectrum of the underlying stochastic process and $N_{\mathrm{phot}} = \sum_{k=1}^{N}{x_k}$ is the integrated flux in the light curve.
-We also have $\sigma_n^2 = N_\mathrm{phot}/2$.
-Moreover, the dead time filter will only depend on the mean count rate, which is the same in the two light curves.
+For a large enough number of data points $N$, the complex Fourier amplitudes $S_j$ will be composed of a sum of two independent random normal variables: $S_j = S_{sj} + S_{nj}$, with $\Re (S_{sj}) \sim \Normal(0, \sigma_{sj}^2)$ and $\Re(S_{nj}) \sim \Normal(0, \sigma_n^2)$, and similarly for the imaginary parts.
+$\sigma_{sj}^2 = \sigma_{s}^2(\nu) = N_\mathrm{phot}P(\nu)/4$ (where $N_{\mathrm{phot}} = \sum_{k=1}^{N}{x_k}$) is given by the power spectrum of the underlying stochastic process and is frequency-dependent.
+However, $\sigma_n^2 = N_\mathrm{phot}/2$ is not.
+Note that $S_{xsj} = S_{ysj}$, because the amplitudes of the stationary noise process will be the same for the Fourier transforms of $\mathbf{x}$ and $\mathbf{y}$, while the components due to white noise differ between the two time series.
+Moreover, the dead time filter will only depend on the mean count rate, which is again the same in the two light curves.
 Thus, the difference between the Fourier amplitudes for the two time series $\mathbf{x}$ and $\mathbf{y}$ will be:
 \begin{equation}
-F_{xj} - F_{yj} = (S_{xj} - S_{yj})\cdot D_j = (S_{xsj} - S_{ysj} + S_{xnj} - S_{ynj})\cdot D_j
-\end{equation}
-It is important to note that $S_{xsj} = S_{ysj}$, that is, the amplitudes of the stationary noise process will be the same for the Fourier transforms of $\mathbf{x}$ and $\mathbf{y}$, while the components due to white noise differ between the two time series.
-Therefore, 
-\begin{equation}
-F_{xj} - F_{yj} = (S_{xnj} - S_{ynj})\cdot D_j
+F_{xj} - F_{yj} = (S_{xj} - S_{yj})\cdot D_j = (S_{xnj} - S_{ynj})\cdot D_j
 \end{equation}
@@
 But the squared norm of the latter \textit{is also what is distorting the periodograms}!
-However, whereas in the case of periodograms the source signal is mingled with the shape of $|\mathcal{D}|^2$, in this case we have a \textit{constant-scatter} random variable which is modulated by the same shape.
+However, in the case of periodograms the source signal is mingled with the shape of $|\mathcal{D}|^2$, while in this case we have a \textit{constant-scatter} random variable which is modulated by the same shape.
 Therefore, we can try to extract the shape of $|\mathcal{D}|^2$ from the Fourier amplitude differences from the two channels, and use it to correct the shape of the periodogram.
+
 %
@@
 Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec and a dead time of 2.5 ms, as we would expect from two identical detectors observing the same stable X-ray source (Figure ~\ref{fig:fourierdiff}, middle panel).
-The Fourier amplitudes $A_{xj}$ and $A_{yj}$ of the light curves from the two detectors are heavily distorted by dead time, with the characteristic damped oscillator-like shape \citep{Vikhlinin+94,Zhang+95}.
+The Fourier amplitudes of the light curves from the two detectors are heavily distorted by dead time, with the characteristic damped oscillator-like shape \citep{Vikhlinin+94,Zhang+95}. 
 As laid out in Section \ref{sec:fourierdiff}, the difference of Fourier amplitudes from two independent but identical detectors shows no source variability, but \textit{still shows the same distortion} due to dead time.

### 2017-12-11 referee_response.md
Additional point about scatter plot in Fig. 1

Report from Referee:

> At this point, I cannot recommend for publication "No Time for Dead Time - Use of the Fourier Amplitude Differences to Normalize Dead Time-Affected Periodograms" by Bachetti and Hupenkothen. The basic reason is that the paper as written is difficult enough to follow, contains typographical errors, misstatements and mislabelings, has poor figures, to the point that I cannot easily create my own code that reproduces the results exactly as presented in this work. An algorithmic paper like this, to be truly useful, should be sufficiently self-contained and explanatory so as to be easily reproducible.

We thank the referee for the frank report. We do acknowledge that the paper was not as clear as it should have been. However, we do think that a poor description should not be confused with a poor result. The extensive modifications we have done to the manuscript will hopefully demonstrate this. We would like to start this response with the description with a possible critical point: in order to accommodate a thorough discussion of the caveats of the method, we decided to take out the real data example from the paper (Cyg X-1). We realize that this choice might raise some concerns from the referee, as traditionally a paper is considered incomplete without real data. However, we find that the addition of real data does not really add anything to the main focus of the paper, which is the description of a data analysis method that works on any instrument with multiple identical detectors. Besides the reassuring fact of seeing a real periodogram from a real BH candidate, a single example of real data spectrum would not do a better job at showing the method, because it would still be a single example, subject to the usual doubts (is it a cherry-picked example?). The simulation environment we use in the paper mimicks NuSTAR sufficiently well, uses thousands of realizations of simulated NuSTAR power spectra - not just one - and the new additions in the discussion about the difference of flux between the two channels also includes effects of count rate differences that are higher than expected from any reasonable situation found in NuSTAR data (where bright sources are usually dominating the observation and are far from the detector edges). In any case, we are setting up a web page showing off the FAD correction working on real data that we will link in the text.

> I realize that the authors have provided a link to a Jupyter notebook to reproduce the results and figures, and it was sufficient to highlight some of the misstatements made in this paper. However, I have some issues with the adequacy of this, as discussed below.
> In section 2.1, the discussion on creating the lightcurves is insufficient. Yes, it is reasonable to create lightcurves with an existing set of packages, but since these packages are in active development a version number for the packages should be given, or a git hash for the versions used.
> How do I know whether any version I run now or in the future will not be different?

We do agree that it is good practice to refer to a specific version of the codes, so we added the version numbers used.

> More importantly "stingray.simulate.Simulator" class is *not* a description of the methods used. A few sentences describing the mechanics behind each method used is necessary. Likewise, going to the Jupyter notebook and simply seeing "from stingray" and "from hendrics" is not a description. Unless I start following a potentially long chain of imports and start reading code, "stingray" and "hendrics" are black boxes. (In general, the existing Jupyter notebook desperately needs comments in the code.) This can be rectified with short descriptions of the algorithms.

We have added some description of the algorithms, in some cases by referencing Bachetti+15 where some of them were already described in detail (the simulation process is basically the same: model periodogram -> Timmer & Koening method -> light curve -> acceptance-rejection method -> event lists -> dead time filter). We hope the new version will be easier to follow.

> This "clipped" nature of the descriptions carries throughout the paper.
> Section 2.2 the fact that the data is coming from NuSTAR is only in the section header; this is not acceptable.
> The "heasarc_pipelines" packages is only referenced as "ASCL in prep." OK, that's Astrophysics Source Code Library, but who are the authors? I tried a search at ASCL, and that package did not come up.

As we said in the opening, we eliminated the part about NuSTAR data analysis from the paper.

> Section 3, x and y are defined, without explicitly saying that you are specifically considering binned lightcurves of identical length representing the exact same times.
We added this information

> Also in this section the expected Fourier amplitude is given as N_phot P(\nu)/4, and only *later* in the paragraph is it explicitly stated as the Leahy normalization.

The section was basically rewritten.

> (As a side note, I see figures on the Jupyter notebook with the Leahy power of white noise being plotted with values of order 100, which is not what I expect for the Leahy normalization.)

We do not fully grasp this point, and we cannot find a place in the notebook where Leahy power from _white noise_ goes to 100, in which case it might just be a misprint of the axis label. The white noise distributions we plot show precisely how the data points follow the correctchi squared distribution. Moreover, the points where the Leahy power goes to 100 in notebook 2 - if the reviewer is referring to that plot - is heavily distorted by dead time and amplified (around 300 Hz is the maximum of the deadtime positive distortion).

> Later in Section 3, A_xj is written when you mean B_xj.

Rewritten.

> Section 4, Figure 3 is said when you mean Figure 2, and

Corrected, and figures are changed anyway.

> Figure 2a is said to be Fourier Amplitudes vs. Fourier Amplitude Differences, when you actually mean the standard deviation of said quantities. (The Jupyter notebook was useful for figuring this out.)

No, we made a confusing mistake in the plot and the notebook and this needs to be clarified. The only point missing in the text is that the _absolute values_ of the FAD and amplitudes are used, and this is the reason for the apparent lack of negative values. The description with the standard deviation is somehow equivalent, with actually the same factor between the quantities (we tried both approaches in the Jupyter notebook, and we chose the plots inconsistently), but it's not what we use in the actual algorithm (see the implementation in the file fad_correction.py in the notebooks/ directory in the repository).

> Figure 1 caption, you say "Real Fourier amplitudes". Did you mean "actual", or did you mean you're plotting only the "Real" component as opposed to the imaginary component of the amplitudes?

Real part. We tried to be clearer in the new version.

> The are a number of places that you simply write "spectral", and from context it is sometime obvious that you meant power spectral variability, and aren't referring to the spectrum, but with a quick read it could easily be misinterpreted as spectral energy distribution in some cases.

We changed all references to "spectral" in order to clarify that we are talking about variability.

> In the description of applying the correction, the multiplication factor to obtain a Leahy-normalized periodogram is only applicable for a specific normalization of the FFT and whether one has applied the forward or reverse transform. I could go on.

    This point is not very clear to us, but anyway the multiplication factor should work with _any_ normalization of the PDS. The way we calculate the FAD, it is done so that the white noise power spectral values in Leahy normalization flatten to ~two, but the same multiplicative factor would correct other normalizations as well (because the unit is always P x multiplicative factors, in Leahy or the various rms normalizations, and this is just a new multiplicative factor)

> Any one of these issues in isolation could be considered trivial and easily forgiven if fixed. The fact that these issues are numerous and persist throughout the entire paper greatly detracts from the clarity of the presentation.
> The Figures are for the most part very poor. The labels are too small. In some cases (Fig 3d) the ranges are poorly chosen. The order and grouping is confusing. (The left of Figure 1 is not even described in the text, the right of Fig. 1 is more naturally paired with Fig. 2a, and might have made your meaning more clear. Fig. 2b and 2c should probably separated out into their own Figure separate from Fig. 2a.) The figures are too small, and only really readable on a computer screen if zoomed in.

We changed most of the figures in order to select the most effective ones and give them more space.

> In general, there is too much explanation and description crammed into the figure caption, instead of the text. I assume this was in some attempt to obtain a "letter" length. Given rapid electronic publication these days, there often isn't a strong motivation for choosing a letter over a journal article, especially if that means sacrificing both clarity and depth.

We respectfully disagree with this. The text in the figures counts exactly as much as the one in the main text for the ApJL rules, so there is would be no advantage whatsoever from the point of view of obtaining a letter length. We just like the figures to work on their own, without the need to look in the main text for essential information needed to understand them. The figures were quite (probably too) complicated and needed some text to describe them properly. In any case, now most of them have changed.

> And we haven't even gotten to discussing the algorithm. The one major question I have is, what happens if the two lightcurve extractions are in fact not identical? How precisely do the two detectors have to behave identically? This is mentioned at the end of Section 5, but not adequately discussed.

In the new version, we discuss more extensively the details of this, and other caveats, in a section on its own. Basically, the only power spectral measurement that is heavily affected by the count rate difference in the two detectors is the single-channel periodogram. Neither the periodogram obtained by the total-intensity light curve (the sum of the two channels) or the cospectrum are very sensitive to the difference of flux in the two channel. In our simulations the parameter indicating the ratio of flux in the two channels was free to change from 0.5 to 2 (with 1 being the same flux in the two channels), and we find basically indistinguishable distributions if the fluxes in the channels are within ~30% of one another (It can be seen in the simulations in the notebooks). The simulations in figure 5 include channel ratios between 0.8 to 1.3.

> I very well likely might have further comments and questions about the results. As I tried to write my own code to check the figures and results, I had some differences from the figures. This could potentially be my fault. However, after running across poorly worded description after poorly worded description, wondering how Fourier amplitudes vs. Fourier amplitude differences could be so narrowly distributed and not have negative values (i.e., Fig. 2a) until I discovered that the plots were instead standard deviation vs. standard deviation, I simply gave up.

The code to test the algorithm conveniently is (and was) contained in the fad_correction.py file in the notebooks/ directory. There, it was clear that we weren't using the standard deviation, but admittedly, we didn't write a reference to this file in the text.

> Again, this paper should be adequate within itself for me to be able to quickly script a code to reproduce the results. It is not. Once the paper is rewritten, I would be willing to try this experiment again, and see if I agree with the results that are presented.

We hope that the new version will make the referee better appreciate the algorithm.

### 2017-12-11 paper/deadtime.tex
Additional point about scatter plot in Fig. 1

@@
 The different behavior of Fourier amplitude differences under pure Poisson noise and dead time noise is evident, by comparing (a) and (b).
-(c) Scatter distribution of the absolute values of dead time-affected Fourier amplitudes versus the difference of Fourier amplitudes for case (b): their relation is clearly linear, with a factor $1/\sqrt{2}$.
+(c) Scatter distribution of the (averaged over multiple intervals) absolute values of dead time-affected Fourier amplitudes versus the difference of Fourier amplitudes for case (b): their relation is clearly linear, with a factor $1/\sqrt{2}$.
 }

### 2017-12-11 paper/deadtime.tex
Rearrangements and edits, a lot

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%% SECTION 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Data simulation} \label{sec:data}
-All simulated and real data sets in this paper were produced and/or analyzed with a combination of the two Python libraries \texttt{stingray}%
-\footnote{The library is under heavy development.
-    For this work we used the version identified by the hash \texttt{3e64f3d}}
-\citep{huppenkothen2016} and \texttt{HENDRICS} v.\texttt{3.0b2} \citep[formerly known as MaLTPyNT;][]{2015ascl.soft02021B}, both based on Astropy \citep{astropy2013}.
-
-We used the same procedure and algorithms described by \citet{Bachetti+15}, Section 4, that we briefly recall here together with references to the methods and classes of the libraries above where these steps are implemented.
-%The classes in the \texttt{stingray.simulate} module were used to simulate light curves with a given noise profile. 
-We used the \citet{timmer1995} method to create a noise-affected light curve starting from a given power spectral shape. 
-This method is implemented in the \texttt{stingray.simulate} module.
-%We first created the noisy light curves and then used an acceptance-rejection method to obtain simulated events. 
-This step needs to be done carefully: if the initial light curves contain significant random noise, the process for the creation of events creates a random variate on the top of the local count rate - which is varying randomly already - producing a non-Poissonian final light curve.
-So, we initially simulated light curves with a very high ``count rate'' - so that the Poisson noise was relatively small - then renormalized the light curves to the wanted (lower) count rate and \rms and finally used these light curves to simulate event lists using the rejection sampling, implemented in the \texttt{stingray.Eventlist.simulate\_times()} method.
-Finally, the \texttt{hendrics.fake.filter\_for\_deadtime()} function was used to apply a non-paralyzable dead time of 2.5\,ms to the simulated event lists.
-For more details on the simulated data sets, see also Section \ref{sec:correction} and the available Jupyter notebooks%
-\footnote{\href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II}} \citep[for a description of Jupyter notebooks, see][]{kluyver2016jupyter}.
-
-%\subsection{Cyg X-1 \nustar dataset}
-%We tested the method also on real data of several bright sources observed by \nustar.
-%As an example, we report here one such test done on \nustar data of the black hole binary Cyg~X-1 together with the steps to reproduce our analysis, using the linked Jupyter notebook if needed.
-%We downloaded the observation directory of \nustar ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package (Bachetti et al., ASCL identifier requested).
-%Equivalently, this download can be done using the online tools provided by HEASARC (e.g. \texttt{xamin}).
-%Starting from the standard cleaned science event files distributed by HEASARC, we applied a barycenter correction using the FTOOL \texttt{barycorr} shipped with HEASOFT 6.21 with the clock correction file n.
-71 from the \nustar CALDB.
-%We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.%
-%\footnote{To use the method on different sources, it is sufficient to download a different ObsID and change the region file containing the position of the source}.
-%We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and produced light curves with photons from 3 to 79 keV and binned with uniform time bins of 1/4096$\sim2.44\cdot10^{-4}$\,sec%
-%\footnote{This procedure uses the scripts \texttt{HENreadfile}, \texttt{HENcalibrate} and \texttt{HENlcurve}, as described at\\ \href{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}}.
-
-%%%%%%%%%%%%%%%%%%%%%%%% SECTION 3 %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%% SECTION 2 %%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%% SECTION 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{The FAD method} \label{sec:fad}
+\subsection{Data simulation} \label{sec:data}
+All simulated and real data sets in this paper were produced and/or analyzed with a combination of the two Python libraries \texttt{stingray}%
+\footnote{The library is under heavy development.
+    For this work we used the version identified by the hash \texttt{3e64f3d}.
+    See \href{https://github.com/StingraySoftware/notebooks/}{https://github.com/StingraySoftware/notebooks/} for tutorials on simulations, light curve production and timing analysis with Stingray}
+\citep{huppenkothen2016} and \texttt{HENDRICS} v.\texttt{3.0b2} \citep[formerly known as MaLTPyNT;][]{2015ascl.soft02021B}, both based on Astropy \citep{astropy2013}.
+
+We used the same procedure and algorithms described by \citet{Bachetti+15}, Section 4, that we briefly recall here together with references to the methods and classes of the libraries above where these steps are implemented.
+%The classes in the \texttt{stingray.simulate} module were used to simulate light curves with a given noise profile. 
+We used the \citet{timmer1995} method to create a noise-affected light curve starting from a given power spectral shape. 
+This method is implemented in the \texttt{stingray.simulate} module.
+%We first created the noisy light curves and then used an acceptance-rejection method to obtain simulated events. 
+This step needs to be done carefully: if the initial light curves contain significant random noise, the process for the creation of events creates a random variate on the top of the local count rate - which is varying randomly already - producing a non-Poissonian final light curve.
+So, we initially simulated light curves with a very high ``count rate'' - so that the Poisson noise was relatively small - then renormalized the light curves to the wanted (lower) count rate and \rms and finally used these light curves to simulate event lists using the rejection sampling, implemented in the \texttt{stingray.Eventlist.simulate\_times()} method.
+Then, the \texttt{hendrics.fake.filter\_for\_deadtime()} function was used to apply a non-paralyzable dead time of 2.5\,ms to the simulated event lists.
+For more details on the simulated data sets, see also Section \ref{sec:correction} and the available Jupyter notebooks%
+\footnote{\href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II}} \citep[for a description of Jupyter notebooks, see][]{kluyver2016jupyter}.
+After producing these synthetic event lists, we started the standard timing analysis: we produced light curves with a bin time of $\sim0.122$\,ms, and calculated power spectral products (cospectrum, periodogram) over segments of these light curves using \texttt{stingray}.
+
+%\subsection{Cyg X-1 \nustar dataset}
+%We tested the method also on real data of several bright sources observed by \nustar.
+%As an example, we report here one such test done on \nustar data of the black hole binary Cyg~X-1 together with the steps to reproduce our analysis, using the linked Jupyter notebook if needed.
+%We downloaded the observation directory of \nustar ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package (Bachetti et al., ASCL identifier requested).
+%Equivalently, this download can be done using the online tools provided by HEASARC (e.g. \texttt{xamin}).
+%Starting from the standard cleaned science event files distributed by HEASARC, we applied a barycenter correction using the FTOOL \texttt{barycorr} shipped with HEASOFT 6.21 with the clock correction file n.
+71 from the \nustar CALDB.
+%We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.%
+%\footnote{To use the method on different sources, it is sufficient to download a different ObsID and change the region file containing the position of the source}.
+%We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and produced light curves with photons from 3 to 79 keV and binned with uniform time bins of 1/4096$\sim2.44\cdot10^{-4}$\,sec%
+%\footnote{This procedure uses the scripts \texttt{HENreadfile}, \texttt{HENcalibrate} and \texttt{HENlcurve}, as described at\\ \href{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}}.
+
 %%%%%%%%%%%%%%%%%%%%%%%% SECTION 4 %%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Dead time-affected white noise} \label{sec:wndeadtime}
+\subsection{First test: white noise} \label{sec:wndeadtime}
 
@@
 
-Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec and a dead time of 2.5 ms, as we would expect from two identical detectors observing the same stable X-ray source (Figure ~\ref{fig:fourierdiff}, middle panel).
-The Fourier amplitudes of the light curves from the two detectors are heavily distorted by dead time, with the characteristic damped oscillator-like shape \citep{Vikhlinin+94,Zhang+95}. 
+Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec and a dead time of 2.5 ms, as we would expect from two identical detectors observing the same stable X-ray source.
+The Fourier amplitudes of the light curves from the two detectors are heavily distorted by dead time, with the characteristic damped oscillator-like shape \citep{Vikhlinin+94,Zhang+95}  (Figure ~\ref{fig:fourierdiff}, middle panel).
 As laid out in Section \ref{sec:fourierdiff}, the difference of Fourier amplitudes from two independent but identical detectors shows no source variability, but \textit{still shows the same distortion} due to dead time.
@@
 Starting from a heavily distorted distribution of the powers, applying the FAD correction ``flattens'' remarkably well the white noise level of the periodogram and the distribution of the scatter of the white noise periodogram and cospectrum.
-Also, it reinstates a remarkably correct distribution of powers, following the expected $\chi^2_2$ distribution \citep{Lewin+88} very closely. 
+Also, it reinstates a correct distribution of powers, following the expected $\chi^2_2$ distribution \citep{Lewin+88} very closely. 
 Analogously, the corrected cospectrum will follow the expected Laplace distribution \citep{Huppenkothen & Bachetti, sub.}.
@@
 
-\section{The FAD correction algorithm} \label{sec:fad}
+\subsection{The FAD algorithm in detail} \label{sec:fad}
 In practice, the FAD correction algorithm in a generic case would work as follows:
@@
 %%%%%%%%%%%%%%%%%%%%%%%% SECTION 6 %%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Testing the FAD correction on simulated data} \label{sec:correction}
+\subsection{FAD correction of generic variable periodograms} \label{sec:correction}
 
@@
 
-\section{Caveats}\label{sec:caveat}
+\subsection{Simulation results and discussion}\label{sec:caveat}
 \begin{figure*}
-    \plotone{imgs/errors.png}
+    \plotone{imgs/errors.pdf}
     \caption{Relative overestimation of FAD with respect to \rms, versus \rms, as calculated from the cospectrum.  
@@
 \end{figure*}
-The simulations show that the shape of the periodogram is precisely corrected by the FAD procedure \textit{if the input light curves have the same count rate} and \textit{for values of the input count rate and \rms that are not too extreme}.
-The first caveat turns out to be an issue only for the single-channel periodogram. 
+
+The simulations show that the shape of the periodogram is precisely corrected by the FAD procedure if (1) \textit{the input light curves have the same count rate} and (2) \textit{for values of the input count rate and \rms that are not too extreme}.
+The first caveat turns out, in practice, to be only a big issue for the single-channel periodogram, but \textit{not} for cospectra and total-intensity periodograms. 
 At high count rates, single-channel periodograms are corrected very well only if the two channels have very similar count rates, with the requirement being unsurprisingly stricter and stricter as the count rate increases.
-However, we find that the total-intensity periodogram and the cospectrum remains well corrected by the FAD even if the count rate in the two channels differs by 30\%, for any reasonable count rate.
+However, we find that the total-intensity periodogram and the cospectrum remains well corrected by the FAD even if the count rate in the two channels differs by 30\% in most cases.
 Therefore, we recommend to use the FAD very carefully with single-channel periodograms, which should not be an issue given that the total-intensity periodogram is more sensitive and more convenient to use anyway.
-A comparison with the cospectrum, that is not affected by white noise distortions, is always recommended.
+A comparison with the cospectrum, that is not affected by white noise level distortions, is always recommended.
 
@@
 We find that the FAD correction consistently overestimates the integrated \rms when the count rate and \rms are \textit{both} very high, \textit{in particular at low frequency} (See Figure~\ref{fig:errors}).
-At standard count rates and fractional \rms for bright black hole binaries, $\sim$200 ct/s and 30\% \rms for the \nustar case, the relative error is below 5\% (meaning that if the \rms is 30\%, the measured \rms is between 30 and 32\%!) and it is symmetrically distributed around 0, as expected from statistical error.
+At $\sim$200 ct/s and 30\% \rms, the relative error is below 5\% (meaning that if the \rms is 30\%, the measured \rms is between 30 and 32\%!) and it is symmetrically distributed around 0, as expected from statistical errors.
 At higher incident rates and \rms, the error distribution skews towards positive relative errors, implying an overestimation of the \rms.
 This should not be a problem in most cases, where the \rms is used as a rough indicator for spectral state.
-If very precise measurements of \rms are needed (for example, to calculate \rms/energy spectra), it is somewhat safer to account for this through simulations, without having to make further risky frequency-dependent corrections to the \rms.
-As a rough estimate, the relative error on the fractional \rms increases \textit{linearly} with the count rate and \textit{quadratically} with real \rms.
+If very precise measurements of \rms are needed (for example, to calculate \rms/energy spectra), it is safer to account for this through simulations.
+As a rough rule-of-thumb, the relative error on the fractional \rms increases \textit{linearly} with the count rate and \textit{quadratically} with \rms.
 A practical way to estimate this effect during analysis is to apply the FAD, obtain a best fit model, calculate the \rms, then use the codes we shared with the Jupyter notebooks to simulate a number of realizations of the light curve, evaluating what is the amount of overestimation involved.
@@
 However, the white noise level subtraction is not always very precise due to mismatches in the mean count rate in the two light curves. 
-A comparison with the FAD-corrected cospectrum, to verify visually the white noise subtraction, is always recommended.
-It is important to be reasonably sure of the white noise level of the periodogram, as the white noise subtraction is the most important step when calculating the significance of a given feature in the periodogram \citep[e.g.][]{Barret+12,Huppenkothen+17}.
-The cospectrum has the advantage of not requiring white noise level subtraction.
+A comparison with the FAD-corrected cospectrum, to verify visually the white noise subtraction, is always recommended: the white noise subtraction is the most important step when calculating the significance of a given feature in the periodogram \citep[e.g.][]{Barret+12,Huppenkothen+17}.
+The cospectrum has indeed the advantage of not requiring white noise level subtraction.
 
+A number of jupyter notebooks is available the address \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the full analysis plotted in the Figures of this paper, plus more examples of application of these techniques to simulated and real data.
+The full algorithm described in Section~\ref{sec:fad} is contained in the \texttt{fad\_correction.py} file in the notebooks directory, for reference.
 In all cases, we find that the adjustment of the white noise standard deviation in the periodogram and the cospectrum works remarkably well, allowing to make a confident analysis of X-ray variability even in sources where this was precluded until now.
-The only 
+Only in cases where the count rate and the \rms are \textit{both} very high (>1000 ct/s incident, >40\% resp.), the FAD correction leads to an overestimation the \rms, even if the white noise level of the periodogram remains flat.
+In these case, we provide some example simulation code to estimate this effect in the notebooks.
 This software will be merged into the main repository of \texttt{stingray} before publication.
-A number of jupyter notebooks will also be posted at the address \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the full analysis plotted in the Figures of this paper, plus more examples of application of these techniques to simulated and real data.
-The full algorithm described in Section~\ref{sec:fad} is contained in the \texttt{fad\_correction.py} file in the notebooks directory, for reference.
 

### 2017-12-11 paper/deadtime.tex
Various edits

@@
 In all cases, we find that the adjustment of the white noise standard deviation in the periodogram and the cospectrum works remarkably well, allowing to make a confident analysis of X-ray variability even in sources where this was precluded until now.
-Only in cases where the count rate and the \rms are \textit{both} very high (>1000 ct/s incident, >40\% resp.), the FAD correction leads to an overestimation the \rms, even if the white noise level of the periodogram remains flat.
+Only in cases where the count rate and the \rms are \textit{both} very high ($>$500 ct/s incident, $>$40\% resp.), the FAD correction leads to an overestimation the \rms, even if the white noise level of the periodogram remains flat.
 In these case, we provide some example simulation code to estimate this effect in the notebooks.

### 2017-12-11 referee_response.md
Minor edits

@@
 We do not fully grasp this point, and we cannot find a place in the notebook where Leahy power from _white noise_ goes to 100, in which case it might just be a misprint of the axis label.
-The white noise distributions we plot show precisely how the data points follow the correctchi squared distribution.
+The white noise distributions we plot show precisely how the data points follow the correct chi squared distribution.
 Moreover, the points where the Leahy power goes to 100 in notebook 2 - if the reviewer is referring to that plot - is heavily distorted by dead time and amplified (around 300 Hz is the maximum of the deadtime positive distortion).
@@
 
-In the new version, we discuss more extensively the details of this, and other caveats, in a section on its own.
+In the new version, we discuss more extensively the details of this, and other caveats, in a subsection on its own.
 Basically, the only power spectral measurement that is heavily affected by the count rate difference in the two detectors is the single-channel periodogram.

### 2017-12-12 notebooks/fad_correction.py
First revision mb (#1)
First revision - MB

@@ -11,6 +11,8 @@ from hendrics.io import load_events
 from scipy.ndimage.filters import gaussian_filter1d
 from scipy.interpolate import UnivariateSpline
 import copy
+import logging
+import pytest
 
 
 def _get_fourier_intv(lc, start_ind, end_ind):
@@ -21,12 +23,48 @@ def _get_fourier_intv(lc, start_ind, end_ind):
 
     freq = scipy.fftpack.fftfreq(len(time), lc.dt)
     good = freq > 0
-# #     print("Bu", factor, countrate_factor, counts[:10], counts_r_out[:10], fourier[:10])
 
     return freq[good], fourier[good], fourier[good] * np.sqrt(2 / (np.sum(counts)))
 
 
-def FAD_power_spectra(lc1, lc2, segment_size, plot=False, smoothing_alg='gauss'):
+def FAD_power_spectra(lc1, lc2, segment_size, plot=False, smoothing_alg='gauss',
+                      smoothing_length=None, verbose=False, tolerance=0.05,
+                      strict=False, all_leahy=False):
+    """Calculate Frequency Amplitude Difference-corrected (cross) power spectra.
+
+    Parameters
+    ----------
+    lc1: class:`stingray.ligthtcurve.Lightcurve`
+    lc1: class:`stingray.ligthtcurve.Lightcurve`
+    segment_size: float
+        Length of the segments to be averaged
+
+    Other parameters
+    ----------------
+    plot : bool
+        Plot diagnostics
+    smoothing_alg : {'gauss', 'spline'}
+        Smoothing algorithm
+    smoothing_length : int
+        Number of bins to smooth in gaussian window smoothing
+    verbose: bool
+        Print out information on the outcome of the algorithm (recommended)
+    tolerance : float
+        Accepted relative error on the FAD-corrected Fourier amplitude, to be
+        used as success diagnostics.
+        Should be
+        ```
+        stdtheor = 2 / np.sqrt(n)
+        std = (average_corrected_fourier_diff / n).std()
+        np.abs((std - stdtheor) / stdtheor) < tolerance
+    strict : bool
+        Fail if condition on tolerance is not met.
+
+    Returns
+    -------
+    """
+    if smoothing_length is None:
+        smoothing_length = segment_size * 3
[…]

### 2017-12-12 notebooks/plot_all_trials.py

@@ -1,0 +1,405 @@
+from pandas import read_csv
+import matplotlib.pyplot as plt
+import numpy as np
+import sys
+import time
+import logging
+from watchdog.observers import Observer
+from watchdog.events import LoggingEventHandler
+from watchdog.events import PatternMatchingEventHandler
+from hendrics.base import r_in, r_det
+import warnings
+warnings.filterwarnings('ignore')
+
+
+def plot_scatter_ratios(results, channel, toler_d_clean=0.01,
+                            filter={}):
+
+    plt.figure()
+    plt.title(channel)
+    plt.axhline(0.0, ls='-')
+    plt.axvline(1.0, ls='-')
+
+    good_clean = np.abs(results['delta clean']) < toler_d_clean
+    minrate, maxrate = np.min(results['incident_rate']), np.max(results['incident_rate'])
+    colors = results['incident_rate'] / maxrate
+    for segsize in list(set(results['segment size'][good_clean])):
+        good_segsize = results['segment size'] == segsize
+        good = good_segsize & good_clean
+        marker = np.int(np.log2(segsize)//2)
+        plt.scatter(results['channel_ratio'][good], results[channel][good],
+                    c=colors[good],
+                    s=10 * results['length'][good] / np.min(results['length'][good]),
+                    marker=(marker, 0), cmap='magma')
+        plt.xlabel('Ratio of flux in the two channels')
+        plt.ylabel('Relative change of measured rms'
+                   ' ({} - clean)/clean'.format(channel))
+    plt.colorbar()
+
+
+def plot_all(file, toler_d_clean=0.01):
+    results = read_csv(file)
+
+    plot_scatter_ratios(results, 'delta clean', toler_d_clean=toler_d_clean)
+    plot_scatter_ratios(results, 'CS', toler_d_clean=toler_d_clean)
+    plot_scatter_ratios(results, 'PDS 1', toler_d_clean=toler_d_clean)
+    plot_scatter_ratios(results, 'PDStot', toler_d_clean=toler_d_clean)
+
+
+def pairplot(file, toler_d_clean=0.5, filters={'channel_ratio': [0.8, 1.2]}):
+    from seaborn import pairplot
+    results = read_csv(file)
+    good_clean = np.abs(results['delta clean']) < toler_d_clean
[…]

### 2017-12-12 referee_response.md
Minor edits here and there

@@
 
-We thank the referee for the frank report.
+We thank the referee for the frank report, that allowed to improve the paper significantly.
 We do acknowledge that the paper was not as clear as it should have been.
-However, we do think that a poor description should not be confused with a poor result.
+However, we also do think that a poor description should not be confused with a poor result.
 The extensive modifications we have done to the manuscript will hopefully demonstrate this.
-We would like to start this response with the description with a possible critical point: in order to accommodate a thorough discussion of the caveats of the method, we decided to take out the real data example from the paper (Cyg X-1).
+We would like to start this response with the description of a possible critical point: in order to accommodate a thorough discussion of the caveats of the method, we decided to take out the real data example from the paper (Cyg X-1).
 We realize that this choice might raise some concerns from the referee, as traditionally a paper is considered incomplete without real data.
-However, we find that the addition of real data does not really add anything to the main focus of the paper, which is the description of a data analysis method that works on any instrument with multiple identical detectors.
+However, we find that the addition of real data does not really add anything to the main focus of the paper, which is the description of a data analysis method that works on any instrument with multiple identical detectors (it will still work practically unmodified with IXPE, that will probably have a dead time only slightly shorter than NuSTAR, and of course Astrosat etc.), and will be very useful to the community.
 Besides the reassuring fact of seeing a real periodogram from a real BH candidate, a single example of real data spectrum would not do a better job at showing the method, because it would still be a single example, subject to the usual doubts (is it a cherry-picked example?).
@@
 
-We have added some description of the algorithms, in some cases by referencing Bachetti+15 where some of them were already described in detail (the simulation process is basically the same: model periodogram -> Timmer & Koening method -> light curve -> acceptance-rejection method -> event lists -> dead time filter).
+We have added some description of the algorithms, in some cases by referencing Bachetti+15 where some of them were already described in detail (the simulation process is basically the same: model periodogram -> Timmer & Koening method -> light curve -> acceptance-rejection method -> clean event lists -> dead time filter -> final event lists).
 We hope the new version will be easier to follow.
@@
 
-The section was basically rewritten.
+The section was basically rewritten, but we did pay attention to specifying the normalization of P the first time it is mentioned.
 
@@
 No, we made a confusing mistake in the plot and the notebook and this needs to be clarified.
-The only point missing in the text is that the _absolute values_ of the FAD and amplitudes are used, and this is the reason for the apparent lack of negative values.
+The only point missing in the text is that the _mean absolute values_ of the FAD and amplitudes in each frequency bin are used, and this is the reason for the apparent lack of negative values.
 The description with the standard deviation is somehow equivalent, with actually the same factor between the quantities (we tried both approaches in the Jupyter notebook, and we chose the plots inconsistently), but it's not what we use in the actual algorithm (see the implementation in the file fad_correction.py in the notebooks/ directory in the repository).

### 2017-12-12 paper/deadtime.tex
Put everything in submittable format
Minor edits here and there

@@
 \begin{figure*}
-\gridline{\fig{imgs/rn_fourierdiff.eps}{0.33\textwidth}{(a)}
-	\fig{imgs/wn_fourierdiff.eps}{0.33\textwidth}{(b)}
-	\fig{imgs/fourier_vs_diff_dt.eps}{0.33\textwidth}{(c)}}
+\gridline{\fig{rn_fourierdiff.eps}{0.33\textwidth}{(a)}
+	\fig{wn_fourierdiff.eps}{0.33\textwidth}{(b)}
+	\fig{fourier_vs_diff_dt.eps}{0.33\textwidth}{(c)}}
 
@@
 For a stochastic process (e.g.\ $1/\nu$-type red noise), the Fourier amplitudes will vary as a function of $N_{\mathrm{phot}}P(\nu)/4$, where $P(\nu)$ (Leahy-normalized, \citealt{Leahy+83}) is the shape of the power spectrum underlying the stochastic process, and $N_{\mathrm{phot}}$ denotes the number of photons in a light curve.
-If the two detectors observe the same source simultaneously, the amplitudes and phases of the stochastic process will be shared among $\mathbf{x}$ and $\mathbf{y}$, while each light curve will be affected \textit{independently} by both the photon counting noise in the detector, as well as the dead time process.
+If the two detectors observe the same source simultaneously, the amplitudes and phases of the stochastic process will be shared among $\mathbf{x}$ and $\mathbf{y}$, while each light curve will be affected \textit{independently} by the photon counting noise in the detector, as well as the dead time process.
 Dead time can be considered a convolution on the signal \citep{Vikhlinin+94}. 
@@
 Note that $S_{xsj} = S_{ysj}$, because the amplitudes of the stationary noise process will be the same for the Fourier transforms of $\mathbf{x}$ and $\mathbf{y}$, while the components due to white noise differ between the two time series.
-Moreover, the dead time filter will only depend on the mean count rate, which is again the same in the two light curves.
+Moreover, the dead time filter will only depend on the count rate, which is again the same in the two light curves.
 Thus, the difference between the Fourier amplitudes for the two time series $\mathbf{x}$ and $\mathbf{y}$ will be:
@@
 But the squared norm of the latter \textit{is also what is distorting the periodograms}!
-However, in the case of periodograms the source signal is mingled with the shape of $|\mathcal{D}|^2$, while in this case we have a \textit{constant-scatter} random variable which is modulated by the same shape.
+However, in the case of periodograms the source power spectrum is mingled with the shape of $|\mathcal{D}|^2$, while in this case we have a \textit{constant-scatter} random variable which is modulated by the same shape.
 Therefore, we can try to extract the shape of $|\mathcal{D}|^2$ from the Fourier amplitude differences from the two channels, and use it to correct the shape of the periodogram.
@@
 \begin{figure*}
-\plotone{imgs/before_and_after.eps}
-%\plotone{imgs/pds_pdf.pdf}
+\plotone{before_and_after.eps}
+%\plotone{pds_pdf.pdf}
 \caption{Periodogram and cospectrum, before and after FAD correction, for a pure white noise light curve. 
@@
 \begin{figure*}
-\plotone{imgs/pds_pdf.pdf}
+\plotone{pds_pdf.pdf}
 \caption{PDF of non-averaged powers in the cospectrum (red) and the periodogram (black), before the FAD correction and after, shown as a histogram. 
@@
 
-Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec and a dead time of 2.5 ms, as we would expect from two identical detectors observing the same stable X-ray source.
+As laid out in Section \ref{sec:fourierdiff}, the difference of Fourier amplitudes from two independent but identical detectors shows no source variability, but \textit{still shows the same distortion} due to dead time (See Figure ~\ref{fig:fourierdiff}, left panel, where this is shown with red noise).
+Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec and a dead time of 2.5 ms, as we would expect from the two identical detectors of \nustar observing the same stable X-ray source.
 The Fourier amplitudes of the light curves from the two detectors are heavily distorted by dead time, with the characteristic damped oscillator-like shape \citep{Vikhlinin+94,Zhang+95}  (Figure ~\ref{fig:fourierdiff}, middle panel).
-As laid out in Section \ref{sec:fourierdiff}, the difference of Fourier amplitudes from two independent but identical detectors shows no source variability, but \textit{still shows the same distortion} due to dead time.
-Therefore, using the difference between the Fourier amplitudes in two detectors, we can in principle renormalize the power spectrum so that only the source variability alters its otherwise flat shape.
+Therefore, using the difference between the Fourier amplitudes in two detectors, we can in principle renormalize the periodogram so that only the source variability alters its otherwise flat shape.
 
-As shown in Figure~\ref{fig:fourierdiff} (right panel), the single-channel Fourier amplitudes are proportional to the difference of the Fourier amplitudes in different realizations, with a constant factor $1/\sqrt{2}$.
+As shown in Figure~\ref{fig:fourierdiff} (right panel), the single-channel Fourier amplitudes are proportional on average to the difference of the Fourier amplitudes in different realizations, with a constant factor $1/\sqrt{2}$.
 Therefore, we expect that the periodogram will be proportional to the square of the Fourier amplitude difference, divided by 2.
-Let us try to \textit{divide the power spectrum by a smoothed version of the squared Fourier differences}, and multiply by 2.
+Let us try to \textit{divide the periodogram by a smoothed version of the squared Fourier differences}, and multiply by 2.
 For smoothing, we used a Gaussian running window with a window width of 50 bins.
@@
 
-The correction is depicted in Figure~\ref{fig:comparison}. 
+The results of this correction are shown in Figure~\ref{fig:comparison}. 
 Starting from a heavily distorted distribution of the powers, applying the FAD correction ``flattens'' remarkably well the white noise level of the periodogram and the distribution of the scatter of the white noise periodogram and cospectrum.
 Also, it reinstates a correct distribution of powers, following the expected $\chi^2_2$ distribution \citep{Lewin+88} very closely. 
-Analogously, the corrected cospectrum will follow the expected Laplace distribution \citep{Huppenkothen & Bachetti, sub.}.
+Analogously, the corrected cospectrum will follow the expected Laplace distribution (Huppenkothen \& Bachetti, sub.).
 While the original dead time-affected cospectrum had a frequency-dependent modification to the \rms level, the FAD-corrected cospectrum gets back to a frequency-independent shape, like in the dead time-free case.
@@
 \begin{figure*}
-    \plotone{imgs/four_qpos.eps}
+    \plotone{four_qpos.eps}
     \caption{Periodograms and cospectra from a simulation with four Lorentzian features (at 50, 200, 300 and 400 Hz) with 40-Hz full with at half maximum (FWHM). 
@@
 
-We are now ready to verify the last step: is the FAD-corrected power spectrum equivalent (albeit with some loss of sensitivity due to the lower number of photons) to the dead time-free power spectrum?
+We are now ready to verify the last step: is the FAD-corrected periodogram equivalent (albeit with some loss of sensitivity due to the lower number of photons) to the dead time-free periodogram?
 To test this, we produced a number of different synthetic datasets as explained in Section~\ref{sec:wndeadtime}, containing different combinations of QPOs and broadband noise components. 
@@
 \begin{figure*}
-    \plotone{imgs/errors.pdf}
+    \plotone{errors.pdf}
     \caption{Relative overestimation of FAD with respect to \rms, versus \rms, as calculated from the cospectrum.  
@@
     Over $\sim$40\% fractional \rms, the errors are significantly skewed towards an overestimation of the \rms, and this is 
-    clearly truer when the incident rate \textit{and} the \rms are high.}
+    clearly truer when the incident rate \textit{and} the \rms are high, and the frequency relatively low.}
     \label{fig:errors}

### 2017-12-12 paper/deadtime.tex
New figures

@@
 In the special case where dead time is constant, its shape can be modeled precisely \citep{Zhang+95,Vikhlinin+94}.
-However, dead time is often different on an event-to-event basis, and it is not obvious how to model it precisely, also because the information on dead time is often incomplete in the data files distributed by HEASARC%
-\footnote{Whereas in principle this information could be obtained by using the PRIOR column in the unfiltered event files for some missions, the live time given in this column is affected by events that are not recorded in the file, like shield vetos in the case of \nustar, and the estimate of dead time is necessarily uncertain}%
-.
-For a more thorough discussion about different dead time behaviors see \citet{Zhang+95}.
+However, dead time is often different on an event-to-event basis (e.g., in \nustar), and it is not obvious how to model it precisely, also because the information on dead time is often incomplete in the data files distributed by HEASARC \citep[see, e.g.][]{Bachetti+15}.
+%\footnote{Whereas in principle this information could be obtained by using the PRIOR column in the unfiltered event files for some missions, the live time given in this column is affected by events that are not recorded in the file, like shield vetos in the case of \nustar, and the estimate of dead time is necessarily uncertain}%
+
+%For a more thorough discussion about different dead time behaviors see \citet{Zhang+95}.
 
@@
 Whereas a noise cospectrum in the absence of dead time would follow a Laplace distribution (Huppenkothen and Bachetti, sub.),
-dead time affects the width of the probability distribution for cospectral powers and modulates the measured \rms proportionally to the distortion acted on power spectra.
+dead time affects the width of the probability distribution for cospectral powers and modulates the measured \rms similarly to the distortion acted on power spectra.
 In this Letter, we show a method to precisely recover the shape of the power density spectrum by looking at the difference of the Fourier amplitudes of the light curves of two independent detectors.
@@
 
-In \sref{sec:data} we briefly describe our data analysis and simulation setup.
-In \sref{sec:fourierdiff} we show that, in the absence of dead time, the Fourier amplitudes of two independent detectors contain the sum of the correlated signal (the source signal) and uncorrelated noise (detector-related noise), and that their difference eliminates the source part.
-In \sref{sec:wndeadtime} we show that, in the presence of dead time, the difference of the Fourier amplitude still eliminates the source signal but retains information on dead time effects.
-In \sref{sec:correction} we show that this can be used to recover the dead noise-free power spectrum.
+In \sref{sec:fourierdiff} we show that, in the absence of dead time, the difference of the Fourier amplitudes calculated  two independent detectors contain the sum of the correlated signal (the source signal) and uncorrelated noise (detector-related noise), and that their difference eliminates the source part.
+In \sref{sec:fadsec} we use extensive simulations to show how to use this fact to correct deadtime-affected periodograms, and we describe the limitations of this method.
 
@@
 However, in the case of periodograms the source power spectrum is mingled with the shape of $|\mathcal{D}|^2$, while in this case we have a \textit{constant-scatter} random variable which is modulated by the same shape.
-Therefore, we can try to extract the shape of $|\mathcal{D}|^2$ from the Fourier amplitude differences from the two channels, and use it to correct the shape of the periodogram.
+Therefore, we can try to extract the shape of $|\mathcal{D}|^2$ from the Fourier amplitude differences from the two channels, and use it to correct the shape of the periodogram, and in Section~\ref{sec:caveat} we describe the limits of the method.
 
@@
 
-\section{The FAD method} \label{sec:fad}
+\section{The FAD method} \label{sec:fadsec}
 \subsection{Data simulation} \label{sec:data}
@@
 \acknowledgments
-We thank David W. Hogg for useful discussions on the topic of Fourier analysis.
+We thank the anonymous referee for coping with the first version of this paper without trashing it.
+We thank David W. Hogg for useful discussions on the topic of Fourier analysis, and Jeff Scargle for useful suggestions and comments.
 MB is supported in part by the Italian Space Agency through agreement ASI-INAF n.2017-12-H.0 and ASI-INFN agreement n.2017-13-H.0.

### 2017-12-12 paper/deadtime.tex
Cut down some text

@@
 
-A number of jupyter notebooks is available the address \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the full analysis plotted in the Figures of this paper, plus more examples of application of these techniques to simulated and real data.
+A number of jupyter notebooks is available the address \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the full analysis plotted in the Figures of this paper and more.
 The full algorithm described in Section~\ref{sec:fad} is contained in the \texttt{fad\_correction.py} file in the notebooks directory, for reference.
@@
 Belloni, T., \& Hasinger, G. 1990, A{\&}A, 230, 103
-
-\bibitem[{Bowyer {et~al.}(1965)Bowyer, Byram, Chubb, \& Friedman}]{Bowyer+65}
-Bowyer, S., Byram, E.~T., Chubb, T.~A., \& Friedman, H. 1965, Astronomical
-  Observations from Space Vehicles, 23, 227
-
-\bibitem[{Gilfanov {et~al.}(2000)Gilfanov, Churazov, \&
-  Revnivtsev}]{Gilfanov+00}
-Gilfanov, M., Churazov, E., \& Revnivtsev, M. 2000, MNRAS, 316, 923
-
-\bibitem[{Grinberg {et~al.}(2013)Grinberg, Hell, Pottschmidt, B{\"o}ck, Nowak,
-  Rodriguez, Bodaghee, Cadolle~Bel, Case, Hanke, K{\"u}hnel, Markoff, Pooley,
-  Rothschild, Tomsick, Wilson-Hodge, \& Wilms}]{Grinberg+13}
-Grinberg, V., Hell, N., Pottschmidt, K., {et~al.} 2013, 554, 88
 

### 2017-12-13 notebooks/simulations.py
Add simulations code

@@ -1,0 +1,885 @@
+from __future__ import print_function, division
+
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import seaborn as sns
+from astropy.table import Table
+import shutil
+
+sns.set_context('talk')
+sns.set_style("whitegrid")
+sns.set_palette("colorblind")
+
+mpl.rcParams['font.size'] = 18.0
+mpl.rcParams['xtick.labelsize'] = 18.0
+mpl.rcParams['ytick.labelsize'] = 18.0
+mpl.rcParams['axes.labelsize'] = 18.0
+mpl.rcParams['axes.labelsize'] = 18.0
+
+from scipy.optimize import curve_fit
+
+import copy
+from hendrics.fake import filter_for_deadtime
+
+from astropy.modeling.models import Lorentz1D, Const1D
+import numpy as np
+
+from hendrics.base import r_in, r_det
+from stingray.modeling.posterior import GaussianLogLikelihood
+from stingray.modeling.parameterestimation import ParameterEstimation
+import os
+import glob
+from pandas import read_csv
+
+np.random.seed(348172694)
+
+from stingray import Lightcurve, Crossspectrum
+from stingray.simulator.simulator import Simulator
+
+from hendrics.io import load_pds, save_pds
+from stingray import AveragedPowerspectrum, AveragedCrossspectrum
+from stingray.events import EventList
+from scipy.stats import linregress
+from plot_all_trials import *
+from fad_correction import *
+
+
+def create_model_lightcurve(model, tstart=0, tstop=8192, dt=1/8192,
+                            mean_ctrate=200, rms=0.25):
+
+    time = np.arange(tstart, tstop, dt)
+
+    # The current normalization is not precise for very high count rates!
+    sim = Simulator(N=len(time), dt=dt, rms=1,
+                    mean=10000, red_noise=3)
+    sim_lc_clean = sim.simulate(model)
+
+    # Correct normalization
+    sim_lc_clean.counts -= np.mean(sim_lc_clean.counts)
+    factor = rms / np.std(sim_lc_clean.counts)
+    sim_lc_clean.counts *= factor
+    sim_lc_clean.counts += 1
+    sim_lc_clean.counts *= mean_ctrate
+
+    sim_lc_clean.counts *= dt
+
+    return sim_lc_clean
+
+
+def create_event_lists_from_lightcurve(lc_in, channel_ratio=1):
+    # work on a copy, not on the original light curve
[…]

### 2017-12-13 notebooks/simulations.py
New figure 1

@@ -881,5 +881,3 @@ def fit_pds_slope_vs_rms(file, toler_d_clean=0.01,
     cb = mpl.colorbar.ColorbarBase(ax2, cmap=cmap, norm=norm)
     cb.set_label('Fractional rms')
 
-
-

### 2017-12-13 paper/deadtime.tex
New figure 1

@@
 \begin{figure*}
-\gridline{\fig{rn_fourierdiff.eps}{0.33\textwidth}{(a)}
-	\fig{wn_fourierdiff.eps}{0.33\textwidth}{(b)}
-	\fig{fourier_vs_diff_dt.eps}{0.33\textwidth}{(c)}}
-
-\caption{(a) and (b): Real-valued Fourier amplitudes obtained by single light curves (top panels) and difference between two realizations of the same source light curve (bottom) in two cases: (a) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (b) no red noise and strong dead time, calculated over many 5\,s segments of the light curve.
+\plottwo{rn_fourierdiff}{wn_fourierdiff}
+\caption{Real-valued Fourier amplitudes obtained by single light curves ($\mathcal{F}_1$) and difference between two realizations of the same source light curve ($\mathcal{F}_1 - \mathcal{F}_2$), plotted against each other in two cases: (Left) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (Right) no red noise and strong dead time, calculated over 5\,s segments of the light curve.
 The red curve gives the frequency-dependent spread of the distributions, measured by the mean of the absolute values of the curves in each frequency bin. 
-The different behavior of Fourier amplitude differences under pure Poisson noise and dead time noise is evident, by comparing (a) and (b).
-(c) Scatter distribution of the (averaged over multiple intervals) absolute values of dead time-affected Fourier amplitudes versus the difference of Fourier amplitudes for case (b): their relation is clearly linear, with a factor $1/\sqrt{2}$.
+The different behavior of Fourier amplitude differences in the two cases is evident: in the deadtime-free case, the Fourier amplitude difference does \textit{not} correlate with the Fourier amplitude, while in the deadtime-affected case, this follows a precise linear relationship.
 }

### 2017-12-15 paper/deadtime.tex
New figure 5
Some wording changes and comments

@@
 \newcommand{\word}{\ensuremath{\phi}\xspace}
+
+\newcommand{\DHN}[1]{\textcolor{green}{DH:~#1}\normalcolor{}}
 
@@
 Being roughly energy-independent, dead time is not usually an issue for spectroscopy, as it only affects the maximum rate of photons that can be recorded, so it basically only increases the observing time needed for high quality spectra.
+
 For timing analysis, the effect of dead time is far more problematic.
@@
 \section{On the difference of Fourier amplitudes} \label{sec:fourierdiff}
-\begin{figure*}
-\plottwo{rn_fourierdiff}{wn_fourierdiff}
-\caption{Real-valued Fourier amplitudes obtained by single light curves ($\mathcal{F}_1$) and difference between two realizations of the same source light curve ($\mathcal{F}_1 - \mathcal{F}_2$), plotted against each other in two cases: (Left) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (Right) no red noise and strong dead time, calculated over 5\,s segments of the light curve.
-The red curve gives the frequency-dependent spread of the distributions, measured by the mean of the absolute values of the curves in each frequency bin. 
-The different behavior of Fourier amplitude differences in the two cases is evident: in the deadtime-free case, the Fourier amplitude difference does \textit{not} correlate with the Fourier amplitude, while in the deadtime-affected case, this follows a precise linear relationship.
-}
-\label{fig:fourierdiff}
-\end{figure*}
+%\begin{figure*}
+%\gridline{\fig{rn_fourierdiff.eps}{0.33\textwidth}{(a)}
+%	\fig{wn_fourierdiff.eps}{0.33\textwidth}{(b)}
+%	\fig{fourier_vs_diff_dt.eps}{0.33\textwidth}{(c)}}      
+%\caption{(a): Real-valued Fourier amplitudes derived from many evenly sampled light curves of $500\,\mathrm{s}$ duration with strong $1/f$ red noise (top, in black).
+On the bottom, we show the \textit{difference} between real-valued Fourier amplitudes as they would be sampled from two independent detectors using the same light curves as in the top panel.
+In red, we show the the frequency-dependent spread of the distributions, measured by the mean of the absolute values of the curves in each frequency bin.
+Panel (b) shows the same as panel (a), but using white noise light curves of $5\,\mathrm{s}$ duration affected by dead time.
+In the case of red noise without dead time, the difference in Fourier amplitudes effectively follows a white noise distribution.
+Because dead time affects the observed light curves \textit{in the detector} (while red noise is intrinsic to the source), the difference in Fourier amplitudes will still contain the dead time contribution to the Fourier amplitudes, and can thus be used to effectively separate real variability from spurious dead time effects.
+%(c) Scatter distribution of the (averaged over multiple intervals) absolute values of dead time-affected Fourier amplitudes versus the difference of Fourier amplitudes for case (b): their relation is clearly linear, with a factor $1/\sqrt{2}$.
+\DHN{I don't really understand what (c) adds.
+Also, why 500s segments in (a) and 5s segments in (b)?}}
+%\label{fig:fourierdiff}
+%\end{figure*}
 
-Let us consider two identical and independent detectors observing the same variable source, producing independent and strictly simultaneous time series, with identical binning, $\mathbf{x} = \{x_k\}_{k=1}^N$ and $\mathbf{y} = \{y_k\}_{k=1}^N$.
+Let us consider two identical and independent detectors observing the same variable source, producing independent and strictly simultaneous time series, with identical even sampling $\delta t$, $\mathbf{x} = \{x_k\}_{k=1}^N$ and $\mathbf{y} = \{y_k\}_{k=1}^N$.
 For a stochastic process (e.g.\ $1/\nu$-type red noise), the Fourier amplitudes will vary as a function of $N_{\mathrm{phot}}P(\nu)/4$, where $P(\nu)$ (Leahy-normalized, \citealt{Leahy+83}) is the shape of the power spectrum underlying the stochastic process, and $N_{\mathrm{phot}}$ denotes the number of photons in a light curve.
+
 If the two detectors observe the same source simultaneously, the amplitudes and phases of the stochastic process will be shared among $\mathbf{x}$ and $\mathbf{y}$, while each light curve will be affected \textit{independently} by the photon counting noise in the detector, as well as the dead time process.
 Dead time can be considered a convolution on the signal \citep{Vikhlinin+94}. 
-As such, for the convolution theorem we will have that the Fourier transform $\mathcal{F}$ of dead time-affected light curves will result in a \textit{product} of the Fourier transform of the signal $\mathcal{S}$ times the Fourier transform of the dead time filter $\mathcal{D}$:
+Following the convolution theorem the Fourier transform $\mathcal{F}$ of dead time-affected light curves will be the \textit{product} of the Fourier transform of the signal $\mathcal{S}$ and the Fourier transform of the dead time filter $\mathcal{D}$:
 \begin{equation}
@@
 \end{equation}
-For a large enough number of data points $N$, the complex Fourier amplitudes $S_j$ will be composed of a sum of two independent random normal variables: $S_j = S_{sj} + S_{nj}$, with $\Re (S_{sj}) \sim \Normal(0, \sigma_{sj}^2)$ and $\Re(S_{nj}) \sim \Normal(0, \sigma_n^2)$, and similarly for the imaginary parts.
-$\sigma_{sj}^2 = \sigma_{s}^2(\nu) = N_\mathrm{phot}P(\nu)/4$ (where $N_{\mathrm{phot}} = \sum_{k=1}^{N}{x_k}$) is given by the power spectrum of the underlying stochastic process and is frequency-dependent.
-However, $\sigma_n^2 = N_\mathrm{phot}/2$ is not.
-Note that $S_{xsj} = S_{ysj}$, because the amplitudes of the stationary noise process will be the same for the Fourier transforms of $\mathbf{x}$ and $\mathbf{y}$, while the components due to white noise differ between the two time series.
-Moreover, the dead time filter will only depend on the count rate, which is again the same in the two light curves.
+For a large enough number of data points $N$, the complex Fourier amplitudes $S_j$ will be composed of a sum of two independent random normal variables for the intrinsic red noise variability and the detector photon counting noise, respectively: $S_j = S_{sj} + S_{nj}$, with $\Re (S_{sj}) \sim \Normal(0, \sigma_{sj}^2)$ and $\Re(S_{nj}) \sim \Normal(0, \sigma_n^2)$, and similarly for the imaginary parts.
+The red noise variance $\sigma_{sj}^2 = \sigma_{s}^2(\nu) = N_\mathrm{phot}P(\nu)/4$ (where $N_{\mathrm{phot}} = \sum_{k=1}^{N}{x_k}$) is given by the power spectrum of the underlying stochastic process and is frequency-dependent.
+However, the photon counting noise $\sigma_n^2 = N_\mathrm{phot}/2$ is independent of frequency.
+Note that $S_{xsj} = S_{ysj}$, because the amplitudes of the stationary noise process will be the same for the Fourier transforms of $\mathbf{x}$ and $\mathbf{y}$ for the case considered here, while the components due to white noise differ between the two time series.
+The dead time filter affects the sum of signal and white noise amplitudes as a multiplicative factor and only depends on count rate, which is equal for both light curves given identical detectors.
 Thus, the difference between the Fourier amplitudes for the two time series $\mathbf{x}$ and $\mathbf{y}$ will be:
@@
 \end{equation}
-So, in practice, the real and imaginary parts of the Fourier amplitude \textit{difference} between two simultaneous lightcurves of the same signal from identical detectors will be a random variate of the form $\Normal(0, 2\sigma_{n}^2)$ for both the imaginary and real parts, \textit{multiplied} by the Fourier transform of the dead time filter.
-But the squared norm of the latter \textit{is also what is distorting the periodograms}!
-However, in the case of periodograms the source power spectrum is mingled with the shape of $|\mathcal{D}|^2$, while in this case we have a \textit{constant-scatter} random variable which is modulated by the same shape.
-Therefore, we can try to extract the shape of $|\mathcal{D}|^2$ from the Fourier amplitude differences from the two channels, and use it to correct the shape of the periodogram, and in Section~\ref{sec:caveat} we describe the limits of the method.
+Because $S_{xsj} = S_{ysj}$, but $S_{xnj} \neq S_{ynj}$ (since the white noise component is formed in each detector separately), the \textit{difference} of the real and imaginary Fourier amplitudes between the two light curves effectively encodes the white noise component only, multiplied by the Fourier transform of the dead time filter.
+This fact effectively allows us to separate out the (source-intrinsic) red noise from the spurious variability introduced by dead time: if we can extract the shape of the dead time filter $|\mathcal{D}|^2$ from the Fourier amplitude differences of the two channels, we can use it to correct the shape of the periodogram.
+In the following section, we lay this procedure out in more detail, and describe its limits in Section~\ref{sec:caveat}.
 
@@
 
-We used the same procedure and algorithms described by \citet{Bachetti+15}, Section 4, that we briefly recall here together with references to the methods and classes of the libraries above where these steps are implemented.
+We used the same procedure and algorithms described by \citet{Bachetti+15}, Section 4, which we briefly summarize here.
 %The classes in the \texttt{stingray.simulate} module were used to simulate light curves with a given noise profile. 
-We used the \citet{timmer1995} method to create a noise-affected light curve starting from a given power spectral shape. 
+We used the \citet{timmer1995} method to create a red noise light curve starting from a given power spectral shape. 
 This method is implemented in the \texttt{stingray.simulate} module.
 %We first created the noisy light curves and then used an acceptance-rejection method to obtain simulated events. 
-This step needs to be done carefully: if the initial light curves contain significant random noise, the process for the creation of events creates a random variate on the top of the local count rate - which is varying randomly already - producing a non-Poissonian final light curve.
-So, we initially simulated light curves with a very high ``count rate'' - so that the Poisson noise was relatively small - then renormalized the light curves to the wanted (lower) count rate and \rms and finally used these light curves to simulate event lists using the rejection sampling, implemented in the \texttt{stingray.Eventlist.simulate\_times()} method.
+This step needs to be done carefully: if the initial light curves contain significant random noise, the process for the creation of events creates a random variate on the top of the local count rate--which is varying randomly already--producing a non-Poissonian final light curve.
+We initially simulated light curves with a very high mean ``count rate'' such that the Poisson noise was relatively small.
+We then renormalized the light curves to the wanted (lower) count rate and \rms and finally used these light curves to simulate event lists using rejection sampling, implemented in the \texttt{stingray.Eventlist.simulate\_times()} method.
 Then, the \texttt{hendrics.fake.filter\_for\_deadtime()} function was used to apply a non-paralyzable dead time of 2.5\,ms to the simulated event lists.
@@
 \plotone{pds_pdf.pdf}
-\caption{PDF of non-averaged powers in the cospectrum (red) and the periodogram (black), before the FAD correction and after, shown as a histogram. 
-After correction, the powers follow remarkably well the expected Laplace and $\chi^2_2$ distributions respectively, as highlighted by the overplotted probability density functions (PDF).}
+\caption{Probability density function of non-averaged powers in the cospectrum (pink) and the periodogram (grey), before the FAD correction and after (red and black, respectively), shown as a fine-grained histogram.
+After correction, the powers follow remarkably well the expected Laplace (cospectrum) and $\chi^2_2$ (periodogram) distributions, as highlighted by the overplotted probability density functions (PDF).}
 \label{fig:dist}
@@
 \begin{enumerate}
-\item split the two light curves in segments as one would do to calculate standard averaged periodograms;
+\item split the light curves from two independent, identical detectors into segments as one would do to calculate standard averaged periodograms;
 \item for each pair of light curve segments: 
 	\begin{itemize}
-	\item calculate the Fourier transform of each channel separately, and then of the summed channels (hereafter total-intensity);
+	\item calculate the Fourier transform of each channel separately, and then of the summed channels (hereafter total-intensity); \DHN{You seem to use ``channel'' and ``detector'' interchangeably.
+Could people get confused when they think channel means energy channel?
+Just something to be careful with!}
 	\item save the unnormalized Fourier amplitudes;
@@
 	\item use the separated single-channel and total-intensity \textit{unnormalized} Fourier amplitudes to calculate the periodograms;
-	\item use the unnormalized Fourier amplitudes from channels A and B to calculate the cospectrum;
+	\item use the unnormalized Fourier amplitudes from channels A and B to calculate the cospectrum; \DHN{These are kind of two different outcomes, right?
+I mean, you don't *need* to also calculate the normalized cospectrum, do you?
+Maybe leave this out and mention that you could do the same process with the cospectrum?}
 	\item divide all periodograms and the cospectrum by the smoothed and squared FAD, and multiply by 2.
 	\end{itemize}
-\item normalize the periodograms to the wanted normalization (Leahy or fractional \rms).
+\item normalize the periodograms to the wanted normalization (Leahy or fractional \rms \DHN{Probably want to put citations for fractional rms normalization here rather than further below?}).
 \end{enumerate}
@@
     For comparison, we also plot the cospectrum without FAD (pink), showing very different amplitudes for the four Lorentzians, due to dead time.
+\DHN{This plot has too much in it.
+I have a hard time separating out which line is which even knowing what this should show.
+I would just plot the dead-time free PDStot and FAD-normalized total PDS (for which, by the way, you can't really read the label in the legend.
+Also, your model components don't seem to be included in the legend?
+Also, maybe cut this off at 1000 Hz, since there's only more white noise above?}
     }
@@
 We are now ready to verify the last step: is the FAD-corrected periodogram equivalent (albeit with some loss of sensitivity due to the lower number of photons) to the dead time-free periodogram?
-To test this, we produced a number of different synthetic datasets as explained in Section~\ref{sec:wndeadtime}, containing different combinations of QPOs and broadband noise components. 
+To test this, we produced a number of different synthetic datasets as explained in Section~\ref{sec:wndeadtime}, containing different combinations of QPOs and broadband noise components.\footnote{A number of jupyter notebooks is available in the GitHub repo: \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the full analysis plotted in the Figures of this paper and more.
+The full algorithm described in Section~\ref{sec:fad} is contained in the \texttt{fad\_correction.py} file in the notebooks directory, for reference.}
 We first calculated the periodogram and cospectrum of the dead time-free data, averaged over 128-s intervals.
@@
 An example of this analysis is shown in Figure~\ref{fig:pds}.
+\DHN{I feel like Figure 3 requires a bit more text here.
+At least a couple of sentences along the lines of ``as we show in Figure 3, the FAD successfully corrects periodograms and cospectra when compared to dead-time free simulated spectra.''}
 
@@
 
+In order to test the robustness of the FAD, we have ran extensive simulations testing how the method performs (1) for a range of different input count rates, leading to dead-time effects of different magnitude in the output periodograms and cospectra, and (2) whenthe light curves do not have the same count rate (since detectors may in reality have slightly different efficiencies).
 The simulations show that the shape of the periodogram is precisely corrected by the FAD procedure if (1) \textit{the input light curves have the same count rate} and (2) \textit{for values of the input count rate and \rms that are not too extreme}.
-The first caveat turns out, in practice, to be only a big issue for the single-channel periodogram, but \textit{not} for cospectra and total-intensity periodograms. 
-At high count rates, single-channel periodograms are corrected very well only if the two channels have very similar count rates, with the requirement being unsurprisingly stricter and stricter as the count rate increases.
-However, we find that the total-intensity periodogram and the cospectrum remains well corrected by the FAD even if the count rate in the two channels differs by 30\% in most cases.
-Therefore, we recommend to use the FAD very carefully with single-channel periodograms, which should not be an issue given that the total-intensity periodogram is more sensitive and more convenient to use anyway.
-A comparison with the cospectrum, that is not affected by white noise level distortions, is always recommended.
+Differing input count rates in different detectors matter in practice only for the single-channel periodogram, but \textit{not} for cospectra and total-intensity periodograms.
+At high count rates, single-channel periodograms are corrected very well only if the two channels have very similar count rates, and count rates must be more similar athigher count rates in order for the correction to apply.
+However, we find that the total-intensity periodogram and the cospectrum remain well corrected by the FAD even if the count rate in the two channels differs by 30\% in most cases.
+Therefore, we recommend to use the FAD very carefully with single-channel periodograms, which should not be an issue given that the total-intensity periodogram is more sensitive and more convenient to use.
+A comparison with the cospectrum, which is not affected by white noise level distortions, is always recommended.
 
-The second caveat needs some attention. 
-We find that the FAD correction consistently overestimates the integrated \rms when the count rate and \rms are \textit{both} very high, \textit{in particular at low frequency} (See Figure~\ref{fig:errors}).
-At $\sim$200 ct/s and 30\% \rms, the relative error is below 5\% (meaning that if the \rms is 30\%, the measured \rms is between 30 and 32\%!) and it is symmetrically distributed around 0, as expected from statistical errors.
-At higher incident rates and \rms, the error distribution skews towards positive relative errors, implying an overestimation of the \rms.
-This should not be a problem in most cases, where the \rms is used as a rough indicator for spectral state.
-If very precise measurements of \rms are needed (for example, to calculate \rms/energy spectra), it is safer to account for this through simulations.
-As a rough rule-of-thumb, the relative error on the fractional \rms increases \textit{linearly} with the count rate and \textit{quadratically} with \rms.
-A practical way to estimate this effect during analysis is to apply the FAD, obtain a best fit model, calculate the \rms, then use the codes we shared with the Jupyter notebooks to simulate a number of realizations of the light curve, evaluating what is the amount of overestimation involved.
+However, we find that the FAD correction consistently overestimates the integrated \rms when the count rate and \rms are \textit{both} very high, \textit{in particular at low frequency} (See Figure~\ref{fig:errors}).
+At $\sim$200 ct/s and 30\% \rms, the relative error is below 5\% (meaning that if the true \rms is 30\%, the measured \rms is between 30 and 32\% \DHN{So shouldn't this be something like 28 to 32 \% if it's symmetrical about zero or am I missing something here?}) and it is symmetrically distributed around 0, as expected from statistical uncertainties.
+At higher incident rates and \rms, the uncertainty distribution is biased towards positive relative errors, implying an overestimation of the \rms.
+\DHN{This is currently impossible to discern from the plot.
+Can we improve that plot somehow?
+I think partly there's so many circles overplotted that it all becomes hard to distinguish.}
+This should not be a problem in most use cases, when the \rms is used as a rough indicator for spectral state.
+If very precise measurements of \rms are needed (for example, to calculate \rms/energy spectra), it is safer to account for this bias through simulations.
+As a rough rule-of-thumb, the bias in the measured fractional \rms increases \textit{linearly} with the count rate and \textit{quadratically} with \rms.
+A practical way to estimate this effect during analysis is to apply the FAD, obtain a best fit model, calculate the \rms, and simulate a number of realizations of the light curve to evaluate the amount of overestimation involved\footnote{relevant code can be found in Jupyter notebooks in the following GitHub repository: \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II}}.
 
@@
 
-A number of jupyter notebooks is available the address \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the full analysis plotted in the Figures of this paper and more.
-The full algorithm described in Section~\ref{sec:fad} is contained in the \texttt{fad\_correction.py} file in the notebooks directory, for reference.
+We performed a number of simulations to test the validity of our method and explore its performance in the limits of high count rates as well as detectors with mis-matched efficiencies. 
 In all cases, we find that the adjustment of the white noise standard deviation in the periodogram and the cospectrum works remarkably well, allowing to make a confident analysis of X-ray variability even in sources where this was precluded until now.
 Only in cases where the count rate and the \rms are \textit{both} very high ($>$500 ct/s incident, $>$40\% resp.), the FAD correction leads to an overestimation the \rms, even if the white noise level of the periodogram remains flat.
-In these case, we provide some example simulation code to estimate this effect in the notebooks.
-This software will be merged into the main repository of \texttt{stingray} before publication.
+%In these case, we provide some example simulation code to estimate this effect in the notebooks.
+%This software will be merged into the main repository of \texttt{stingray} before publication.
 
 \acknowledgments
-We thank the anonymous referee for coping with the first version of this paper without trashing it.
+We thank the anonymous referee for providing very helpful feedback.
 We thank David W. Hogg for useful discussions on the topic of Fourier analysis, and Jeff Scargle for useful suggestions and comments.

### 2017-12-15 paper/referee_response.md

--- 2017-12-12 referee_response.md
@@
 
-We thank the referee for the frank report, that allowed to improve the paper significantly.
-We do acknowledge that the paper was not as clear as it should have been.
-However, we also do think that a poor description should not be confused with a poor result.
-The extensive modifications we have done to the manuscript will hopefully demonstrate this.
+We thank the referee for the frank report and their constructive suggestions, which allowed us to improve the paper significantly.
+We acknowledge that the paper was not as clear as it should have been.
+However.
+We have extensively modified the manuscript will hopefully demonstrate this.
 We would like to start this response with the description of a possible critical point: in order to accommodate a thorough discussion of the caveats of the method, we decided to take out the real data example from the paper (Cyg X-1).
-We realize that this choice might raise some concerns from the referee, as traditionally a paper is considered incomplete without real data.
-However, we find that the addition of real data does not really add anything to the main focus of the paper, which is the description of a data analysis method that works on any instrument with multiple identical detectors (it will still work practically unmodified with IXPE, that will probably have a dead time only slightly shorter than NuSTAR, and of course Astrosat etc.), and will be very useful to the community.
-Besides the reassuring fact of seeing a real periodogram from a real BH candidate, a single example of real data spectrum would not do a better job at showing the method, because it would still be a single example, subject to the usual doubts (is it a cherry-picked example?).
-The simulation environment we use in the paper mimicks NuSTAR sufficiently well, uses thousands of realizations of simulated NuSTAR power spectra - not just one - and the new additions in the discussion about the difference of flux between the two channels also includes effects of count rate differences that are higher than expected from any reasonable situation found in NuSTAR data (where bright sources are usually dominating the observation and are far from the detector edges).
-In any case, we are setting up a web page showing off the FAD correction working on real data that we will link in the text.
+We realize that this choice might raise some concerns from the referee, as traditionally a paper might be considered incomplete without real data.
+However, for an algorithm paper like this one, we find that the addition of real data detracts from the main focus of the paper, which is the description of a data analysis method that works on any instrument with multiple identical detectors.
+The presented method will still work practically unmodified with IXPE, which will probably have a dead time only slightly shorter than NuSTAR, and of course current instruments like Astrosat.
+The NuSTAR detectors and dead time within NuSTAR are well enough understood to simulate very precisely, thus aside from the reassurance of seeing a real periodogram from a real BH candidate, a single example of real data periodogram would not do a better job at showing the method compared to the thousands of realizations of simlated NuSTAR power spectra we simulated and allowed us to test the efficacy of the methods in different parameter regimes.
+
+We have also added a new discussion about several caveats of the method.
+Most prominantly, we discuss the effect a difference in flux between the two detectors would have, and also include the effects that a difference in count rates between the two detectors would have on the results, up to a difference higher than any reasonable sitaution found in NuSTAR data.
+
+We are setting up a web page showing off the FAD correction working on real data that we will link in the text.
+
+Overall, we have edited the paper for clarity, expanded where necessary and completely redone the figures to improve the ease with which they can be understood.
 
@@
 
-We do agree that it is good practice to refer to a specific version of the codes, so we added the version numbers used.
+We agree that it is good practice to refer to a specific version of the codes, so we added the version numbers used.
 
@@
 
-We have added some description of the algorithms, in some cases by referencing Bachetti+15 where some of them were already described in detail (the simulation process is basically the same: model periodogram -> Timmer & Koening method -> light curve -> acceptance-rejection method -> clean event lists -> dead time filter -> final event lists).
+We have added some description of the algorithms, and included appropriate references where some of them were already described in detail (the simulation process is basically the same to Bachetti+2015: model periodogram -> Timmer & Koening method -> light curve -> acceptance-rejection method -> clean event lists -> dead time filter -> final event lists).
 We hope the new version will be easier to follow.
@@
 > Section 3, x and y are defined, without explicitly saying that you are specifically considering binned lightcurves of identical length representing the exact same times.
-We added this information
+
+We have slightly expanded this explanation to make sure we state our assumptions about the nature of the light curves.
 
@@
 
-The section was basically rewritten, but we did pay attention to specifying the normalization of P the first time it is mentioned.
+We have rewritten this section in part for clarity, and have made sure to specify the normalization of the periodogram where it is first mentioned.
 
@@
 
-Rewritten.
+We thank the reviewer for pointing out this typo, which has been fixed.
 
@@
 
-Corrected, and figures are changed anyway.
+We have fixed this, and have significantly changed the figures to improve clarity.
 
@@
 
-No, we made a confusing mistake in the plot and the notebook and this needs to be clarified.
+In this case, we made a confusing mistake in both the plot and the notebook, and we thank the referee for bringing this to our attention, because it needs clarification.
 The only point missing in the text is that the _mean absolute values_ of the FAD and amplitudes in each frequency bin are used, and this is the reason for the apparent lack of negative values.
-The description with the standard deviation is somehow equivalent, with actually the same factor between the quantities (we tried both approaches in the Jupyter notebook, and we chose the plots inconsistently), but it's not what we use in the actual algorithm (see the implementation in the file fad_correction.py in the notebooks/ directory in the repository).
+The description with the standard deviation is somehow equivalent, with actually the same factor between the quantities.
+We tried both approaches in the Jupyter notebook, and we chose the plots inconsistently in the paper, but it is not what is being used in the actual algorithm (see the implementation in the file fad_correction.py in the notebooks/ directory in the repository).
+We have edited the text and figure to make them consistent.
 
@@
 
-Real part. We tried to be clearer in the new version.
+Real part. We have clarified this in the new version.
 
@@
 
-We changed all references to "spectral" in order to clarify that we are talking about variability.
+We changed all references to "spectral" in order to clarify that we are talking about variability only.
 
@@
 
-This point is not very clear to us, but anyway the multiplication factor should work with _any_ normalization of the PDS.
-The way we calculate the FAD, it is done so that the white noise power spectral values in Leahy normalization flatten to ~two, but the same multiplicative factor would correct other normalizations as well (because the unit is always P x multiplicative factors, in Leahy or the various rms normalizations, and this is just a new multiplicative factor)
+We are not sure that we understand the point the referee makes here, but we would like to point out that the multiplication factor should work with _any_ normalization of the PDS.
+The way we calculate the FAD, it is done so that the white noise power spectral values in Leahy normalization flatten to ~two, but the same multiplicative factor would correct other normalizations as well: the unit is always P x multiplicative factors, in Leahy or the various rms normalizations, andthe correction is just a new multiplicative factor to be included in calculating the normalization.
 
@@
 
-We respectfully disagree with this.
-The text in the figures counts exactly as much as the one in the main text for the ApJL rules, so there is would be no advantage whatsoever from the point of view of obtaining a letter length.
-We just like the figures to work on their own, without the need to look in the main text for essential information needed to understand them.
-The figures were quite (probably too) complicated and needed some text to describe them properly.
-In any case, now most of them have changed.
+While we understand how that perception could arise, given that our paper was otherwise not very clear, but we would like to assure the referee that this was not our intention.
+Our aim was for our figures to work on their own, without the need to look in the main text for essential information to understand them.
+We agree that the complexity of the figures meant they required too much text to describe them; our new, simpler figures should be easier to read and have shorter captions attached to them.
 
@@
 Basically, the only power spectral measurement that is heavily affected by the count rate difference in the two detectors is the single-channel periodogram.
-Neither the periodogram obtained by the total-intensity light curve (the sum of the two channels) or the cospectrum are very sensitive to the difference of flux in the two channel.
+Neither the periodogram obtained by the total-intensity light curve (the sum of the two channels) or the cospectrum are very sensitive to the difference of flux in the two channels.
 In our simulations the parameter indicating the ratio of flux in the two channels was free to change from 0.5 to 2 (with 1 being the same flux in the two channels), and we find basically indistinguishable distributions if the fluxes in the channels are within ~30% of one another (It can be seen in the simulations in the notebooks).
 The simulations in figure 5 include channel ratios between 0.8 to 1.3.
-
-> I very well likely might have further comments and questions about the results.
-As I tried to write my own code to check the figures and results, I had some differences from the figures.
-This could potentially be my fault.
-However, after running across poorly worded description after poorly worded description, wondering how Fourier amplitudes vs.
-Fourier amplitude differences could be so narrowly distributed and not have negative values (i.e., Fig.
-2a) until I discovered that the plots were instead standard deviation vs.
-standard deviation, I simply gave up.
-
-The code to test the algorithm conveniently is (and was) contained in the fad_correction.py file in the notebooks/ directory.
-There, it was clear that we weren't using the standard deviation, but admittedly, we didn't write a reference to this file in the text.
 
@@
 
-We hope that the new version will make the referee better appreciate the algorithm.
+We thank the referee for their attempt to reproduce our results. We hope that the new version of this papers simplifies this exercise significantly, and we would welcome any further suggestions.

### 2017-12-15 paper/deadtime.tex

@@
 \section{On the difference of Fourier amplitudes} \label{sec:fourierdiff}
-%\begin{figure*}
-%\gridline{\fig{rn_fourierdiff.eps}{0.33\textwidth}{(a)}
-%	\fig{wn_fourierdiff.eps}{0.33\textwidth}{(b)}
-%	\fig{fourier_vs_diff_dt.eps}{0.33\textwidth}{(c)}}      
-%\caption{(a): Real-valued Fourier amplitudes derived from many evenly sampled light curves of $500\,\mathrm{s}$ duration with strong $1/f$ red noise (top, in black).
-On the bottom, we show the \textit{difference} between real-valued Fourier amplitudes as they would be sampled from two independent detectors using the same light curves as in the top panel.
-In red, we show the the frequency-dependent spread of the distributions, measured by the mean of the absolute values of the curves in each frequency bin.
-Panel (b) shows the same as panel (a), but using white noise light curves of $5\,\mathrm{s}$ duration affected by dead time.
-In the case of red noise without dead time, the difference in Fourier amplitudes effectively follows a white noise distribution.
-Because dead time affects the observed light curves \textit{in the detector} (while red noise is intrinsic to the source), the difference in Fourier amplitudes will still contain the dead time contribution to the Fourier amplitudes, and can thus be used to effectively separate real variability from spurious dead time effects.
-%(c) Scatter distribution of the (averaged over multiple intervals) absolute values of dead time-affected Fourier amplitudes versus the difference of Fourier amplitudes for case (b): their relation is clearly linear, with a factor $1/\sqrt{2}$.
-\DHN{I don't really understand what (c) adds.
-Also, why 500s segments in (a) and 5s segments in (b)?}}
-%\label{fig:fourierdiff}
-%\end{figure*}
+
+\begin{figure*}
+\plottwo{rn_fourierdiff}{wn_fourierdiff}
+\caption{Real-valued Fourier amplitudes obtained by single light curves ($\mathcal{F}_1$) and difference between two realizations of the same source light curve ($\mathcal{F}_1 - \mathcal{F}_2$), plotted against each other in two cases: (Left) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (Right) no red noise and strong dead time, calculated over 5\,s segments of the light curve.
+The red curve gives the frequency-dependent spread of the distributions, measured by the mean of the absolute values of the curves in each frequency bin. 
+The different behavior of Fourier amplitude differences in the two cases is evident: in the deadtime-free case, the Fourier amplitude difference does \textit{not} correlate with the Fourier amplitude, while in the deadtime-affected case, this follows a precise linear relationship.
+}
+\label{fig:fourierdiff}
+\end{figure*}
 
@@
 If the two detectors observe the same source simultaneously, the amplitudes and phases of the stochastic process will be shared among $\mathbf{x}$ and $\mathbf{y}$, while each light curve will be affected \textit{independently} by the photon counting noise in the detector, as well as the dead time process.
+
 Dead time can be considered a convolution on the signal \citep{Vikhlinin+94}. 
@@
     \caption{Relative overestimation of FAD with respect to \rms, versus \rms, as calculated from the cospectrum.  
-    We encoded the frequency of the feature in the color, and the incident rate in the size of the scatter points.
+    We encoded in the color the  the incident rate (Top) and the frequency of the feature.
     From this visualization we see two regimes: below $\sim$40\% fractional \rms, the errors are dominated by statistical errors. 

### 2017-12-15 paper/referee_response.md
Merge conflicts solved, comments in green addressed (not in Fig. 4 yet)

@@
 However.
-We have extensively modified the manuscript will hopefully demonstrate this.
+We have extensively modified the manuscript to hopefully demonstrate this.
 We would like to start this response with the description of a possible critical point: in order to accommodate a thorough discussion of the caveats of the method, we decided to take out the real data example from the paper (Cyg X-1).
@@
 The presented method will still work practically unmodified with IXPE, which will probably have a dead time only slightly shorter than NuSTAR, and of course current instruments like Astrosat.
-The NuSTAR detectors and dead time within NuSTAR are well enough understood to simulate very precisely, thus aside from the reassurance of seeing a real periodogram from a real BH candidate, a single example of real data periodogram would not do a better job at showing the method compared to the thousands of realizations of simlated NuSTAR power spectra we simulated and allowed us to test the efficacy of the methods in different parameter regimes.
+The NuSTAR detectors and dead time within NuSTAR are well enough understood to simulate very precisely, thus aside from the reassurance of seeing a real periodogram from a real BH candidate, a single example of real data periodogram would not do a better job at showing the method compared to the thousands of realizations of simulated NuSTAR power spectra we produced, that allowed us to test the efficacy of the methods in different parameter regimes.
 
@@
 
-We are setting up a web page showing off the FAD correction working on real data that we will link in the text.
+We are setting up a "Gallery" on Github showing off the FAD correction working on real data that we will link in the text, with a unique identifier on Zenodo or similar services.
 
@@
 
-We thank the reviewer for pointing out this typo, which has been fixed.
+We thank the reviewer for pointing out this typo.
 
@@
 We are not sure that we understand the point the referee makes here, but we would like to point out that the multiplication factor should work with _any_ normalization of the PDS.
-The way we calculate the FAD, it is done so that the white noise power spectral values in Leahy normalization flatten to ~two, but the same multiplicative factor would correct other normalizations as well: the unit is always P x multiplicative factors, in Leahy or the various rms normalizations, andthe correction is just a new multiplicative factor to be included in calculating the normalization.
+The way we calculate the FAD, it is done so that the white noise power spectral values in Leahy normalization flatten to ~two, but the same multiplicative factor would correct other normalizations as well: the unit is always P x multiplicative factors, in Leahy or the various rms normalizations, and the correction is just a new multiplicative factor to be included in calculating the normalization.
 
@@
 We agree that the complexity of the figures meant they required too much text to describe them; our new, simpler figures should be easier to read and have shorter captions attached to them.
+We would like to point out that the text in the figures counts in the number of words allowed for letters, so there would be no advantage from this point of view.
 

### 2017-12-15 paper/deadtime.tex
Merge conflicts solved, comments in green addressed (not in Fig. 4 yet)

@@
 Because $S_{xsj} = S_{ysj}$, but $S_{xnj} \neq S_{ynj}$ (since the white noise component is formed in each detector separately), the \textit{difference} of the real and imaginary Fourier amplitudes between the two light curves effectively encodes the white noise component only, multiplied by the Fourier transform of the dead time filter.
-This fact effectively allows us to separate out the (source-intrinsic) red noise from the spurious variability introduced by dead time: if we can extract the shape of the dead time filter $|\mathcal{D}|^2$ from the Fourier amplitude differences of the two channels, we can use it to correct the shape of the periodogram.
+This fact effectively allows us to separate out the (source-intrinsic) red noise from the spurious variability introduced by dead time: if we can extract the shape of the dead time filter $|\mathcal{D}|^2$ from the Fourier amplitude differences of the two detectors, we can use it to correct the shape of the periodogram.
 In the following section, we lay this procedure out in more detail, and describe its limits in Section~\ref{sec:caveat}.
@@
 %\footnote{To use the method on different sources, it is sufficient to download a different ObsID and change the region file containing the position of the source}.
-%We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI channels into energy values, and produced light curves with photons from 3 to 79 keV and binned with uniform time bins of 1/4096$\sim2.44\cdot10^{-4}$\,sec%
+%We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI detectors into energy values, and produced light curves with photons from 3 to 79 keV and binned with uniform time bins of 1/4096$\sim2.44\cdot10^{-4}$\,sec%
 %\footnote{This procedure uses the scripts \texttt{HENreadfile}, \texttt{HENcalibrate} and \texttt{HENlcurve}, as described at\\ \href{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}}.
@@
 
-As shown in Figure~\ref{fig:fourierdiff} (right panel), the single-channel Fourier amplitudes are proportional on average to the difference of the Fourier amplitudes in different realizations, with a constant factor $1/\sqrt{2}$.
+As shown in Figure~\ref{fig:fourierdiff} (right panel), the single-detector Fourier amplitudes are proportional on average to the difference of the Fourier amplitudes in different realizations, with a constant factor $1/\sqrt{2}$.
 Therefore, we expect that the periodogram will be proportional to the square of the Fourier amplitude difference, divided by 2.
@@
 	\begin{itemize}
-	\item calculate the Fourier transform of each channel separately, and then of the summed channels (hereafter total-intensity); \DHN{You seem to use ``channel'' and ``detector'' interchangeably.
-Could people get confused when they think channel means energy channel?
-Just something to be careful with!}
+	\item calculate the Fourier transform of each detector separately, and then of the summed detectors (hereafter total-intensity); 
 	\item save the unnormalized Fourier amplitudes;
 	\item multiply these Fourier amplitudes by $\sqrt{2/N_{ph}}$ (that would give Leahy-normalized periodograms if squared);
-	\item subtract the Leahy-normalized Fourier amplitudes of the two channels between them, \textit{take the absolute value}, and obtain this way the Fourier Amplitude Differences (FAD);
+	\item subtract the Leahy-normalized Fourier amplitudes of the two detectors between them, \textit{take the absolute value}, and obtain this way the Fourier Amplitude Differences (FAD);
 	\item \textit{smooth} the FAD using a Gaussian-window interpolation with a large number of bins, in our case all the bins contained in 1-2 Hz;
-	\item use the separated single-channel and total-intensity \textit{unnormalized} Fourier amplitudes to calculate the periodograms;
-	\item use the unnormalized Fourier amplitudes from channels A and B to calculate the cospectrum; \DHN{These are kind of two different outcomes, right?
-I mean, you don't *need* to also calculate the normalized cospectrum, do you?
-Maybe leave this out and mention that you could do the same process with the cospectrum?}
-	\item divide all periodograms and the cospectrum by the smoothed and squared FAD, and multiply by 2.
+	\item use the separated single-detector and total-intensity \textit{unnormalized} Fourier amplitudes to calculate the periodograms (and/or the cospectrum);
+	\item divide all periodograms (and/or the cospectrum) by the smoothed and squared FAD, and multiply by 2.
 	\end{itemize}
-\item normalize the periodograms to the wanted normalization (Leahy or fractional \rms \DHN{Probably want to put citations for fractional rms normalization here rather than further below?}).
+\item normalize the periodograms to the wanted normalization (e.g. \citealt{Leahy+83} or fractional \rms: \citealt{BelloniHasinger90,Miyamoto+91}).
 \end{enumerate}
@@
     \caption{Periodograms and cospectra from a simulation with four Lorentzian features (at 50, 200, 300 and 400 Hz) with 40-Hz full with at half maximum (FWHM). 
-    We plotted and fitted periodograms and cospectra before and after applying the dead time filter
+    We plotted and fitted periodograms and cospectra before and after applying a 2.5\,ms dead time filter
     The total \rms before dead time was 40\% and the incident photon flux 400 ct/s. 
-    After applying a dead time of 2.5 ms like in \nustar, the ``detected'' photon flux decreased to $\sim$200 ct/s as expected. 
-    As can be seen from the best-fit curves, there is no significant difference between FAD-normalized and deadtime-free periodograms and cospectra.
+    As can be seen from the best-fit curves, there is no significant difference between FAD-normalized and deadtime-free periodograms and cospectra (the curves overlap exactly).
     For comparison, we also plot the cospectrum without FAD (pink), showing very different amplitudes for the four Lorentzians, due to dead time.
-\DHN{This plot has too much in it.
-I have a hard time separating out which line is which even knowing what this should show.
-I would just plot the dead-time free PDStot and FAD-normalized total PDS (for which, by the way, you can't really read the label in the legend.
-Also, your model components don't seem to be included in the legend?
-Also, maybe cut this off at 1000 Hz, since there's only more white noise above?}
     }
@@
 
-All spectra were then expressed in fractional \rms \citep{BelloniHasinger90,Miyamoto+91} normalization, where the integral of the fitted power spectral components over the frequency returns directly its fractional \rms.
+All spectra were then expressed in fractional \rms normalization, where the integral of the fitted power spectral components over the frequency returns directly its fractional \rms.
 In the \rms normalization, the values of each point of the periodogram, after white noise subtraction, should be consistent between the dead time-free and the FAD-corrected periodograms.
@@
 For periodograms, the model included also a constant offset to account for the white noise level.
-An example of this analysis is shown in Figure~\ref{fig:pds}.
-\DHN{I feel like Figure 3 requires a bit more text here.
-At least a couple of sentences along the lines of ``as we show in Figure 3, the FAD successfully corrects periodograms and cospectra when compared to dead-time free simulated spectra.''}
+An example of this analysis is shown in Figure~\ref{fig:pds}: the FAD successfully corrects so well periodograms and cospectra when compared to dead-time free simulated spectra, that in the figure they are almost indistinguishable.
 
@@
     Over $\sim$40\% fractional \rms, the errors are significantly skewed towards an overestimation of the \rms, and this is 
-    clearly truer when the incident rate \textit{and} the \rms are high, and the frequency relatively low.}
+    clearly truer when the incident rate \textit{and} the \rms are high, and the frequency relatively low (as can be seen by the fact that the distribution of black points in both plots is more skewed towards positive values).
+}
     \label{fig:errors}
@@
 The simulations show that the shape of the periodogram is precisely corrected by the FAD procedure if (1) \textit{the input light curves have the same count rate} and (2) \textit{for values of the input count rate and \rms that are not too extreme}.
-Differing input count rates in different detectors matter in practice only for the single-channel periodogram, but \textit{not} for cospectra and total-intensity periodograms.
-At high count rates, single-channel periodograms are corrected very well only if the two channels have very similar count rates, and count rates must be more similar athigher count rates in order for the correction to apply.
-However, we find that the total-intensity periodogram and the cospectrum remain well corrected by the FAD even if the count rate in the two channels differs by 30\% in most cases.
-Therefore, we recommend to use the FAD very carefully with single-channel periodograms, which should not be an issue given that the total-intensity periodogram is more sensitive and more convenient to use.
+Differing input count rates in different detectors matter in practice only for the single-detector periodogram, but \textit{not} for cospectra and total-intensity periodograms.
+At high count rates, single-detector periodograms are corrected very well only if the two detectors have very similar count rates, and count rates must be more similar athigher count rates in order for the correction to apply.
+However, we find that the total-intensity periodogram and the cospectrum remain well corrected by the FAD even if the count rate in the two detectors differs by 30\% in most cases.
+Therefore, we recommend to use the FAD very carefully with single-detector periodograms, which should not be an issue given that the total-intensity periodogram is more sensitive and more convenient to use.
 A comparison with the cospectrum, which is not affected by white noise level distortions, is always recommended.
@@
 However, we find that the FAD correction consistently overestimates the integrated \rms when the count rate and \rms are \textit{both} very high, \textit{in particular at low frequency} (See Figure~\ref{fig:errors}).
-At $\sim$200 ct/s and 30\% \rms, the relative error is below 5\% (meaning that if the true \rms is 30\%, the measured \rms is between 30 and 32\% \DHN{So shouldn't this be something like 28 to 32 \% if it's symmetrical about zero or am I missing something here?}) and it is symmetrically distributed around 0, as expected from statistical uncertainties.
+At $\sim$200 ct/s and 50\% \rms, the relative overestimation is below 5\% (meaning that if the true \rms is 50\%, the measured \rms is between 50 and 53\%) and it is symmetrically distributed around 0, as expected from statistical uncertainties.
 At higher incident rates and \rms, the uncertainty distribution is biased towards positive relative errors, implying an overestimation of the \rms. 
-\DHN{This is currently impossible to discern from the plot.
-Can we improve that plot somehow?
-I think partly there's so many circles overplotted that it all becomes hard to distinguish.}
 This should not be a problem in most use cases, when the \rms is used as a rough indicator for spectral state.

### 2017-12-15 paper/deadtime.tex
Merge conflicts solved, comments in green addressed (not in Fig. 4 yet)

@@
     The total \rms before dead time was 40\% and the incident photon flux 400 ct/s. 
-    As can be seen from the best-fit curves, there is no significant difference between FAD-normalized and deadtime-free periodograms and cospectra (the curves overlap exactly).
+    There is no significant difference between FAD-normalized and deadtime-free periodograms and cospectra, that are almost indistinguishable (note also the agreement between all best-fit Lorentzians).
     For comparison, we also plot the cospectrum without FAD (pink), showing very different amplitudes for the four Lorentzians, due to dead time.
@@
     Over $\sim$40\% fractional \rms, the errors are significantly skewed towards an overestimation of the \rms, and this is 
-    clearly truer when the incident rate \textit{and} the \rms are high, and the frequency relatively low (as can be seen by the fact that the distribution of black points in both plots is more skewed towards positive values).
+    clearly truer when the incident rate \textit{and} the \rms are high, and the frequency relatively low (as can be seen by the fact that the distribution of darker points in both plots is more skewed towards positive values).
 }

### 2017-12-15 paper/deadtime.tex
Fix references
New figures

--- 2017-12-15 paper/deadtime.tex
@@
     \plotone{four_qpos.eps}
-    \caption{Periodograms and cospectra from a simulation with four Lorentzian features (at 50, 200, 300 and 400 Hz) with 40-Hz full with at half maximum (FWHM). 
-    We plotted and fitted periodograms and cospectra before and after applying a 2.5\,ms dead time filter
-    The total \rms before dead time was 40\% and the incident photon flux 400 ct/s. 
-    As can be seen from the best-fit curves, there is no significant difference between FAD-normalized and deadtime-free periodograms and cospectra (the curves overlap exactly).
-    For comparison, we also plot the cospectrum without FAD (pink), showing very different amplitudes for the four Lorentzians, due to dead time.
+    \caption{Periodogram from a simulation with four Lorentzian features (at 50, 200, 300 and 400 Hz) with 40-Hz full with at half maximum (FWHM). 
+    We plotted and fitted the periodograms obtained before and after applying a 2.5\,ms dead time filter
+    The total \rms before dead time was 30\% and the incident photon flux 400 ct/s. 
+    There is no significant difference between the FAD-normalized and the deadtime-free periodogram, while the cospectrum without FAD (pink) clearly distorts the curves at different frequencies.
     }
@@
 We are now ready to verify the last step: is the FAD-corrected periodogram equivalent (albeit with some loss of sensitivity due to the lower number of photons) to the dead time-free periodogram?
-To test this, we produced a number of different synthetic datasets as explained in Section~\ref{sec:wndeadtime}, containing different combinations of QPOs and broadband noise components.\footnote{A number of jupyter notebooks is available in the GitHub repo: \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the full analysis plotted in the Figures of this paper and more.
-The full algorithm described in Section~\ref{sec:fad} is contained in the \texttt{fad\_correction.py} file in the notebooks directory, for reference.}
+To test this, we produced a number of different synthetic datasets as explained in Section~\ref{sec:wndeadtime}, containing different combinations of QPOs and broadband noise components.\footnote{See the notebooks at \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the analysis plotted in the Figures of this paper and more.
+The algorithm described in Section~\ref{sec:fad} is contained in the \texttt{fad\_correction.py} file in the notebooks directory.}
 We first calculated the periodogram and cospectrum of the dead time-free data, averaged over 128-s intervals.
@@
     \caption{Relative overestimation of FAD with respect to \rms, versus \rms, as calculated from the cospectrum.  
-    We encoded in the color the  the incident rate (Top) and the frequency of the feature.
+    We encoded in the color the  the incident rate (left) and the frequency of the feature (right).
     From this visualization we see two regimes: below $\sim$40\% fractional \rms, the errors are dominated by statistical errors. 
     These errors will simply decrease when we average more data, as we expect from statistical errors.
-    Over $\sim$40\% fractional \rms, the errors are significantly skewed towards an overestimation of the \rms, and this is 
-    clearly truer when the incident rate \textit{and} the \rms are high, and the frequency relatively low (as can be seen by the fact that the distribution of black points in both plots is more skewed towards positive values).
-}
+    Over $\sim$40\% fractional \rms, FAD-corrected spectra overestimate the \rms, and this is 
+    in particular when the incident rate is high, and the frequency relatively low. }
     \label{fig:errors}

### 2018-01-15 paper/deadtime.tex
Third revision

@@
 \documentclass[twocolumn]{aastex61}
+\pdfoutput=1
 
@@
 For timing analysis, the effect of dead time is far more problematic.
-The periodogram, commonly referred to as power density spectrum (PDS)%
+Dead time heavily distorts the periodogram, the most widely used statistical tool to estimate the power density spectrum (PDS)%
 \footnote{here we will use the term PDS for the actual source power spectrum, and \textit{periodogram} to indicate our estimate of it, or otherwise said, the realization of the ``real'' power spectrum we observe in the data}%
-, which is the most widely used statistical tool to investigate rapid variability, is heavily distorted by dead time, with a characteristic pattern similar to a damped oscillator.
-This pattern is stronger for brighter sources, and it is often not possible to disentangle this power spectral distortion due to dead time and the broadband noise components characterizing the emission of accreting systems.
+, with a characteristic pattern that is stronger for brighter sources. 
+It is often not possible to disentangle this power spectral distortion due to dead time and the broadband noise components characterizing the emission of accreting systems.
 In the special case where dead time is constant, its shape can be modeled precisely \citep{Zhang+95,Vikhlinin+94}.
@@
 Since dead time is uncorrelated between the two detectors, the resulting powers have a mean white noise level fixed to 0, which resolves the first and most problematic issue created by dead time (see details in \citealt{Bachetti+15}); however, the resulting powers no longer follow the statistical distribution expected for power spectra, and their probability distribution is frequency-dependent.
-Whereas a noise cospectrum in the absence of dead time would follow a Laplace distribution (Huppenkothen and Bachetti, sub.),
+Whereas a noise cospectrum in the absence of dead time would follow a Laplace distribution \citep{HuppenkothenBachetti18},
 dead time affects the width of the probability distribution for cospectral powers and modulates the measured \rms similarly to the distortion acted on power spectra.
-In this Letter, we show a method to precisely recover the shape of the power density spectrum by looking at the difference of the Fourier amplitudes of the light curves of two independent detectors.
+In this Letter, we show a method to precisely recover the shape of the periodogram by looking at the difference of the Fourier amplitudes of the light curves of two independent detectors.
 This difference, in fact, contains information on the uncorrelated noise produced by dead time, but not on the source-related  signal which is correlated between the two detectors.
@@
 
-In \sref{sec:fourierdiff} we show that, in the absence of dead time, the difference of the Fourier amplitudes calculated  two independent detectors contain the sum of the correlated signal (the source signal) and uncorrelated noise (detector-related noise), and that their difference eliminates the source part.
+In \sref{sec:fourierdiff} we show that, in the absence of dead time, the difference of the Fourier amplitudes calculated from two independent detectors contains the sum of the correlated signal (the source signal) and uncorrelated noise (detector-related noise), and that their difference eliminates the source part.
 In \sref{sec:fadsec} we use extensive simulations to show how to use this fact to correct deadtime-affected periodograms, and we describe the limitations of this method.
@@
 \begin{figure*}
-\plottwo{rn_fourierdiff}{wn_fourierdiff}
+\plottwo{rn_fourierdiff.pdf}{wn_fourierdiff.pdf}
 \caption{Real-valued Fourier amplitudes obtained by single light curves ($\mathcal{F}_1$) and difference between two realizations of the same source light curve ($\mathcal{F}_1 - \mathcal{F}_2$), plotted against each other in two cases: (Left) Strong $1/f$ red noise and no dead time, calculated over many 500\,s segments of the light curve, and (Right) no red noise and strong dead time, calculated over 5\,s segments of the light curve.
@@
 
-%
-%
-%The resulting Fourier amplitudes will be of the form
-%
-%\begin{eqnarray}
-%A_{xj} &=& A_{xsj} + A_{xdj} + A_{xnj} \nonumber \\
-%B_{xj} &=& B_{xsj} + B_{xdj} + B_{xnj} \, ,
-%\end{eqnarray}
-%
-%\noindent where $A_{xsj}$ and $B_{xsj}$ denote the real and imaginary components of the signal power in the Fourier amplitudes,  $A_{xdj}$ and $B_{xdj}$ denote the variance introduced by dead time, and $A_{xnj}$ and $B_{xnj}$ similarly denote the white noise components in the Fourier amplitudes.
-%For a large enough number of data points $N$, the Fourier amplitudes $A_{xj}$ and $B_{xj}$ will be composed of a sum of three independent random normal variables, with $A_{xsj} \sim \Normal(0, \sigma_{sj}^2)$,  $A_{xdj} \sim \Normal(0, \sigma_{dj}^2)$ and $A_{xnj} \sim \Normal(0, \sigma_n^2)$, where $\sigma_{sj}^2 = \sigma_{s}^2(\nu) = N_\mathrm{phot}P(\nu)/4$ is given by the power spectrum of the underlying stochastic process, $P_j = P(\nu_j)$, $\sigma_{dj}^2$ is an unknown, frequency-dependent variance introduced by dead time, and $N_{\mathrm{phot}} = \sum_{k=1}^{N}{x_k}$ is the integrated flux in the light curve.
-We also have $\sigma_n^2 = N_\mathrm{phot}/2$, and hence the combined distributions become
-%
-%\begin{eqnarray}
-%A_{xj} &\sim & \Normal(0, \sigma_{sj}^2 + \sigma_{dj}^2 + \sigma_{n}^2) \nonumber \\
-%A_{yj} &\sim & \Normal(0, \sigma_{sj}^2 + \sigma_{dj}^2 + \sigma_{n}^2) \nonumber \, .
-%\end{eqnarray}
-%
-%\noindent Similar expressions can be found for $A_{yj}$ and $B_{yj}$, respectively.
-It is important to note that $A_{xsj} = A_{ysj}$ and similarly $B_{xsj} = B_{ysj}$, that is, the amplitudes of the stationary noise process will be the same for the Fourier transforms of $\mathbf{x}$ and $\mathbf{y}$, while the components due to dead time and white noise differ between the two time series.
-%
-%As depicted in Figure~\ref{fig:fourierdiff}, the correlation between Fourier amplitudes implies that their difference will be independent of the source-induced variability $P(\nu_j)$ and will again be distributed following a normal distribution
-%
-%\[
-%A_{xj} - A_{yj} \sim \Normal(0, 2\sigma_{dj}^2 + 2\sigma_{n}^2) \; .
-%\]
-%
-%\noindent The difference in Fourier amplitudes effectively separates the frequency-dependent effects of source variability and variability due to detector effects.
-
 %%%%%%%%%%%%%%%%%%%%%%%% SECTION 3 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Data simulation} \label{sec:data}
-All simulated and real data sets in this paper were produced and/or analyzed with a combination of the two Python libraries \texttt{stingray}%
+All simulated sets in this paper were produced and analyzed with a combination of the two Python libraries \texttt{stingray}%
 \footnote{The library is under heavy development.
@@
     See \href{https://github.com/StingraySoftware/notebooks/}{https://github.com/StingraySoftware/notebooks/} for tutorials on simulations, light curve production and timing analysis with Stingray}
-\citep{huppenkothen2016} and \texttt{HENDRICS} v.\texttt{3.0b2} \citep[formerly known as MaLTPyNT;][]{2015ascl.soft02021B}, both based on Astropy \citep{astropy2013}.
+\citep{huppenkothen2016} and \texttt{HENDRICS} v.\texttt{3.0b2} \citep[formerly known as MaLTPyNT;][]{2015ascl.soft02021B}, both affiliated to Astropy \citep{astropy2013,astropy18}.
 
 We used the same procedure and algorithms described by \citet{Bachetti+15}, Section 4, which we briefly summarize here.
-%The classes in the \texttt{stingray.simulate} module were used to simulate light curves with a given noise profile. 
 We used the \citet{timmer1995} method to create a red noise light curve starting from a given power spectral shape. 
 This method is implemented in the \texttt{stingray.simulate} module.
-%We first created the noisy light curves and then used an acceptance-rejection method to obtain simulated events. 
 This step needs to be done carefully: if the initial light curves contain significant random noise, the process for the creation of events creates a random variate on the top of the local count rate--which is varying randomly already--producing a non-Poissonian final light curve.
@@
 Then, the \texttt{hendrics.fake.filter\_for\_deadtime()} function was used to apply a non-paralyzable dead time of 2.5\,ms to the simulated event lists.
-For more details on the simulated data sets, see also Section \ref{sec:correction} and the available Jupyter notebooks%
-\footnote{\href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II}} \citep[for a description of Jupyter notebooks, see][]{kluyver2016jupyter}.
-After producing these synthetic event lists, we started the standard timing analysis: we produced light curves with a bin time of $\sim0.122$\,ms, and calculated power spectral products (cospectrum, periodogram) over segments of these light curves using \texttt{stingray}.
-
-%\subsection{Cyg X-1 \nustar dataset}
-%We tested the method also on real data of several bright sources observed by \nustar.
-%As an example, we report here one such test done on \nustar data of the black hole binary Cyg~X-1 together with the steps to reproduce our analysis, using the linked Jupyter notebook if needed.
-%We downloaded the observation directory of \nustar ObsID 30001011009 (UT 2014-10-04) from the HEASARC using the custom \texttt{heasarc\_pipelines} package (Bachetti et al., ASCL identifier requested).
-%Equivalently, this download can be done using the online tools provided by HEASARC (e.g. \texttt{xamin}).
-%Starting from the standard cleaned science event files distributed by HEASARC, we applied a barycenter correction using the FTOOL \texttt{barycorr} shipped with HEASOFT 6.21 with the clock correction file n.
-71 from the \nustar CALDB.
-%We selected photons in a region of 50\arcsec around the nominal position of Cyg X-1 using the FTOOL \texttt{fselect}.%
-%\footnote{To use the method on different sources, it is sufficient to download a different ObsID and change the region file containing the position of the source}.
-%We used the scripts contained in \texttt{HENDRICS} to load the event lists for the two detectors FPMA and FPMB, calibrate them to translate the PI detectors into energy values, and produced light curves with photons from 3 to 79 keV and binned with uniform time bins of 1/4096$\sim2.44\cdot10^{-4}$\,sec%
-%\footnote{This procedure uses the scripts \texttt{HENreadfile}, \texttt{HENcalibrate} and \texttt{HENlcurve}, as described at\\ \href{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}{http://hendrics.readthedocs.io/en/master/tutorials/quicklook.html}}.
+For more details on the simulated data sets and the validation of the simulation infrastracture, see also Section \ref{sec:correction} and the available Jupyter notebooks%
+\footnote{\href{https://github.com/matteobachetti/deadtime-paper-II/}{https://github.com/matteobachetti/deadtime-paper-II/}}%
+\footnote{\href{https://github.com/stingraysoftware/HENDRICS/notebooks}{https://github.com/stingraysoftware/HENDRICS/notebooks}}.
+After producing these synthetic event lists, we started the standard timing analysis: we produced light curves with a bin time of $\sim0.244$\,ms, and calculated power spectral products (cospectrum, periodogram) over segments of these light curves using \texttt{stingray}.
 
@@
 \plotone{before_and_after.eps}
-%\plotone{pds_pdf.pdf}
-\caption{Periodogram and cospectrum, before and after FAD correction, for a pure white noise light curve. 
+\caption{Periodogram and cospectrum, before and after FAD correction, for a pure white noise light curve (count rate 2000 ct/s). 
 The deadtime-driven distortion of the white noise level in the periodogram, and the frequency-dependent modulation of the \rms in both spectra, disappear after applying the FAD correction. 
-Spectra were calculated over 2-sec intervals and averaged, to decrease the scatter and highlight the distortion of powers.}
+We averaged 500 periodograms calculated over 2-sec intervals, to decrease the scatter and highlight the distortion of powers.}
 \label{fig:comparison}
@@
 As laid out in Section \ref{sec:fourierdiff}, the difference of Fourier amplitudes from two independent but identical detectors shows no source variability, but \textit{still shows the same distortion} due to dead time (See Figure ~\ref{fig:fourierdiff}, left panel, where this is shown with red noise).
-Let us simulate two constant light curves with an incident mean count rate of 400 counts/sec and a dead time of 2.5 ms, as we would expect from the two identical detectors of \nustar observing the same stable X-ray source.
-The Fourier amplitudes of the light curves from the two detectors are heavily distorted by dead time, with the characteristic damped oscillator-like shape \citep{Vikhlinin+94,Zhang+95}  (Figure ~\ref{fig:fourierdiff}, middle panel).
+Let us simulate two constant 1000-sec light curves with an incident mean count rate of 2000 counts/sec and a dead time of 2.5 ms, as we would expect from the two identical detectors of \nustar observing the same stable X-ray source.
+The Fourier amplitudes of the light curves from the two detectors are heavily distorted by dead time, with the characteristic damped oscillator-like shape \citep{Vikhlinin+94,Zhang+95}  (Figure~\ref{fig:fourierdiff}, middle panel).
 Therefore, using the difference between the Fourier amplitudes in two detectors, we can in principle renormalize the periodogram so that only the source variability alters its otherwise flat shape.
@@
 Starting from a heavily distorted distribution of the powers, applying the FAD correction ``flattens'' remarkably well the white noise level of the periodogram and the distribution of the scatter of the white noise periodogram and cospectrum.
-Also, it reinstates a correct distribution of powers, following the expected $\chi^2_2$ distribution \citep{Lewin+88} very closely. 
-Analogously, the corrected cospectrum will follow the expected Laplace distribution (Huppenkothen \& Bachetti, sub.).
-While the original dead time-affected cospectrum had a frequency-dependent modification to the \rms level, the FAD-corrected cospectrum gets back to a frequency-independent shape, like in the dead time-free case.
+Also, it reinstates a correct distribution of powers, following very closely the expected $\chi^2_2$ distribution (\citealt{Lewin+88}; Figure~\ref{fig:dist}, right). 
+Analogously, the corrected cospectrum will follow the expected Laplace distribution (\citealt{HuppenkothenBachetti18}; Figure~\ref{fig:dist}, left).
+While the original dead time-affected cospectrum had a distorted, frequency-dependent \rms level, the FAD-corrected cospectrum returns to the correct distribution at all frequencies.
 
@@
 	\item subtract the Leahy-normalized Fourier amplitudes of the two detectors between them, \textit{take the absolute value}, and obtain this way the Fourier Amplitude Differences (FAD);
-	\item \textit{smooth} the FAD using a Gaussian-window interpolation with a large number of bins, in our case all the bins contained in 1-2 Hz;
+	\item \textit{smooth} the FAD using a Gaussian-window interpolation with a large number of bins, in our case all the bins contained in 1-2 Hz, but this might need an adjustment at extreme count rates ($\gtrsim 10/\deadt$), where significant gradients in the white noise periodogram can occur in less than 1 Hz;
 	\item use the separated single-detector and total-intensity \textit{unnormalized} Fourier amplitudes to calculate the periodograms (and/or the cospectrum);
@@
     \plotone{four_qpos.eps}
-    \caption{Periodogram from a simulation with four Lorentzian features (at 50, 200, 300 and 400 Hz) with 40-Hz full with at half maximum (FWHM). 
+    \caption{Periodogram, in fractional \rms normalization, from a simulation with four Lorentzian features (at 50, 200, 300 and 400 Hz) with 40-Hz full with at half maximum (FWHM). 
     We plotted and fitted the periodograms obtained before and after applying a 2.5\,ms dead time filter
@@
 
-We are now ready to verify the last step: is the FAD-corrected periodogram equivalent (albeit with some loss of sensitivity due to the lower number of photons) to the dead time-free periodogram?
-To test this, we produced a number of different synthetic datasets as explained in Section~\ref{sec:wndeadtime}, containing different combinations of QPOs and broadband noise components.\footnote{See the notebooks at \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the analysis plotted in the Figures of this paper and more.
+We are now ready to verify whether the FAD-corrected periodogram is a good approximation to the dead time-free periodogram.
+To test this, we produced a number of different synthetic datasets as explained in Section~\ref{sec:wndeadtime}, containing different combinations of QPOs and broadband noise components, expressed as pairs of Lorentzian curves\footnote{See the notebooks at \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II} to reproduce the analysis plotted in the Figures of this paper and more.
 The algorithm described in Section~\ref{sec:fad} is contained in the \texttt{fad\_correction.py} file in the notebooks directory.}
-We first calculated the periodogram and cospectrum of the dead time-free data, averaged over 128-s intervals.
-Then, we applied a dead time filter to the event list and applied the FAD correction, as described in Section~\ref{sec:fad}
+We first calculated the periodogram and cospectrum of the dead time-free data, averaged over 64--512\,s intervals.
+Then, we applied a 2.5\,ms dead time filter to the event list and applied the FAD correction, as described in Section~\ref{sec:fad}
 
-All spectra were then expressed in fractional \rms normalization, where the integral of the fitted power spectral components over the frequency returns directly its fractional \rms.
-In the \rms normalization, the values of each point of the periodogram, after white noise subtraction, should be consistent between the dead time-free and the FAD-corrected periodograms.
-We fitted all spectra with the model which produced the simulated data and checked if the \rms values were consistent with the fit on the dead time-free periodogram.
-To calculate this \rms, we fitted the spectra with two Lorentzian components, and integrated the model over the full frequency range.
-For periodograms, the model included also a constant offset to account for the white noise level.
+All spectra were then expressed in fractional \rms normalization \citep{Miyamoto+91,BelloniHasinger90}.
+In this normalization, the integrated model returns the full fractional \rms of the light curve, and the dead time-free and the FAD-corrected periodograms should be consistent over the full frequency range.
 An example of this analysis is shown in Figure~\ref{fig:pds}: the FAD successfully corrects so well periodograms and cospectra when compared to dead-time free simulated spectra, that in the figure they are almost indistinguishable.
 
+We ran extensive simulations testing how the method performs (1) for a range of different input count rates, leading to dead-time effects of different magnitude in the output periodograms and cospectra, and (2) when the light curves do not have the same count rate (since detectors may in reality have slightly different efficiencies).
+We fitted all spectra with a two-Lorentzian model, plus a constant offset to account for the white noise level in periodograms.
+We calculated the \rms by integrating the model fitted above over the full frequency range, and compared the results in the deadtime-free and FAD-corrected cases.
+
 \subsection{Simulation results and discussion}\label{sec:caveat}
+
 \begin{figure*}
@@
 
-In order to test the robustness of the FAD, we have ran extensive simulations testing how the method performs (1) for a range of different input count rates, leading to dead-time effects of different magnitude in the output periodograms and cospectra, and (2) whenthe light curves do not have the same count rate (since detectors may in reality have slightly different efficiencies).
-The simulations show that the shape of the periodogram is precisely corrected by the FAD procedure if (1) \textit{the input light curves have the same count rate} and (2) \textit{for values of the input count rate and \rms that are not too extreme}.
+The simulations described above show that the shape of the periodogram is precisely corrected by the FAD procedure if \textit{the input light curves have the same count rate} and \textit{for values of the input count rate and \rms that are not too extreme}.
 Differing input count rates in different detectors matter in practice only for the single-detector periodogram, but \textit{not} for cospectra and total-intensity periodograms.
-At high count rates, single-detector periodograms are corrected very well only if the two detectors have very similar count rates, and count rates must be more similar athigher count rates in order for the correction to apply.
+At high count rates, single-detector periodograms are corrected very well only if the two detectors have very similar count rates, and count rates must be more similar at higher count rates in order for the correction to apply.
 However, we find that the total-intensity periodogram and the cospectrum remain well corrected by the FAD even if the count rate in the two detectors differs by 30\% in most cases.
@@
 A practical way to estimate this effect during analysis is to apply the FAD, obtain a best fit model, calculate the \rms, and simulate a number of realizations of the light curve to evaluate the amount of overestimation involved\footnote{relevant code can be found in Jupyter notebooks in the following GitHub repository: \href{https://github.com/matteobachetti/deadtime-paper-II}{https://github.com/matteobachetti/deadtime-paper-II}}.
-
-%%%%%%%%%%%%%%%%%%%%%%%% SECTION 6 %%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%\section{Example: Cyg X-1 \nustar dataset}
-%We tested the method also on real data of several bright sources observed by \nustar.
-%As an example, we report here one such test done on \nustar data of the black hole binary Cyg~X-1 together with the steps to reproduce our analysis, using the linked Jupyter notebook if needed.
-%
-%Cyg X-1 is a persistent black hole X-ray binary, alternating soft and hard spectral states with distinct timing and spectral features \citep[see, e.g., ][]{Grinberg+13}.
-%We downloaded standard data products of 
-%The observation we analyze here was taken during the source's soft state, that is characterized by a non-thermal X-ray spectrum, stable radio jets and, what matters the most here, distinct aperiodic variability that is well fitted by an exponential cutoff power law with index $\sim1$ (see, e.g., \citealt{Gilfanov+00}).
-%We followed the procedure described in \sref{sec:correction}, dividing the light curves in 512-s segments and smoothing the squared FAD with a Gaussian window of 1-s width (512 bins).
-%The results are shown in Figure~\ref{fig:pds}, lower panel for comparison with the simulations. 
-%
-%We fitted the four spectra of Cyg X-1 with an exponential cutoff power law. 
-%For periodograms, we added to the models an additive constant to account for the white noise level.
-%In all cases, the estimates returned by the fit were consistent between the different spectra in all but the amplitude parameter of the power law curve.
-%We used this amplitude to calculate the ratios between the \rms measured by the deadtime-affected cospectrum and the FAD-corrected spectra.
-%The increase of \rms between the dead time-affected cospectrum and the FAD-corrected cospectrum and periodograms is consistent to 2\% with the ratio $r_{in}/r_{det}$, where $r_{in}$ is the incident count rate, and $r_{det}$ is the detected count rate,
-%given by
-%
-%\begin{equation}
-%r_{det} = \frac{r_{in}}{1 + \deadt r_{in}}
-%\end{equation} 
-%(using the standard non-paralyzable dead time formula, where \deadt is dead time) which is the drop of \rms expected from the effect of dead time \citep{Bachetti+15}.
 
@@
 Only in cases where the count rate and the \rms are \textit{both} very high ($>$500 ct/s incident, $>$40\% resp.), the FAD correction leads to an overestimation the \rms, even if the white noise level of the periodogram remains flat.
-%In these case, we provide some example simulation code to estimate this effect in the notebooks.
-%This software will be merged into the main repository of \texttt{stingray} before publication.
 
 \acknowledgments
-We thank the anonymous referee for providing very helpful feedback.
+We thank the anonymous referee for providing very insightful feedback.
 We thank David W. Hogg for useful discussions on the topic of Fourier analysis, and Jeff Scargle for useful suggestions and comments.
@@
 
+\software{Astropy \citep{astropy2013},
+          Matplotlib \citep{Matplotlib07},
+          scipy \& numpy \citep{numpy11},
+          stingray \citep{huppenkothen2016},
+          HENDRICS \citep[before name change]{2015ascl.soft02021B},
+          Jupyter notebooks \citep{kluyver2016jupyter}}
 \bibliographystyle{aasjournal}
 %\bibliography{deadtime,papers3}
+
 \begin{thebibliography}{}
-\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
 \providecommand{\url}[1]{\href{#1}{#1}}
@@
   {Ptak}, {Refsdal}, {Servillat}, \& {Streicher}}]{astropy2013}
-{Astropy Collaboration}, {Robitaille}, T.~P., {Tollerud}, E.~J., {et~al.} 2013,
+{Astropy Collaboration}, {et~al.} 2013,
   \aap, 558, A33
+
+\bibitem[{Astropy Project {et~al.}(2018)Price-Whelan, , G{\"u}nther, Lim,
+  Crawford, Conseil, Shupe, Craig, Dencheva, Ginsburg, VanderPlas, Bradley,
+  P{\'e}rez-Su{\'a}rez, de~Val-Borro, Aldcroft, Cruz, Robitaille, Tollerud,
+  Ardelean, Babej, Bachetti, Bakanov, Bamford, Barentsen, Barmby, Baumbach,
+  Berry, Biscani, Boquien, Bostroem, Bouma, Brammer, Bray, Breytenbach,
+  Buddelmeijer, Burke, Calderone, Rodr{\'\i}guez, Cara, Cardoso, Cheedella,
+  Copin, Crichton, D{\'A}vella, Deil, Depagne, Dietrich, Donath, Droettboom,
+  Earl, Erben, Fabbro, Ferreira, Finethy, Fox, Garrison, Gibbons, Goldstein,
+  Gommers, Greco, Greenfield, Groener, Grollier, Hagen, Hirst, Homeier, Horton,
+  Hosseinzadeh, Hu, Hunkeler, , Jain, Jenness, Kanarek, Kendrew, Kern,
+  Kerzendorf, Khvalko, King, Kirkby, Kulkarni, Kumar, Lee, Lenz, Littlefair,
+  Ma, Macleod, Mastropietro, McCully, Montagnac, Morris, Mueller, Mumford,
+  Muna, Murphy, Nelson, Nguyen, Ninan, N{\"o}the, Ogaz, Oh, Parejko, Parley,
+  Pascual, Patil, Patil, Plunkett, Prochaska, Rastogi, Janga, Sabater,
+  Sakurikar, Seifert, Sherbert, Sherwood-Taylor, Shih, Sick, Silbiger,
+  Singanamalla, {Singer, L. P.}, Sladen, Sooley, Sornarajah, Streicher, Teuben,
+  Thomas, Tremblay, Turner, Terr{\'o}n, van Kerkwijk, de~la Vega, Watkins,
+  Weaver, Whitmore, Woillez, \& Zabalza}]{astropy18}
+Astropy Project, {et~al.} 2018, arXiv,
+  arXiv:1801.02634
 
@@
 Belloni, T., \& Hasinger, G. 1990, A{\&}A, 230, 103
+
+\bibitem[{Hunter(2007)}]{Matplotlib07}
+Hunter, J.~D. 2007, Computing in Science and Engineering, 9, 90
+
+\bibitem[{Huppenkothen \& Bachetti(2017)}]{HuppenkothenBachetti18}
+Huppenkothen, D., \& Bachetti, M. 2017, arXiv, arXiv:1709.09666
 
@@
 
+\bibitem[{van~der Walt {et~al.}(2011)van~der Walt, Colbert, \&
+  Varoquaux}]{numpy11}
+van~der Walt, S., Colbert, S.~C., \& Varoquaux, G. 2011, Computing in Science
+  Engineering, 13, 22
+
 \bibitem[{Vikhlinin {et~al.}(1994)Vikhlinin, Churazov, \&

### 2018-01-31 paper/deadtime.tex
Correct affiliations, correct paper references, some typos

@@
 \newcommand{\counts}{\ensuremath{y}\xspace}
-\newcommand{\rms}{\ensuremath{\mathrm{r.m.s.}}\xspace}
+\newcommand{\rms}{\ensuremath{\mathrm{rms}}\xspace}
 \newcommand{\pars}{\ensuremath{\theta}\xspace}
@@
 \affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Place, New York, NY 10003, USA}
+\affiliation{DIRAC Institute, Department of Astronomy, University of Washington, 3910 15th Ave NE, Seattle, WA 98195}
 
@@
 This can make it difficult to model the aperiodic variability of the source or look for quasi-periodic oscillations.
-Whereas in some instruments a simple a-priori correction for dead time-affected power spectra is possible, 
+Whereas in some instruments a simple a priori correction for dead-time-affected power spectra is possible, 
 this is not the case for others such as \nustar, where the dead time is non-constant and long ($\sim$2.5\,ms).
@@
 
-In this Letter we suggest a new, powerful method to normalize deadtime-affected cospectra and power density spectra.
+In this Letter, we suggest a new, powerful method to normalize dead-time-affected cospectra and power density spectra.
 Our approach uses the difference of the Fourier amplitudes from two independent detectors to characterize and filter out the effect of dead time.
@@
 In \sref{sec:fourierdiff} we show that, in the absence of dead time, the difference of the Fourier amplitudes calculated from two independent detectors contains the sum of the correlated signal (the source signal) and uncorrelated noise (detector-related noise), and that their difference eliminates the source part.
-In \sref{sec:fadsec} we use extensive simulations to show how to use this fact to correct deadtime-affected periodograms, and we describe the limitations of this method.
+In \sref{sec:fadsec} we use extensive simulations to show how to use this fact to correct dead-time-affected periodograms, and we describe the limitations of this method.
 
@@
 The red curve gives the frequency-dependent spread of the distributions, measured by the mean of the absolute values of the curves in each frequency bin. 
-The different behavior of Fourier amplitude differences in the two cases is evident: in the deadtime-free case, the Fourier amplitude difference does \textit{not} correlate with the Fourier amplitude, while in the deadtime-affected case, this follows a precise linear relationship.
+The different behavior of Fourier amplitude differences in the two cases is evident: in the dead-time-free case, the Fourier amplitude difference does \textit{not} correlate with the Fourier amplitude, while in the dead-time-affected case, this follows a precise linear relationship.
 }
@@
 \footnote{\href{https://github.com/matteobachetti/deadtime-paper-II/}{https://github.com/matteobachetti/deadtime-paper-II/}}%
-\footnote{\href{https://github.com/stingraysoftware/HENDRICS/notebooks}{https://github.com/stingraysoftware/HENDRICS/notebooks}}.
+\footnote{\href{https://github.com/StingraySoftware/HENDRICS/tree/master/notebooks}{https://github.com/StingraySoftware/HENDRICS/tree/master/notebooks}}.
 After producing these synthetic event lists, we started the standard timing analysis: we produced light curves with a bin time of $\sim0.244$\,ms, and calculated power spectral products (cospectrum, periodogram) over segments of these light curves using \texttt{stingray}.
@@
 \caption{Periodogram and cospectrum, before and after FAD correction, for a pure white noise light curve (count rate 2000 ct/s). 
-The deadtime-driven distortion of the white noise level in the periodogram, and the frequency-dependent modulation of the \rms in both spectra, disappear after applying the FAD correction. 
+The dead-time-driven distortion of the white noise level in the periodogram, and the frequency-dependent modulation of the \rms in both spectra, disappear after applying the FAD correction. 
 We averaged 500 periodograms calculated over 2-sec intervals, to decrease the scatter and highlight the distortion of powers.}
@@
 As laid out in Section \ref{sec:fourierdiff}, the difference of Fourier amplitudes from two independent but identical detectors shows no source variability, but \textit{still shows the same distortion} due to dead time (See Figure ~\ref{fig:fourierdiff}, left panel, where this is shown with red noise).
-Let us simulate two constant 1000-sec light curves with an incident mean count rate of 2000 counts/sec and a dead time of 2.5 ms, as we would expect from the two identical detectors of \nustar observing the same stable X-ray source.
+Let us simulate two constant 1000\,sec light curves with an incident mean count rate of 2000 counts/sec and a dead time of 2.5 ms, as we would expect from the two identical detectors of \nustar observing the same stable X-ray source.
 The Fourier amplitudes of the light curves from the two detectors are heavily distorted by dead time, with the characteristic damped oscillator-like shape \citep{Vikhlinin+94,Zhang+95}  (Figure~\ref{fig:fourierdiff}, middle panel).
@@
     The total \rms before dead time was 30\% and the incident photon flux 400 ct/s. 
-    There is no significant difference between the FAD-normalized and the deadtime-free periodogram, while the cospectrum without FAD (pink) clearly distorts the curves at different frequencies.
+    There is no significant difference between the FAD-normalized and the dead-time-free periodogram, while the cospectrum without FAD (pink) clearly distorts the curves at different frequencies.
     }
@@
 We fitted all spectra with a two-Lorentzian model, plus a constant offset to account for the white noise level in periodograms.
-We calculated the \rms by integrating the model fitted above over the full frequency range, and compared the results in the deadtime-free and FAD-corrected cases.
+We calculated the \rms by integrating the model fitted above over the full frequency range, and compared the results in the dead-time-free and FAD-corrected cases.
 
@@
 DH is supported by the James Arthur Postdoctoral Fellowship and the Moore-Sloan Data Science Environment at New York University.
+DH acknowledges support from the DIRAC Institute in the Department of Astronomy at the University of Washington.
+The DIRAC Institute is supported through generous gifts from the Charles and Lisa Simonyi Fund for Arts and Sciences, and the Washington Research Foundation.
 
@@
 \bibitem[{Bachetti(2015)}]{2015ascl.soft02021B}
-Bachetti, M. 2015, Astrophysics Source Code Library, ascl:1502.021
+Bachetti, M. 2015, MaLTPyNT: Quick look timing analysis for NuSTAR data, Astrophysics Source Code Library, ascl:1502.021
 
@@
 \bibitem[{Huppenkothen \& Bachetti(2017)}]{HuppenkothenBachetti18}
-Huppenkothen, D., \& Bachetti, M. 2017, arXiv, arXiv:1709.09666
+Huppenkothen, D., \& Bachetti, M. 2017, accepted to ApJ, arXiv:1709.09666
 
@@
   {et~al.}}]{kluyver2016jupyter}
-Kluyver, T., Ragan-Kelley, B., P{\'e}rez, F., {et~al.} 2016, in ELPUB, 87--90
+Kluyver, T., Ragan-Kelley, B., P{\'e}rez, F., {et~al.} 2016, in ``Positioning and Power in Academic Publishing: Players, Agents and Agendas'', 87--90
 
@@
   Gilfanov}]{Vikhlinin+94}
-Vikhlinin, A., Churazov, E., \& Gilfanov, M. 1994, 287, 73
+Vikhlinin, A., Churazov, E., \& Gilfanov, M. 1994, A\&A, 287, 73
 
